### 2016-04-18 ms_nihao_budget.tex
baryonic budget paper

\documentclass[useAMS,usenatbib]{mn2e}
\input psfig.sty
\usepackage{array}
%\usepackage{graphicx}
%\usepackage{epstopdf}

\voffset=-0.8in

\def \gas {\textsc{gasoline}}
\def \gastwo {\textsc{ESF-gasoline2}}
\def \changa {\textsc{changa}}
\def \mean#1{\left< #1 \right>}

%%MISC
\def \aj {AJ}
\def \apj {ApJ}
\def \apjl {ApJL}
\def \mnras {MNRAS}
\def \apjs {ApJS}
\def \aap {A\&A}
\def \nat {Nature}
\def \pasp {PASP}
\def \na {NewA}

\def \etal {et~al.~}
\def \eg{e.g.}
\def \Section{\S}
\def \spose#1{\hbox  to 0pt{#1\hss}}  
\def \lta{\mathrel{\spose{\lower 3pt\hbox{$\sim$}}\raise  2.0pt\hbox{$<$}}}
\def \gta{\mathrel{\spose{\lower  3pt\hbox{$\sim$}}\raise 2.0pt\hbox{$>$}}}
\def \ion#1#2{#1{\footnotesize{#2}}\relax}
\def \ha       {H$\alpha$}
\def \hi       {\ion{H}{I}}
\def \hii      {\ion{H}{II}}
\def \oii      {[\ion{O}{II}]}

%%UNITS
\def \kmsmpc {\>{\rm km}\,{\rm s}^{-1}\,{\rm Mpc}^{-1}}
\def \kms {\ifmmode  \,\rm km\,s^{-1} \else $\,\rm km\,s^{-1}  $ \fi }
\def \kpc {\ifmmode  {\rm kpc}  \else ${\rm  kpc}$ \fi  }  
\def \hkpc {\ifmmode  {h^{-1}\rm kpc}  \else ${h^{-1}\rm kpc}$ \fi  }  
\def \hMpc {\ifmmode  {h^{-1}\rm Mpc}  \else ${h^{-1}\rm Mpc}$ \fi  }  
\def \Msun {\ifmmode \rm M_{\odot} \else $\rm M_{\odot}$ \fi}
\def \hMsun {\ifmmode h^{-1}\,\rm M_{\odot} \else $h^{-1}\,\rm M_{\odot}$ \fi}
\def \hhMsun {\ifmmode h^{-2}\,\rm M_{\odot}\else $h^{-2}\,\rm M_{\odot}$ \fi}
\def \Lsun {\ifmmode L_{\odot} \else $L_{\odot}$ \fi} 
\def \hhLsun {\ifmmode h^{-2}\,\rm L_{\odot} \else $h^{-2}\,\rm L_{\odot}$ \fi}

%%COSMOLOGY

\def\LCDM{$\Lambda$CDM }
\def \LCDM {\ifmmode \Lambda{\rm CDM} \else $\Lambda{\rm CDM}$ \fi}
\def \sig8 {\ifmmode \sigma_8 \else $\sigma_8$ \fi} 
\def \Omegam {\ifmmode \Omega_{\rm m} \else $\Omega_{\rm m}$ \fi} 
\def \Omegab {\ifmmode \Omega_{\rm b} \else $\Omega_{\rm b}$ \fi} 
\def \Omegar {\ifmmode \Omega_{\rm r} \else $\Omega_{\rm r}$ \fi} 
\def \fbar {\ifmmode f_{\rm b} \else $f_{\rm b}$ \fi} 
\def \OmegaL {\ifmmode \Omega_{\rm \Lambda} \else $\Omega_{\rm \Lambda}$\fi} 
\def \Deltavir {\ifmmode \Delta_{\rm vir} \else $\Delta_{\rm vir}$ \fi}
\def \rhocrit {\ifmmode \rho_{\rm crit} \else $\rho_{\rm crit}$ \fi}

%DARK MATTER
\def \rs {\ifmmode r_{\rm s} \else $r_{\rm s}$ \fi} 
\def \rh {\ifmmode r_{\rm h} \else $r_{\rm h}$ \fi} 
\def \Rvir {\ifmmode R_{\rm vir} \else $R_{\rm vir}$ \fi}
\def \Vvir {\ifmmode V_{\rm  vir} \else  $V_{\rm vir}$  \fi} 
\def \Vmax {\ifmmode V_{\rm  max} \else  $V_{\rm max}$  \fi} 
\def \Mvir {\ifmmode M_{\rm  vir} \else $M_{\rm  vir}$ \fi}  
\def \Mhalo {\ifmmode M_{\rm tot} \else $M_{\rm  tot}$ \fi}  
\def \Nvir {\ifmmode N_{\rm  vir} \else $N_{\rm  vir}$ \fi}  
\def \Jvir {\ifmmode J_{\rm vir} \else $J_{\rm vir}$ \fi} 
\def \Evir {\ifmmode E_{\rm vir} \else $E_{\rm vir}$ \fi} 
\def \lam {\ifmmode \lambda  \else $\lambda$ \fi} 
\def \lamp {\ifmmode \lambda^{\prime} \else $\lambda^{\prime}$  \fi} 
\def \lampc {\ifmmode \lambda^{\prime}_{\rm c} \else
  $\lambda^{\prime}_{\rm c}$  \fi}

\def \xoff {\ifmmode x_{\rm off} \else $x_{\rm off}$ \fi}
\def \rhorms {\ifmmode \rho_{\rm rms} \else $\rho_{\rm rms}$ \fi}
\def \qbar {\ifmmode \bar{q} \else $\bar{q}$ \fi}

%%BARYONS
\def \Mb {\ifmmode M_{\rm b} \else $M_{\rm b}$ \fi} 
\def \eSF {\ifmmode \epsilon_{\rm SF} \else $\epsilon_{\rm SF}$ \fi} 
\def \Md {\ifmmode M_{\rm d} \else $M_{\rm d}$ \fi} 
\def \Mg {\ifmmode M_{\rm g} \else $M_{\rm g}$ \fi} 
\def \Rb {\ifmmode R_{\rm b} \else $R_{\rm b}$ \fi} 
\def \Rd {\ifmmode R_{\rm d} \else $R_{\rm d}$ \fi} 
\def \Rg {\ifmmode R_{\rm g} \else $R_{\rm g}$ \fi} 
\def \mgal {\ifmmode m_{\rm gal} \else $m_{\rm gal}$ \fi} 
\def \rj {\ifmmode {\cal R}_j \else ${\cal R}_j$ \fi} 
\def \lamgal {\ifmmode \lambda_{\rm gal} \else $\lambda_{\rm gal}$ \fi} 
\def \Vcirc {\ifmmode V_{\rm circ} \else $V_{\rm circ}$ \fi} 
\def \Vrot {\ifmmode V_{\rm rot} \else $V_{\rm rot}$ \fi} 
\def \Vflat {\ifmmode V_{\rm flat} \else $V_{\rm flat}$ \fi} 
\def \Mstar {\ifmmode M_{\rm star} \else $M_{\rm star}$ \fi} 
\def \Mgas {\ifmmode M_{\rm gas} \else $M_{\rm gas}$ \fi} 
\def \Mbar {\ifmmode M_{\rm bar} \else $M_{\rm bar}$ \fi}

%%MASS-TO-LIGHT RATIOS
\def \DeltaIMF {\ifmmode \Delta_{\rm IMF} \else $\Delta_{\rm IMF}$ \fi}

\def \VV {\ifmmode V_{\rm 2.2}/V_{200} \else $V_{2.2}/V_{200}$ \fi} 
\def \dvr {\ifmmode \partial_{\rm VR} \else $\partial_{\rm VR}$ \fi}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Baryon Budget] {NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes}

\author[Wang et al.]{Liang Wang$^{1,3}$\thanks{wangliang@pmo.ac.cn}, Aaron A. Dutton$^{2,3}$,
  Gregory S. Stinson$^3$, Andrea V. Macci\`o$^{2,3}$, 
\newauthor{Thales Gutcke$^3$, Xi Kang$^1$}\\
$^1$Purple Mountain Observatory, the Partner Group of MPI f\"ur Astronomie, 2 West Beijing Road, Nanjing 210008, China\\
$^2$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\
$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany}
\begin{document}

\date{to be submitted to MNRAS}

\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2015}

\maketitle

\label{firstpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas ($10^7$K$ <
  T$), inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that for all of our haloes, the missing mass is not just outside 
  the virial radius $\Rvir$, it has been relocated past 2$\Rvir$.  
  Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing $\sim
  90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with observational estimates.    
%  Finally we show that the baryonic budget of most massive 
%  galaxies in NIHAO suite can match the observation for most 
%  components but the cool gas, which requires further 
%  theoretical and observational work to find the answer where
%  the cool gas actually is.
\end{abstract}

\begin{keywords}
  galaxies: evolution -- galaxies: formation -- galaxies: dwarf -- galaxies: spiral -- 
  methods: numerical -- cosmology: theory
\end{keywords}

\setcounter{footnote}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 1: INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}
Cosmic structure formation has redistributed the baryons from  a
nearly uniformly distributed plasma into a variety of states,
including stars, stellar remnants, cold (atomic and molecular) gas,
and hot (ionized) gas. The theories of galaxy formation can predict
the amount of mass in these different states, which can in turn be tested by
observational constraints.

%% missing baryon problem
On cosmological scales, the ratio between the total baryonic and
gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
  b}/\Omega_{\rm m}\simeq 0.16$ (The Planck Collaboration 2014).
However, the cold baryonic mass density implied by several galaxy baryon
estimates is only 3-8\% of the big bang nucleosynthesis expection
\citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
cosmic baryons are thought to be in the form of hot gas around or
between galaxies \citep{Cen09}. Until recently only a fraction of
these baryons had been detected \citep{Bregman07, Shull12}.  This
discrepancy is referred to as the ``missing baryon problem''.
Recent advances in the detection of gas in the circum
galactic medium (CGM) have come from the COS survey \citep{Tumlinson11,
  Tumlinson13, Thom12,  Werk12, Werk13}.  On the scale of Milky Way
mass haloes $\Mhalo \sim 10^{12}\Msun$ a significant amount of warm
($10^4 < T < 10^7$K) gas has been detected \citep{Werk14}, accounting
for 33-88\% of the baryon budget. In the future such observations will
be extended to a wider range of halo masses.

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project. NIHAO galaxies are consistent with the stellar mass vs halo
mass relations from halo abundance matching since redshift $z\sim 4$
\citep{Wang15}, the galaxy star formation rate vs stellar mass
relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
stellar mass relation at $z\sim 0$ (Stinson \etal 2015).  Therefore,
the simulations make plausible predictions for the mass fractions and
physical locations of the warm and hot gas components.  We find that
all the haloes contain less baryons than expected according to the
cosmic baryonic fraction, but the missing fraction is strongly mass
dependent.

This paper is organized as follows: The cosmological hydrodynamical
simulations including star formation and feedback are briefly
described in  \S\ref{sec:sims}; In \S\ref{sec:budget} we present the
results including the baryonic budget, baryon distribution, and a
comparison with observations; \S\ref{sec:sum} gives a summary of our
results.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 2 SIMULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulations} 
\label{sec:sims}

In this study we use simulations from the NIHAO (Numerical
Investigation of a Hundred Astrophysical Objects) project \citep{Wang15}.  
The initial conditions are created to keep the same numerical
resolution across the whole mass range with typically a million dark
matter particles inside the virial radius of the target halo at 
redshift $z=0$.  The halos to be re-simulated at higher resolution
with baryons have been extracted from 3 different pure N-body
simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
respectively.  We adopted the  latest compilation of cosmological
parameters from the Planck  satellite \citep{Planck14}. 
More information on the collisionless parent simulations and
sample  selection can be found in \citet{Dutton14} and \citet{Wang15}

We use the SPH hydrodynamics code {\sc gasoline} \citep{Wadsley04},
with a revised treatment of  hydrodynamics as described in
\citet{Keller14}.  The code includes a subgrid model for turbulent
mixing of metal and energy \citep{Wadsley08}, heating and cooling
include photoelectric heating of dust grains, ultraviolet (UV) heating
and ionization and  cooling due to hydrogen, helium and metals
\citep{Shen10}.  The star formation and feedback modeling follows what
was used in the MaGICC simulations \citep{Stinson13}.  There are two
small changes in NIHAO simulations: The change in  number of neighbors
and the new combination of softening length and  particle mass increases
the threshold for star formation from  9.3 to 10.3
cm$^{-3}$, the increase of pre-SN feedback efficiency $\epsilon_{\rm
  ESF}$, from 0.1 to 0.13.  The more detail on star formation and
feedback modeling can be found in \citet{Wang15}.

%% FIGURE 1
\begin{figure}
\centerline{
%  \psfig{figure=barbudget_linear_v3.eps,width=0.5\textwidth}}
%\centerline{
%  \psfig{figure=barbudget_v3.eps,width=0.5\textwidth}
  \psfig{figure=barbudget_linearlog.eps,width=0.5\textwidth}
}
\caption{Fractional baryon content of our NIHAO simulations 
  as a function of halo
  mass. The green points show the ratio between the baryonic mass
  (stars + gas) inside the virial radius and the total baryonic mass
  associated with the dark matter halo and the green lines are best
  fitting lines. The blue points show the
  corresponding fraction for the stars. The solid green line and
  shaded region shows a double power-law fit, together with the
  1$\sigma$ scatter. For the stellar mass fraction we show several
  relations from halo abundance matching.    The linear (upper panel)
  and logarithmic (lower panel) scales emphasize the large amount of
  ``missing'' baryons and the low star formation efficiencies.}
\label{fig:budget}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 3 RESULTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Results}
%\label{sec:results}

%We study the baryonic budget using the full set simulations of the NIHAO project.  
%The large range of the mass covered by our simulations enables
%us see the baryon fractions and mass profiles of different 
%galaxies, depending on the halo mass and stellar content.

%% FIGURE 2
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile_v4.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations.
  A comparison of how the baryons distribute in the halo with 
  different masses. 
  The lines are color coded by their halo mass, which show a clear
  trend that the more massive halo preserve more baryons alone
  the radius.}
\label{fig:rps}
\end{figure}

\section{Baryon budget}
\label{sec:budget}

We define the fiducial baryonic mass as:
\begin{equation}
M_{\rm b} \equiv M_{\rm b}(R_{200})= \frac{f_{\rm b}}{1-f_{\rm b}}M_{\rm dm}(R_{200}) 
\end{equation}
where the $M_{\rm dm}$ is the total dark matter mass in the halo, and
the $f_{\rm b} = \Omegab/\Omegam \sim 0.15$ is the cosmic baryon
fraction (the ratio between baryon density and mass density including baryonic mass
plus dark matter), so that the  $M_{\rm b}$ is the baryonic mass inside the
virial radius if the baryons follow the dark matter closely.

Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
component inside the virial radius 
to the fiducial baryonic mass for the most massive galaxy in
each zoom-in region. We present the fractions of total stellar mass
(blue points), and the total baryonic mass
including stellar mass plus gas mass (green points).
For the stellar mass fraction we also show the relations from the halo abundance 
matching \citep{Moster13, Behroozi13, Kravtsov14}.
The grey area is the one sigma scatter around the mean value 
from \citet{Kravtsov14}.

We tried to capture the behaviour of the baryonic mass fraction as a 
function of the halo mass using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line. These are 
measured in four different mass ranges, and are  summarized in Table.~\ref{tab:sigma}.

\begin{table}
\caption{Scatters for best fit parameters for the total baryonic mass 
fraction computed inside one virial radius, $R_{200}$,  as a function of halo mass $M_{200}$
in different mass ranges.} 
\begin{center}
\begin{tabular}{lc}
\hline
Mass Range & $\sigma $ \\
\hline
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$ & 0.151 \\
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$ & 0.236 \\
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$ & 0.125 \\
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$ & 0.0518 \\
\hline
\end{tabular}
\label{tab:sigma}
\end{center}
\end{table}

The trends of each component fraction are similar, in that  the
fractions are relatively low in low mass haloes, and increase as the
halo mass increases.  The main difference between the different
components is the slope, with the baryonic mass fraction having a
shallower slope than the stellar mass fraction.  This is because in low mass haloes
($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in the form of
gas, while in the highest mass haloes we study ($\Mhalo\sim
10^{12}\Msun$) there are roughly equal amounts of stars and gas.

Fig.~\ref{fig:budget} shows that all haloes in our study contain
less than the universal fraction of baryons. The
upper panel uses a linear y-axis scale, which highlights the large
amount of baryons that are missing, especially in low mass haloes. The
logarithmic scale in the lower panel highlights the power-law nature of the relatons.

Since the haloes we study are above the mass where the cosmic UV
background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons,
consistent with expectations from energy driven gas outflows
\citep[e.g.,][]{Dutton12}.

\subsection{Where are the missing baryons?}
\label{sec:where}

Fig.~\ref{fig:rps} shows the mass ratio profiles of total baryons  for
each simulation. Here the y-axis is the ratio between the baryonic to
dark matter mass, $M_{\rm b}(<R) / M_{\rm dm}(<R)$, enclosed
within a sphere of radius, $R$, normalized by the cosmic
baryon-to-dark matter ratio, $\Omega_{\rm b}/\Omega_{\rm dm}$.

Each solid curve represents a halo, and the curves are colored by
their halo mass (red for high masses to blue for low masses).  Broadly
speaking, the curves have a similar shape, with a normalization that
depends on halo mass. They have a cusp in  the central region where the
stars and cold gas dominate, then become flat in the outer region.
More massive haloes have higher baryon fractions at all radii.  At
small radii, the baryon to dark matter ratio is higher than the cosmic
value due to gas dissipation.  Even beyond the virial radius, there is
little change in the baryon fraction up to 2 virial radii.  We thus
conclude that the missing baryons are well outside of the virial
radius.

%The curves show a gradual transition based on mass that confirms 
%what we find in Fig.~\ref{fig:budget}. 
%In general terms, the lowest mass halos have a small peak but drop
%relatively steeply until $\sim$ 0.2R$_{200}$, then the curves rise slowly.
%As the masses increase, the central peaks rise and the curves in the 
%outer part are flater.
%Finally, the most massive galaxies have an almost constant curve 
%which are close but still less than 1.

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=budget.eps,width=0.5\textwidth}
}
\caption{Baryonic budget (the fraction of different components) 
  of $3.5\times 10^{11} < M_{200}/\Msun <
  3.5 \times 10^{12}$ NIHAO galaxies (blue points 
  with 1$\sigma$ error bars) compared with observations of 
  M$_{200}$ = 10$^{12.2}$ $\Msun$ galaxies (shaded regions)
  }
\label{fig:comparison}
\end{figure}

%% TABLE 2
\begin{table*}
\caption{The baryonic budget parameters for galaxies in NIHAO sample
  in different mass bins. We refer to gas in the temperature range  T
  $<$ $10^4$ K as cold; $10^4$ K $\leqslant$ T $<$ $10^5$ K as cool;
  $10^5$ K $\leqslant$ T $<$ $10^7$ K as warm;  and T $\geqslant$
  $10^7$ K as hot.}
\begin{center}
\begin{tabular}{ccccc}
\hline
\input{budgettable4.txt}
\hline
\end{tabular}
\label{tab:comperison}
\end{center}
\end{table*}

\subsection{Comparison with Observations of Milky Way mass haloes}
Since the CGM is too diffuse to create emission lines, it must be
observed using quasar absorption lines.
The COS-HALOs survey is filling in details about the $z \sim 0$
CGM \citep{Peeples14, Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.
For the CGM of low-redshift $L^*$ galaxies, \citet{Tumlinson13} and 
\citet{Peeples14} constrain the mass of  the
warm-hot CGM ($T \sim 10^{5-7}$), \citet{Werk14} provides a strict
lower limit to the mass of cool material ($T \sim 10^{4-5}$) in the
CGM of these galaxies.  In a study using X-rays, 
\citet{Anderson13} place a
constraints on the mass of  hot gas ($T > 10^7$) residing in the
extended hot halos.

In Fig.~\ref{fig:comparison}, we show the mean values and standard deviation
of the mass fraction of stars and different components of gas in our
most massive galaxies ($3.49 \times 10^{11} \Msun$ $<$ M$_{200}$ $<$ 
$3.53 \times 10^{12} \Msun$) with blue points and error bars.
The gas is assigned to a range of temperature bins: 
cold gas (T $< 10^4$ K), cool gas ($10^4$ K $<$ T $< 10^5$ K), 
warm gas ($10^5$ K $<$ T $< 10^7$ K) and hot gas (T $> 10^7$ K).
The observational constraints are shown with the same colour scheme
in Fig. 11 in \citet{Werk14}.

In this plot \citet{Werk14} provides observational constraints for 
CGM gas mass that are shown as the shaded bars.
The stellar  mass range comes from
halo abundance matching as described in \citet{Kravtsov14}.  
The cold disk gas mass comes from from \citet{Dutton11}.

The observations and the simulations match well in every phase
outside of the cool CGM gas, where the observations find $3\times$
the mass that simulations predict.  If the observations are correct,
the simulations have either ejected too far gas that could be cool, or 
they have created a CGM with the wrong mix of gas temperatures. The
total gas fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the
latter option.  As the CGM of lower mass galaxies will soon be observed ,
Table~\ref{tab:comperison} lists information about CGM
mass fractions of the different components of gas in haloes down to a
halo mass of $\sim 10^{10}\Msun$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SECTION 4: SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{sec:sum}

We have used the NIHAO galaxy simulation suite \citep{Wang15} to study
the statistical features of the baryonic budget and distribution
spanning halo masses of $\sim 10^{10}$ to $\sim 10^{12}\Msun$. NIHAO
is a large (currently 88) set of high resolution cosmological
hydrodynamical galaxy formation simulations. As shown in previous papers
the NIHAO galaxies reproduce several key observed scaling relations.
We summarize our results as follows:

\begin{itemize}
\item All of the NIHAO haloes have a lower baryon to dark matter ratio, 
      inside the viriral radius, than the cosmic baryon fraction.

\item The missing baryons in all haloes are beyond 2 virial radii.

\item Lower mass haloes have lost a larger fraction of their baryons, 
      even though they convert a lower fraction of the baryons into stars.

\item For the highest mass haloes in our study $\sim 10^{12}\Msun$ 
      our simulations are consistent with the observed fractions of stars, 
      cold gas, warm and hot gas. However, we underpredict 
      the cool ($10^4 < T < 10^5 K$) gas with $f_{\rm cool}=0.11\pm0.06$ 
      vs 0.28-0.48 observed.

\item This discrepancy may indicate that our feedback model pushes the 
      gas too far, or puts gas in the wrong phases, 
      and can be resolved with future observations. 
      Since we match the overall gas fraction we think that  
      there might be some problem in mixing the gas temperature.
\end{itemize}

\section*{Acknowledgments}

{\sc Gasoline} was written by Tom Quinn and James Wadsley. Without
their contribution, this paper would have been impossible.
The simulations were performed on the {\sc theo} cluster of the
Max-Planck-Institut f\"ur Astronomie and the {\sc hydra} cluster at
the Rechenzentrum in Garching; and the Milky Way supercomputer, funded
by the Deutsche Forschungsgemeinschaft (DFG) through Collaborative
Research Center (SFB 881) "The Milky Way System" (subproject Z2),
hosted and co-funded by the J\"ulich Supercomputing Center (JSC). We
greatly appreciate the contributions of all these computing
allocations.  AAD, GSS and AVM acknowledge support through the
Sonderforschungsbereich SFB 881 “The Milky Way System” (subproject A1)
of the German Research Foundation (DFG).  The analysis made use of the
pynbody package \citep{Pontzen13}.
%
The authors acknowledge support from the MPG-CAS through the
partnership programme between the MPIA group lead by AVM and the PMO
group lead by XK.
LW acknowledges support of the MPG-CAS student
programme.
XK acknowledge the support from 973 program (No. 2015CB857003, 2013CB834900),
NSFC project No.11333008 and the ``Strategic Priority Research Program the Emergence
of Cosmological Structures'' of the CAS(No.XD09010000).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{}

%%AAAAAAAA

% Extended Hot Halos around Isolated Galaxies Observed in the ROSAT All-Sky Survey
\bibitem[Anderson et al.(2013)]{Anderson13} Anderson, M.~E., Bregman, J.~N., Dai, X.\ 2013, \apj, 762, 106

% Fundamental differences between SPH and grid methods
\bibitem[Agertz et al.(2007)]{Agertz07} Agertz, O., Moore, B., Stadel, J.\ 2007, \mnras, 380, 963

%%BBBBBBBB

%The Average Star Formation Histories of Galaxies in Dark Matter Halos
% from z = 0-8
\bibitem[Behroozi et al.(2013)]{Behroozi13} Behroozi, P.~S.,
  Wechsler, R.~H., \& Conroy, C.\ 2013, \apj, 770, 57

%A First Estimate of the Baryonic Mass Function of Galaxies
\bibitem[Bell et al.(2003)]{Bell03} Bell, E.~F., McIntosh, D.~H., Katz, N., Weinberg, M.~D.,\ 2003, \apj, 585, 117

% Multiscale Gaussian Random Fields and Their Application to Cosmological Simulations
%\bibitem[Bertschinger(2001)]{Bertschinger01} Bertschinger, E.\ 2001, 
%\apjs, 137, 1

% The Search for the Missing Baryons at Low Redshift
\bibitem[Bregman (2007)]{Bregman07}
Bregman, J.~N.\ 2007, ARAA, 45, 221

%% CCCCCCCC

%Where are the baryons
\bibitem[Cen \& Ostriker (1999)]{Cen09} 
Cen, R.~Y., Ostriker, J.~P.\ 1999, \apj, 514, 1

%% DDDDDDDD

%Dark halo response and the stellar initial mass function in early-type and late-type galaxies
\bibitem[Dutton et al.(2011)]{Dutton11} Dutton, A.~A., Conroy, 
  C., van den Bosch, F.~C., et al.\ 2011, \mnras, 416, 322

%The baryonic Tully-Fisher relation and galactic outflows
\bibitem[Dutton(2012)]{Dutton12} Dutton, A.~A.\ 2012,
  \mnras, 424, 3123

%Cold dark matter haloes in the Planck era: evolution of structural parameters for Einasto and NFW profiles
\bibitem[Dutton \& Macci{\`o}(2014)]{Dutton14} Dutton,
  A.~A., \& Macci{\`o}, A.~V.\ 2014, \mnras, 441, 3359

%% EEEEEEEEE

%% FFFFFFFFF

% The Cosmic Baryon Budget
\bibitem[Fukugita et al.(1998)]{Fukugita98} Fukugita, M., Hogan, C.~J., Peebles, P.~J.~F.\ 1998, \apj, 503, 518

%% GGGGGGGGG

%% HHHHHHHHH

%% JJJJJJJJJJJ

%% KKKKKKKKKKK

%A superbubble feedback model for galaxy simulations
\bibitem[Keller et al.(2014)]{Keller14} Keller, B.~W., Wadsley, 
  J., Benincasa, S.~M., \& Couchman, H.~M.~P.\ 2014, \mnras, 442, 3013

% Stellar mass -- halo mass relation and star formation efficiency in
% high-mass halos
\bibitem[Kravtsov et al.(2014)]{Kravtsov14} Kravtsov, A., 
Vikhlinin, A., \& Meshscheryakov, A.\ 2014, arXiv:1401.7329

%% LLLLLLLLL

%% MMMMMMMMM

% The Baryon Content of Cosmic Structures
\bibitem[McGaugh et al.(2010)]{McGaugh10} McGaugh, S.~S., 
Schombert, J.~M., de Blok, W.~J.~G., Zagursky, M.~J.\ 2010, \mnras,
708, 14

% Galactic star formation and accretion histories from matching galaxies to dark matter haloes
\bibitem[Moster et al.(2013)]{Moster13} Moster, B.~P., Naab, T., 
\& White, S.~D.~M.\ 2013, \mnras, 428, 3121

%% NNNNNNNNN

%% OOOOOOOO

%% PPPPPPPPP

%Planck 2013 results. XVI. Cosmological parameters
\bibitem[the Planck Collaboration et  al.(2014)]{Planck14}
  Planck Collaboration, Ade, P.~A.~R., Aghanim, N., et al.\ 2014,
  \aap, 571, AA16

% A Budget and Accounting of Metals at z ~ 0: Results from the COS-Halos Survey
\bibitem[Peeples et al.(2014)]{Peeples14} Peeples, M.~S., Werk, J.~K., Tumlinson, J., et al.\ 2014, \apj, 786, 54

% Dark MaGICC: the effect of dark energy on disc galaxy formation. Cosmology does matter
%\bibitem[Penzo et al.(2014)]{Penzo14} Penzo, C., Macci{\`o}, 
%  A.~V., Casarini, L., Stinson, G.~S., \& Wadsley, J.\ 2014, \mnras, 442, 176

% The baryon content of the universe
\bibitem[Persic \& Salucci(1992)]{Persic92} Persic, M., Salucci, P.\ 1992, \mnras, 258, 14

%pynbody: N-Body/SPH analysis for python
\bibitem[Pontzen et al.(2013)]{Pontzen13} Pontzen, A., Ro{\v s}kar, R., Stinson, G., \& Woods, R.\ 2013, Astrophysics Source Code Library, 1305.002

%% RRRRRRRRRRR

%Evolution of the Mass-Metallicity Relations in Passive and Star-forming Galaxies from SPH-cosmological Simulations

%Multiphase smoothed-particle hydrodynamics
%\bibitem[Ritchie \& Thomas(2001)]{Ritchie01} Ritchie, B.~W.,
%  \& Thomas, P.~A.\ 2001, \mnras, 323, 743

%% SSSSSSSSSSSS

% The enrichment of the intergalactic medium with adiabatic feedback - I. Metal cooling and metal diffusion
\bibitem[Shen et al.(2010)]{Shen10} Shen, S., Wadsley, J., 
\& Stinson, G.\ 2010, \mnras, 407, 1581

% The Baryon Census in a Multiphase Intergalactic Medium: 30% of the Baryons May Still be Missing
\bibitem[Shull et al.(2012)]{Shull12}
Shull, J.~M., Smith, B.~D., Danforth, C.~W.\ 2012, \apj, 759, 23

%Making Galaxies In a Cosmological Context: the need for early stellar feedback
\bibitem[Stinson et al.(2013)]{Stinson13} Stinson, G.~S., Brook, 
C., Macci{\`o}, A.~V., et al.\ 2013, \mnras, 428, 129

%% TTTTTTTTTTT

% Not Dead Yet: Cool Circumgalactic Gas in the Halos of Early-type Galaxies
\bibitem[Thom et al.(2012)]{Thom12}
Thom, C., Tumlinson, J., Werk, J.~K.\ 2012, \apjl, 758, L41

% The Large, Oxygen-Rich Halos of Star-Forming Galaxies Are a Major Reservoir
% of Galactic Metals
\bibitem[Tumlinson et al.(2011)]{Tumlinson11} Tumlinson, J., Thom, C., Werk, J., et al.\ 2011, Science, 334, 948

% The COS-Halos Survey: Rationale, Design and a Census of Circumgalactic Neutral Hydrogen
\bibitem[Tumlinson et al.(2013)]{Tumlinson13} Tumlinson, J., Thom, C., Werk, J., et al.\ 2013, \apj, 777, 59

%% VVVVVVVVVVVV

%% WWWWWWWWWWWWWW

%Gasoline: a flexible, parallel implementation of TreeSPH
\bibitem[Wadsley et al.(2004)]{Wadsley04} Wadsley, J.~W., Stadel, 
J., \& Quinn, T.\ 2004, \na, 9, 137

%On the treatment of entropy mixing in numerical cosmology
\bibitem[Wadsley et al.(2008)]{Wadsley08} Wadsley, J.~W., 
Veeravalli, G., \& Couchman, H.~M.~P.\ 2008, \mnras, 387, 427

  %NIHAO project I: Reproducing the inefficiency of galaxy formation across cosmic time with a large sample of cosmological hydrodynamical simulations
\bibitem[Wang et al.(2015)]{Wang15} Wang, L., Dutton, A.~A.,  Stinson, G.~S., et al.\ 2015, \mnras, 454, 83

% The COS-Halos Survey: Keck LRIS and Magellan MagE Optical Spectroscopy
\bibitem[Werk et al.(2012)]{Werk12} Werk, J.~k., Prochaska, J.~X., Thom, C., et al.\ 2012, \apjs, 198, 3

% The COS-Halos Survey: An Empirical Description of Metal-line Absorption in the Low-redshift Circumgalactic Medium
\bibitem[Werk et al.(2013)]{Werk13} Werk, J.~k., Prochaska, J.~X., Thom, C., et al.\ 2013, \apjs, 204, 17

%The COS-Halos Survey: Physical Conditions and Baryonic Mass in the Low-redshift Circumgalactic Medium
\bibitem[Werk et al.(2014)]{Werk14} Werk, J.~k., Prochaska, J.~X., Thom, C., et al.\ 2014, \apj, 792, 8

%% YYYYYYYYYYYY

%% ZZZZZZZZZZZZZ

\end{thebibliography}

\label{lastpage}
\end{document}

### 2016-04-19 ms_nihao_budget.tex
add gas fraction in different phases figure and remove table 1

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% SECTION 3 RESULTS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Results}
+%\label{sec:results}
+
+%We study the baryonic budget using the full set simulations of the NIHAO project.  
+%The large range of the mass covered by our simulations enables
+%us see the baryon fractions and mass profiles of different 
+%galaxies, depending on the halo mass and stellar content.
+
 %% FIGURE 1
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% SECTION 3 RESULTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Results}
-%\label{sec:results}
+%% FIGURE 2
+\begin{figure*}
+\centerline{
+  \psfig{figure=budgetpro.eps,width=0.99\textwidth}
+}
+\caption{Radial profile of the mass fraction of the gas in each phase
+         to total baryon mass in each radial bin 
+         at z=0 for all galaxies in NIHAO sample.
+         Each solid line is from one galaxy and color coded with
+         the halo mass.}
+\label{fig:corona}
+\end{figure*}
 
-%We study the baryonic budget using the full set simulations of the NIHAO project.  
-%The large range of the mass covered by our simulations enables
-%us see the baryon fractions and mass profiles of different 
-%galaxies, depending on the halo mass and stellar content.
-
-%% FIGURE 2
+%% FIGURE 3
 \begin{figure}
@@
 \end{eqnarray}
-The green shaded region indicates the scatter about the best fit line. These are 
-measured in four different mass ranges, and are  summarized in Table.~\ref{tab:sigma}.
-
-\begin{table}
-\caption{Scatters for best fit parameters for the total baryonic mass 
-fraction computed inside one virial radius, $R_{200}$,  as a function of halo mass $M_{200}$
-in different mass ranges.} 
-\begin{center}
-\begin{tabular}{lc}
-\hline
-Mass Range & $\sigma $ \\
-\hline
-$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$ & 0.151 \\
-$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$ & 0.236 \\
-$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$ & 0.125 \\
-$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$ & 0.0518 \\
-\hline
-\end{tabular}
-\label{tab:sigma}
-\end{center}
-\end{table}
+The green shaded region indicates the scatter about the best fit line,
+{\bf which are 0.151 for haloes with mass in the range of  
+$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
+halo mass in 
+$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
+0.125 for halo mass in
+$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
+and 0.0518 for halo mass in
+$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.}
 
@@
 \citep[e.g.,][]{Dutton12}.
+
+\subsection{Mass budget of the corona}
+\label{sec:corona}
+
+In Fig.~\ref{fig:corona}, we present the radial distribution of 
+gas in different phases normalized to the
 
@@
 
-%% FIGURE 3
+%% FIGURE 4
 \begin{figure}
@@
 
-%% TABLE 2
+%% TABLE 1
 \begin{table*}

### 2016-04-22 ms_nihao_budget.tex
revised budget paper

@@
   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing $\sim
-  90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
+  90\%$ of their baryons. 
+  {\bf Cool gas dominates the fraction of total baryons surrounding
+  galaxies up to several times of virial radius, in which most of
+  them are well outside of virial radius.}
+   More massive haloes ($\Mhalo\sim
   10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
@@
 discrepancy is referred to as the ``missing baryon problem''.
-Recent advances in the detection of gas in the circum
-galactic medium (CGM) have come from the COS survey \citep{Tumlinson11,
+{\bf Several theoretical research with cosmological simulation
+have constrained the phase status and cosmological enviroments of
+the potential reservior to hide the missing baryons 
+\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.}
+
+{\bf The circum galactic medium (CGM) is one major potential 
+reservior of missing baryons in halo scale.}
+Recent advances in the detection of  gas in the CGM have come 
+from the COS survey \citep{Tumlinson11,
   Tumlinson13, Thom12,  Werk12, Werk13}.  On the scale of Milky Way
@@
 be extended to a wider range of halo masses.
+{\bf To understand the physical properties of CGM and the origins 
+of components in each phase has been shown to be able to test the
+impact of feedback models \citep{Sharma12,Marasco13}.
+\citet{Dave09} predicted galactic halo baryon fractions of
+galaxies with halo mass range from $10^{11} \Msun$ to
+$10^{13} \Msun$
+cosmological hydrodynamic simulations with a well-constrained
+model for galactic outflow, which found that, without outflow
+model, the baryon fraction is roughly the cosmic baryonic 
+fraction, but with outflow in the simulation, the baryon fraction
+is increasingly suppressed in haloes to lower mass. By comparing
+results at z=3 and z=0, they showed the large haloes remove their
+baryons at early epoch while small haloes lose baryons more
+recently due to wind material takes longer to return to low-mass
+galaxies than high-mass galaxies.
+\citet{Sokolowska16} studied halo gas of three Milky way-sized 
+galaxies using cosmological zoom-in simulations. They found that
+most of missing baryons actually resides in warm-hot and hot gas
+which contribute to 80\% of the total gas reservior. 
+The recovered baryon fraction within 3 virial radii is 90\% and 
+can solve the missing baryon problem.
+The warm-hot medium is sensitive to the feedback model so that
+the reliable spatial mapping of warm-hot medium will provide 
+a stringent test for feedback models.}
 
@@
 
+%% FIGURE 4
+\begin{figure}
+\centerline{
+  \psfig{figure=missing_vr.eps,width=0.5\textwidth}
+}
+\caption{Baryon radius as function of total mass within virial 
+         radius. The points are color coded by the ratio 
+         between baryon radius to virial radius of each galaxy.}
+\label{fig:missvr}
+\end{figure}
+
+%% FIGURE 5
+\begin{figure*}
+\centerline{
+  \psfig{figure=budget_inout.eps,width=0.99\textwidth}
+}
+\caption{Mass fraction of gas mass in four phases to the fiducial
+         baryonic mass within virial radius. The blue points are
+         mass fraction for the gas inside virial radius and the 
+         red points are gas between virial radius and baryon
+         radius.}
+\label{fig:inout}
+\end{figure*}
+
 \section{Baryon budget}
@@
 M_{\rm b} \equiv M_{\rm b}(R_{200})= \frac{f_{\rm b}}{1-f_{\rm b}}M_{\rm dm}(R_{200}) 
+\label{equ:mb}
 \end{equation}
@@
 
-In Fig.~\ref{fig:corona}, we present the radial distribution of 
-gas in different phases normalized to the
+{\bf In Fig.~\ref{fig:corona}, we present the radial distribution of 
+gas in different phases normalized to the total baryon mass in
+corresponding radial bins at z=0.
+All simulations share a common attribute.
+The cold gas (T$< 10^4$ K) in corona mostly locates 
+in very center region 
+($R < 0.5 R_{\rm vir}$) where most stars in galaxies form.
+The cool ($10^4$K $<$ T $<$ $10^5$K) and 
+warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas expand to large 
+distance contrastly,
+the fractions keep constant till 2 times $R_{\rm vir}$.
+The hot gas (T$>10^7$K) is minority in corona for 
+all galaxies in NIHAO
+sample, the maximum of the fraction of hot gas is less
+than 5\%.}
+
+{\bf Despite these similarities, we find considerably high proportion
+of cool gas for lower mass galaxies (M$_{\rm tot} < 10^{11} \Msun$)
+in the whole corona region.
+For higher mass galaxies, warm-hot gas dominates the corona 
+which signals higher efficiency  of feedback.
+Even beyond virial radius, the cool and warm-hot gas has
+similar features as the gas within virial radius which reveals
+the gas surrounding galaxies within large distance is the major
+reservior of baryons.}
 
@@
 
-%% FIGURE 4
+{\bf To find out how far the baryons escape, we measured the baryon 
+radius within which the total baryon mass equals to the fiducial
+baryonic mass defined by Equ.~\ref{equ:mb}.
+Fig.~\ref{fig:missvr} illustrates the baryon radius of each galaxy
+as function of the total mass within virial mass.
+We find the baryon radius increases as the total mass goes higher
+generally.
+In the whole mass range, The baryon radii normalized by 
+corresponding virial radii span a similar range
+which are from larger than virial radius to more than 5 times
+virial radius, except there are three galaxies with baryon
+radii larger than 8 times virial radius. 
+It shows that the normalized distance where the baryons inside
+virial radius can reach is not sensitive to the halo masses.}
+
+{\bf In Fig.~\ref{fig:inout}, we calculate the fractions of 
+these four kinds of gas inside virial radius and between 
+virial radius and baryon radius. The upper-left panel shows the 
+fractions of cold gas. The fractions of cold gas between
+virial radius and baryon radius of
+galaxies with halo masses in the range between $10^{9} \Msun$ to 
+$10^{10} \Msun$ are greater than 80\%. As the halo mass increase,
+this fractions go down dramatically, in the mass range between
+$10^{10} \Msun$ and $10^{11} \Msun$ the fractions are less than 
+20\% for most of galaxies and the fractions of galaxies with halo
+mass above $10^{11} \Msun$ are almost 0. 
+For the cold gas inside virial radius, the fractions increase
+gradually as halo masses increase and the maximum fraction is
+about 20\% with halo mass at $10^{12} \Msun$.
+The upper-right panel is about the fractions of cool gas. 
+The fractions of cool gas in region outside of virial radius 
+increase from 0 at halo masses are $10^9 \Msun$ to 80\% at halo 
+masses are around $10^{10} \Msun$ to $10^{11} \Msun$, then 
+decrease in higher mass range and reach 0 again at halo masses
+are $10^{12} \Msun$. The cool gas insdie virial radius shares 
+a similar trend but the maximum fraction is about 40\% at 
+halo masses are $10^{11} \Msun$.
+The fractions for warm-hot gas are shown in the lower-left panel,
+the trends of the gas inside and outside gas are quite similar
+which increase as the halo masses increase monotonically and whose 
+maximum values are only 20\%.
+The hot gas shown in the lower-right panel is absolutely minority,
+the fraction of gas inside baryon radius is almost 0 in the 
+whole halo mass range.
+We thus conclude that, for the galaxies with halo mass 
+below $10^{11}$, the majority of baryons associated with the
+halo mass within virial radius are in the cold and cool phases, 
+meanwhile are well outside of virial radius, for the gas inside
+virial radius, the majority is cool gas for the galaxies with
+halo masses are $10^{11} \Msun$ and when halo masses are higher
+than $10^{11} \Msun$ the fractions of cold gas, cool gas and 
+warm-hot gas are comparable.}
+
+%% FIGURE 6
 \begin{figure}
@@
 total gas fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the
-latter option.  As the CGM of lower mass galaxies will soon be observed ,
+latter option.  
+{\bf However, \citet{Stern16} developed a new method to constrain the
+physical condtions in the cool CGM from measurements of ionic 
+columns denisities. This new method combined the information
+available from different during the photoionization modeling,
+and was applied to the COS-HALOs data, 
+yielding a total cool CGM mass within the virial radius
+of $1.3\times10^{10}\Msun$ which is shown by the green hashed
+bar in Fig~\ref{fig:budget} and have good agreement with
+our prediction.
+As the Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the
+cool gas is the most important component in CGM so that
+the more correct knowledge about physical properties of CGM are
+necessary to understand the role the CGM on galaxy formation
+better.}
+As the CGM of lower mass galaxies will soon be observed ,
 Table~\ref{tab:comperison} lists information about CGM
@@
 
+\item {\bf Cold gas in most of galaxies (except several low mass
+      galaxies with low SFR) locates within 0.5 times virial 
+      radius. The cool gas dominates the corona at low mass range
+      end and the fraction of warm-hot gas increase with 
+      the increasing of halo mass and become majority at high
+      mass end.}
+
 \item The missing baryons in all haloes are beyond 2 virial radii.
+
+\item {\bf Cool gas is major component in total baryons 
+      whose mass is same as the fiducial baryonic mass of 
+      total dark matter mass inside virial radius. Most of the
+      cool gas in these baryons locates out of the virial radius.}
 
@@
 \item For the highest mass haloes in our study $\sim 10^{12}\Msun$ 
-      our simulations are consistent with the observed fractions of stars, 
-      cold gas, warm and hot gas. However, we underpredict 
-      the cool ($10^4 < T < 10^5 K$) gas with $f_{\rm cool}=0.11\pm0.06$ 
-      vs 0.28-0.48 observed.
+      our simulations are consistent with the observed 
+      fractions of stars, 
+      cold gas, warm and hot gas.
 
-\item This discrepancy may indicate that our feedback model pushes the 
+\item We underpredict 
+      the cool ($10^4 < T < 10^5 K$) gas 
+      with $f_{\rm cool}=0.11\pm0.06$ 
+      vs 0.28-0.48 observed of COS-HALOs.
+      {\bf \citet{Stern16} employed new method which have
+      a tight constraint on CGM properties shows a 
+      similar result as we predict.
+      To solve this discrepancy may be helpful to answer
+      if current feedback model pushes the 
       gas too far, or puts gas in the wrong phases, 
-      and can be resolved with future observations. 
-      Since we match the overall gas fraction we think that  
-      there might be some problem in mixing the gas temperature.
+      and can be resolved with future observations.}
+
 \end{itemize}
@@
 
+% Missing Halo Baryons and Galactic Outflows
+\bibitem[Dave{\'e} (2009)]{Dave09} Dav{\'e}, R.\ 2009, ASPC, 419, 347D
+
+% The intergalactic medium over the last 10 billion years - I. Lya absorption and physical conditions
+\bibitem[Dav{\'e} et al.(2010)]{Dave10} Dav{\'e}, R., Oppenheimer, B.~D., Katz, N., et al.\ 2010, \mnras, 408, 2051
+
 %Dark halo response and the stellar initial mass function in early-type and late-type galaxies
@@
 
+% Large-scale mass distribution in the Illustris simulation
+\bibitem[Haider et al.(2016)]{Haider16}
+Haider, M., Steinhauser, D., Vogelsberger, M., et al.\ 2016, \mnras, 457, 3024
+
+% Distributions of the Baryon Fraction on Large Scales in the Universe
+\bibitem[He et al.(2005)]{He05}
+He, P., Feng, L.~L., Fang, L.~Z.\ 2005, \apj, 623, 601
+
 %% JJJJJJJJJJJ
@@
 %% MMMMMMMMM
+
+% On the origin of the warm-hot absorbers in the Milky Way's halo
+\bibitem[Marasco et al.(2013)]{Marasco13} 
+Marasco, A., Marinacci, F., Fraternali, F.\ 2013, \mnras, 433, 1634
 
@@
 
+% On the structure of hot gas in haloes: implications for the LX-TX relation and missing baryons
+\bibitem[Sharma et al.(2012)]{Sharma12}
+Sharma, P., McCourt, M., Parrish, I.~J., Quataert, E.\ 2012, \mnras, 427, 1219
+
 % The Baryon Census in a Multiphase Intergalactic Medium: 30% of the Baryons May Still be Missing
@@
 Shull, J.~M., Smith, B.~D., Danforth, C.~W.\ 2012, \apj, 759, 23
+
+% Diffuse Coronae in Cosmological Simulations of Milky Way-sized Galaxies
+\bibitem[Sokolowska et al.(2016)]{Sokolowska16}
+Sokolowska, A., Mayer, L., Babul, A., Madau, P., Shen, S.\ 2016, \apj, 819, 21
+
+% A Universal Density Structure for Circum-Galactic Gas
+\bibitem[Stern et al.(2016)]{Stern16} 
+Stern, J., Hennawi, J.~F., Prochaska, J.~X., Werk, J.~K.\ 2016, arXiv:1604.02168
 
@@
 
+% The Temperature Structure of the Warm-Hot Intergalactic Medium
+\bibitem[Yoshida et al.(2005)]{Yoshida05} 
+Yoshida, N., Furlanetto, S.~R., Hernquist, L.\ 2005, \apj, 618L, 91
+
 %% ZZZZZZZZZZZZZ
+
+% Dynamical effect of the turbulence of the intergalactic medium on the baryon fraction distribution
+\bibitem[Zhu et al.(2011)]{Zhu11} Zhu, W., Feng, L.~L., Fang, L.~Z.\ 2011, \mnras, 415, 1093
 

### 2016-05-30 ms_nihao_budget.tex
Aaron's edition

--- 2016-04-19 ms_nihao_budget.tex
@@
 \def \Mvir {\ifmmode M_{\rm  vir} \else $M_{\rm  vir}$ \fi}  
-\def \Mhalo {\ifmmode M_{\rm tot} \else $M_{\rm  tot}$ \fi}  
+\def \Mhalo {\ifmmode M_{200} \else $M_{200}$ \fi}  
 \def \Nvir {\ifmmode N_{\rm  vir} \else $N_{\rm  vir}$ \fi}  
@@
 \def \Mbar {\ifmmode M_{\rm bar} \else $M_{\rm bar}$ \fi}
+\def \Rbar {\ifmmode R_{\rm bar} \else $R_{\rm bar}$ \fi}
 
@@
   fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
-  find that for all of our haloes, the missing mass is not just outside 
-  the virial radius $\Rvir$, it has been relocated past 2$\Rvir$.  
-  Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing $\sim
-  90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
+  find that all of our haloes {\bf are missing baryons. The missing
+    mass been relocated past 2 virial radii, and is dominated by cool gas.}
+   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
+  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
   10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
   30\%$ missing, consistent with observational estimates.
+
 %  Finally we show that the baryonic budget of most massive 
@@
 gravitating mass is measured to be $f_{\rm b}\equiv \Omega_{\rm
-  b}/\Omega_{\rm m}\simeq 0.16$ (The Planck Collaboration 2014).
+  b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
 However, the cold baryonic mass density implied by several galaxy baryon
-estimates is only 3-8\% of the big bang nucleosynthesis expection
+estimates is only 3-8\% of the big bang nucleosynthesis expectation
 \citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
@@
 discrepancy is referred to as the ``missing baryon problem''.
-Recent advances in the detection of gas in the circum
-galactic medium (CGM) have come from the COS survey \citep{Tumlinson11,
+{\bf Several theoretical studies with cosmological simulations
+have constrained the phase and cosmological environments of
+the potential reservoirs of the missing baryons 
+\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.}
+
+{\bf The circum galactic medium (CGM) is a major potential  reservoir
+  of the missing baryons.}  Recent advances in the detection of  gas
+in the CGM have come  from the COS survey \citep{Tumlinson11,
   Tumlinson13, Thom12,  Werk12, Werk13}.  On the scale of Milky Way
@@
 be extended to a wider range of halo masses.
+%{\bf ??? To understand
+%  the physical properties of the CGM and the origins of components in
+%  each phase has been shown to be able to test the impact of feedback
+%  models \citep{Sharma12,Marasco13}???
+  {\bf The physical properties of the CGM has been shown to be able to
+    test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
+    predicted galactic halo baryon fractions of galaxies with halo
+    masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
+    cosmological hydrodynamical simulations with a well-constrained
+    model for galactic outflows.  They found that, without the outflow
+    model, the baryon fraction inside the virial radius is roughly the
+    cosmic baryonic fraction, but with the outflow model, the baryon
+    fraction is increasingly suppressed in lower mass haloes.  By
+    comparing results at $z=3$ and $z=0$, they showed that large
+    haloes remove their baryons at early times while small haloes lose
+    baryons more recently due to the wind material taking longer to
+    return to low-mass galaxies than high-mass galaxies.
+%  
+  \citet{Sokolowska16} studied the halo gas of three Milky way-sized
+  galaxies using cosmological zoom-in simulations. They found that
+  most of missing baryons actually resides in warm-hot and hot gas
+  which contribute to 80\% of the total gas reservoir.  The recovered
+  baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
+  is sensitive to the feedback model so that a reliable spatial
+  mapping of the warm-hot medium will provide  a stringent test for
+  feedback models.}
 
@@
 relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
-stellar mass relation at $z\sim 0$ (Stinson \etal 2015).  Therefore,
+stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore,
 the simulations make plausible predictions for the mass fractions and
@@
 cosmic baryonic fraction, but the missing fraction is strongly mass
-dependent.
+dependent.  {\bf Mention Gutcke et al. 2016}
 
@@
 }
-\caption{Fractional baryon content of our NIHAO simulations 
-  as a function of halo
-  mass. The green points show the ratio between the baryonic mass
-  (stars + gas) inside the virial radius and the total baryonic mass
-  associated with the dark matter halo and the green lines are best
-  fitting lines. The blue points show the
-  corresponding fraction for the stars. The solid green line and
-  shaded region shows a double power-law fit, together with the
+\caption{Fractional baryon content of our NIHAO simulations  as a
+  function of halo mass. The green points show the ratio between the
+  baryonic mass (stars + gas) inside the virial radius and the total
+  baryonic mass associated with the dark matter halo. The blue points
+  show the corresponding fraction for the stars. The solid green line
+  and shaded region shows a double power-law fit, together with the
   1$\sigma$ scatter. For the stellar mass fraction we show several
@@
          Each solid line is from one galaxy and color coded with
-         the halo mass.}
+         the halo mass. {\bf tickmarks overlap. fix. use $R_{200}$ for virial radius}}
 \label{fig:corona}
 \end{figure*}
-
-%% FIGURE 3
-\begin{figure}
-\centerline{
-  \psfig{figure=ratioprofile_v4.eps,width=0.5\textwidth}
-}
-\caption{Baryon distribution of each galaxy from NIHAO simulations.
-  A comparison of how the baryons distribute in the halo with 
-  different masses. 
-  The lines are color coded by their halo mass, which show a clear
-  trend that the more massive halo preserve more baryons alone
-  the radius.}
-\label{fig:rps}
-\end{figure}
 
@@
 Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
-component inside the virial radius 
-to the fiducial baryonic mass for the most massive galaxy in
-each zoom-in region. We present the fractions of total stellar mass
-(blue points), and the total baryonic mass
-including stellar mass plus gas mass (green points).
-For the stellar mass fraction we also show the relations from the halo abundance 
-matching \citep{Moster13, Behroozi13, Kravtsov14}.
-The grey area is the one sigma scatter around the mean value 
-from \citet{Kravtsov14}.
+component inside the virial radius  to the fiducial baryonic mass for
+the most massive galaxy in each zoom-in region. We present the
+fractions of total stellar mass (blue points), and the total baryonic
+mass including stellar mass plus gas mass (green points).  For the
+stellar mass fraction we also show the relations from the halo
+abundance  matching \citep{Moster13, Behroozi13, Kravtsov14}.  The
+grey area is the one sigma scatter around the mean value  from
+\citet{Kravtsov14}.
 
-We tried to capture the behaviour of the baryonic mass fraction as a 
+We tried to capture the behavior of the baryonic mass fraction as a 
 function of the halo mass using a double power law formula:
@@
 The green shaded region indicates the scatter about the best fit line,
-{\bf which are 0.151 for haloes with mass in the range of  
+{\bf which is 0.151 for haloes with mass in the range of  
 $3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
@@
 components is the slope, with the baryonic mass fraction having a
-shallower slope than the stellar mass fraction.  This is because in low mass haloes
-($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in the form of
-gas, while in the highest mass haloes we study ($\Mhalo\sim
-10^{12}\Msun$) there are roughly equal amounts of stars and gas.
+shallower slope than the stellar mass fraction.  This is because in
+low mass haloes ($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in
+the form of gas, while in the highest mass haloes we study
+($\Mhalo\sim 10^{12}\Msun$) there are roughly equal amounts of stars
+and gas.
 
-Fig.~\ref{fig:budget} shows that all haloes in our study contain
-less than the universal fraction of baryons. The
-upper panel uses a linear y-axis scale, which highlights the large
-amount of baryons that are missing, especially in low mass haloes. The
-logarithmic scale in the lower panel highlights the power-law nature of the relatons.
+Fig.~\ref{fig:budget} shows that all haloes in our study contain less
+than the universal fraction of baryons. The upper panel uses a linear
+y-axis scale, which highlights the large amount of baryons that are
+missing, especially in low mass haloes. The logarithmic scale in the
+lower panel highlights the power-law nature of the relations.
 
@@
 
-In Fig.~\ref{fig:corona}, we present the radial distribution of 
-gas in different phases normalized to the
+{\bf In Fig.~\ref{fig:corona}, we present the radial distribution of
+  gas in different phases at $z=0$, normalized to the total baryon
+  mass profile, such that for a given halo the four phases add up to
+  unity.  All simulations share a common attribute.  The cold gas (T$<
+  10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
+  where most stars in galaxies form.  In contrast, the cool ($10^4$K
+  $<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
+  located at large distances with roughly constant fractions up to 2
+  times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
+  for all galaxies in the NIHAO sample, with the maximum hot gas
+  fraction at any radius being  less than 5\%.}
+
+{\bf Despite these similarities, we find a considerably higher proportion
+  of cool gas in lower mass galaxies (M$_{\rm tot} < 10^{11} \Msun$)
+  in the whole corona region.  For higher mass galaxies, warm-hot gas
+  dominates the corona  which signals higher efficiency  of feedback.
+  Even beyond the virial radius, the cool and warm-hot gas has similar
+  features as the gas within virial radius which reveals the gas
+  surrounding galaxies within large distance is the major reservoir of
+  baryons.}
+
+%% FIGURE 3
+\begin{figure}
+\centerline{
+  \psfig{figure=ratioprofile_v4.eps,width=0.5\textwidth}
+}
+\caption{Baryon distribution of each galaxy from NIHAO simulations. 
+ The lines are color coded by their halo mass, which shows a
+  clear trend that the more massive haloes preserve more baryons at
+  all radii.}
+\label{fig:rps}
+\end{figure}
+
+%% FIGURE 4
+\begin{figure}
+\centerline{
+  \psfig{figure=missing_vr.eps,width=0.5\textwidth}
+}
+\caption{Baryon radius as function of total virial mass.
+         The points are color coded by the ratio 
+         between baryon radius and the virial radius of each galaxy.}
+\label{fig:missvr}
+\end{figure}
+
+%% FIGURE 5
+\begin{figure*}
+\centerline{
+  \psfig{figure=budget_inout.eps,width=0.99\textwidth}
+}
+\caption{Mass fraction of gas in four phases (relative to the fiducial
+  baryonic mass within virial radius). The blue and red points are for
+  gas  inside and outside the virial radius, respectively. Cool gas is
+  the dominant component of the CGM in NIHAO simulations.}
+\label{fig:inout}
+\end{figure*}
 
@@
 
-%% FIGURE 4
+{\bf To estimate how far the baryons escape, we measured the radius,
+  $\Rbar$, within which the total baryon mass equals to the fiducial
+  baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
+  the true extent of the missing baryons since the baryon mass
+  includes gas and stars that belong to nearby lower mass haloes.
+  Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
+  function of the virial mass.  We find the baryon radius generally
+  increases with virial mass. But when normalized by the virial
+  radius, the distance baryons are ejected to span a similar range of radii
+  $\Rbar/R_{200}\sim 2-6$.}
+
+{\bf In Fig.~\ref{fig:inout}, we calculate the fractions of gas (in each phase)
+inside the virial radius (blue points) and between 
+the virial and baryon radii (red points).
+%
+The upper-left panel shows the  fractions of cold gas. The fractions
+of cold gas between the virial radius and baryon radius of galaxies with
+halo masses in the range between $10^{9} \Msun$ to  $10^{10} \Msun$
+are greater than 80\%. As the halo mass increases, this fraction goes
+down dramatically, in the mass range between $10^{10} \Msun$ and
+$10^{11} \Msun$ the fractions are less than  20\% for most of galaxies
+and the fractions for galaxies with halo mass above $10^{11} \Msun$ are
+almost 0.  For the cold gas inside the virial radius, the fractions
+increase gradually as halo mass increases and the maximum fraction is
+about 20\% with at a halo mass of $10^{12} \Msun$.
+%
+The upper-right panel shows the fractions of cool gas.  The fractions
+of cool gas in region outside of virial radius  increase from 0 at
+halo masses are $10^9 \Msun$ to 80\% at halo  masses are around
+$10^{10} \Msun$ to $10^{11} \Msun$, then  decrease in higher mass
+range and reach 0 again at halo masses are $10^{12} \Msun$. The cool
+gas inside virial radius shares  a similar trend but the maximum
+fraction is about 40\% at  halo masses are $10^{11} \Msun$.
+%
+The fractions for warm-hot gas are shown in the lower-left panel.
+The trends of the gas inside and outside gas are quite similar
+which increase as the halo masses increase monotonically and whose 
+maximum values are only 20\%.
+%
+The hot gas shown in the lower-right panel and is negligible both
+inside and outside the virial radius across the whole mass range we
+study.
+%
+We thus conclude that, for galaxies with halo mass 
+below $10^{11}$, the majority of baryons associated with the
+dark matter halo are in the cold and cool phases, 
+and are located well outside of virial radius. For the gas inside
+virial radius, the majority is cool gas for the galaxies with
+halo masses are $10^{11} \Msun$ and when halo masses are higher
+than $10^{11} \Msun$ the fractions of cold gas, cool gas and 
+warm-hot gas are comparable.}
+
+%% FIGURE 6
 \begin{figure}
@@
 }
-\caption{Baryonic budget (the fraction of different components) 
-  of $3.5\times 10^{11} < M_{200}/\Msun <
-  3.5 \times 10^{12}$ NIHAO galaxies (blue points 
+\caption{Baryonic budget 
+  of NIHAO haloes of mass $3.5\times 10^{11} < M_{200}/\Msun <
+  3.5 \times 10^{12}$ (blue points 
   with 1$\sigma$ error bars) compared with observations of 
-  M$_{200}$ = 10$^{12.2}$ $\Msun$ galaxies (shaded regions)
+  $M_{200} \sim 10^{12}\Msun$ haloes (shaded regions)
   }
@@
 \begin{table*}
-\caption{The baryonic budget parameters for galaxies in NIHAO sample
-  in different mass bins. We refer to gas in the temperature range  T
+  \caption{The baryonic budget parameters for NIHAO galaxies
+    in different halo  mass bins. We refer to gas in the temperature range  T
   $<$ $10^4$ K as cold; $10^4$ K $\leqslant$ T $<$ $10^5$ K as cool;
@@
 \end{tabular}
-\label{tab:comperison}
+\label{tab:comparison}
 \end{center}
@@
 Since the CGM is too diffuse to create emission lines, it must be
-observed using quasar absorption lines.
-The COS-HALOs survey is filling in details about the $z \sim 0$
-CGM \citep{Peeples14, Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.
-For the CGM of low-redshift $L^*$ galaxies, \citet{Tumlinson13} and 
-\citet{Peeples14} constrain the mass of  the
-warm-hot CGM ($T \sim 10^{5-7}$), \citet{Werk14} provides a strict
-lower limit to the mass of cool material ($T \sim 10^{4-5}$) in the
-CGM of these galaxies.  In a study using X-rays, 
-\citet{Anderson13} place a
-constraints on the mass of  hot gas ($T > 10^7$) residing in the
-extended hot halos.
+observed using quasar absorption lines.  The COS-HALOs survey is
+filling in details about the $z \sim 0$ CGM \citep{Peeples14,
+  Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.  For the CGM of
+low-redshift $\sim L^*$ galaxies ($\Mstar\sim 10^{10.5}\Msun$),
+\citet{Tumlinson13} and \citet{Peeples14} constrain the mass of  the
+warm-hot CGM ($T \sim 10^{5-7}$K), \citet{Werk14} provides a strict
+lower limit to the mass of cool material ($T \sim 10^{4-5}$K) in the
+CGM of these galaxies.  In a study using X-rays,  \citet{Anderson13}
+place a constraints on the mass of  hot gas ($T > 10^7$K) residing in
+the extended hot halos.
 
@@
 In this plot \citet{Werk14} provides observational constraints for
-CGM gas mass that are shown as the shaded bars.
-The stellar  mass range comes from
-halo abundance matching as described in \citet{Kravtsov14}.  
-The cold disk gas mass comes from from \citet{Dutton11}.
+CGM gas mass that are shown as the shaded bars.  The stellar  mass
+range comes from halo abundance matching as described in
+\citet{Kravtsov14}.   The cold disk gas mass comes from from
+\citet{Dutton11}.
 
-The observations and the simulations match well in every phase
-outside of the cool CGM gas, where the observations find $3\times$
-the mass that simulations predict.  If the observations are correct,
-the simulations have either ejected too far gas that could be cool, or 
-they have created a CGM with the wrong mix of gas temperatures. The
-total gas fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the
-latter option.  As the CGM of lower mass galaxies will soon be observed ,
-Table~\ref{tab:comperison} lists information about CGM
+The observations and the simulations match well in every phase {\bf
+  except} the cool CGM gas, where the observations find $3\times$ the
+mass that simulations predict.  If the observations are correct, the
+simulations have either ejected {\bf cool gas too far}, or  they have
+created a CGM with the wrong mix of gas temperatures. The total gas
+fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
+option.   {\bf However, \citet{Stern16} developed a new method to
+  constrain the physical conditions in the cool CGM from measurements
+  of ionic  columns densities. This new method combines the
+  information available from different ??? during the photoionization
+  modeling, and was applied to the COS-HALOs data,  yielding a total
+  cool CGM mass within the virial radius of $1.3\times10^{10}\Msun$
+  which is shown by the green hashed bar in Fig~\ref{fig:budget} and
+  is in good agreement with our prediction.  As the
+  Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
+  the most important component in CGM so that the more accurate
+  knowledge of the physical properties of CGM are necessary to better
+  understand the role of the CGM in galaxy formation.}
+%
+As the CGM of lower mass galaxies will soon be observed,
+Table~\ref{tab:comparison} lists information about CGM
 mass fractions of the different components of gas in haloes down to a
@@
 \item All of the NIHAO haloes have a lower baryon to dark matter ratio, 
-      inside the viriral radius, than the cosmic baryon fraction.
+      inside the virial radius, than the cosmic baryon fraction.
+
+\item {\bf Cold gas ($T<10^4$K) is mostly restricted to be within
+      0.2 virial radii.  The cool gas ($10^4 < T < 10^5$K) dominates
+      the corona at low masses ($M_{200}\lta 3\times 10^{11} \Msun$)
+      while the warm-hot gas ($10^5 < T < 10^7$K) dominates at high
+      masses ($M_{200}\gta 3\times 10^{11} \Msun$).}
 
 \item The missing baryons in all haloes are beyond 2 virial radii.
+
+\item {\bf ??? I don't understand this sentence ?? Cool gas is a major
+  component in total baryons  whose mass is same as the fiducial
+  baryonic mass of  total dark matter mass inside virial radius. Most
+  of the cool gas in these baryons locates out of the virial radius.}
 
@@
 
-\item For the highest mass haloes in our study $\sim 10^{12}\Msun$ 
-      our simulations are consistent with the observed fractions of stars, 
-      cold gas, warm and hot gas. However, we underpredict 
-      the cool ($10^4 < T < 10^5 K$) gas with $f_{\rm cool}=0.11\pm0.06$ 
-      vs 0.28-0.48 observed.
+\item For the highest mass haloes in our study $\sim 10^{12}\Msun$ our
+      simulations are consistent with the observed  fractions of stars,
+      cold gas, warm and hot gas.
 
-\item This discrepancy may indicate that our feedback model pushes the 
-      gas too far, or puts gas in the wrong phases, 
-      and can be resolved with future observations. 
-      Since we match the overall gas fraction we think that  
-      there might be some problem in mixing the gas temperature.
+\item {\bf For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
+      which is significantly lower than the observations from COS-HALOs
+      ($f_{\rm cool}=0.28-0.48$), but is in excellent agreement with the
+      analysis of \citet{Stern16}.}
+
 \end{itemize}
@@
 their contribution, this paper would have been impossible.
+%
 The simulations were performed on the {\sc theo} cluster of the
@@
 greatly appreciate the contributions of all these computing
-allocations.  AAD, GSS and AVM acknowledge support through the
+allocations.
+%
+AAD, GSS and AVM acknowledge support through the
 Sonderforschungsbereich SFB 881 “The Milky Way System” (subproject A1)
@@
 group lead by XK.
-LW acknowledges support of the MPG-CAS student
-programme.
-XK acknowledge the support from 973 program (No. 2015CB857003, 2013CB834900),
-NSFC project No.11333008 and the ``Strategic Priority Research Program the Emergence
-of Cosmological Structures'' of the CAS(No.XD09010000).
+%
+LW acknowledges support of the MPG-CAS student programme.
+%
+XK acknowledge the support from 973 program (No. 2015CB857003,
+2013CB834900), NSFC project No.11333008 and the ``Strategic Priority
+Research Program the Emergence of Cosmological Structures'' of the
+CAS(No.XD09010000).
 
@@
 
-% Multiscale Gaussian Random Fields and Their Application to Cosmological Simulations
-%\bibitem[Bertschinger(2001)]{Bertschinger01} Bertschinger, E.\ 2001, 
-%\apjs, 137, 1
-
 % The Search for the Missing Baryons at Low Redshift
@@
 %% DDDDDDDD
+
+% Missing Halo Baryons and Galactic Outflows
+\bibitem[Dav{\'e} (2009)]{Dave09} Dav{\'e}, R.\ 2009, ASPC, 419, 347D
+
+% The intergalactic medium over the last 10 billion years - I. Lya absorption and physical conditions
+\bibitem[Dav{\'e} et al.(2010)]{Dave10} Dav{\'e}, R., Oppenheimer, B.~D., Katz, N., et al.\ 2010, \mnras, 408, 2051
 
@@
 
-% Dark MaGICC: the effect of dark energy on disc galaxy formation. Cosmology does matter
-%\bibitem[Penzo et al.(2014)]{Penzo14} Penzo, C., Macci{\`o}, 
-%  A.~V., Casarini, L., Stinson, G.~S., \& Wadsley, J.\ 2014, \mnras, 442, 176
-
 % The baryon content of the universe
@@
 
-%Evolution of the Mass-Metallicity Relations in Passive and Star-forming Galaxies from SPH-cosmological Simulations
-
-%Multiphase smoothed-particle hydrodynamics
-%\bibitem[Ritchie \& Thomas(2001)]{Ritchie01} Ritchie, B.~W.,
-%  \& Thomas, P.~A.\ 2001, \mnras, 323, 743
-
 %% SSSSSSSSSSSS
@@
 
+% Diffuse Coronae in Cosmological Simulations of Milky Way-sized Galaxies
+\bibitem[Sokolowska et al.(2016)]{Sokolowska16}
+Sokolowska, A., Mayer, L., Babul, A., Madau, P., Shen, S.\ 2016, \apj, 819, 21
+
+% A Universal Density Structure for Circum-Galactic Gas
+\bibitem[Stern et al.(2016)]{Stern16} 
+Stern, J., Hennawi, J.~F., Prochaska, J.~X., Werk, J.~K.\ 2016, arXiv:1604.02168
+
 %Making Galaxies In a Cosmological Context: the need for early stellar feedback
@@
 C., Macci{\`o}, A.~V., et al.\ 2013, \mnras, 428, 129
+
+% NIHAO III: the constant disc gas mass conspiracy
+\bibitem[Stinson et al.(2015)]{Stinson15} Stinson, G.~S., Dutton, A.~A., Wang, L., et al.\ 2015, \mnras, 454, 1105
 

### 2016-05-31 ms_nihao_budget.tex
fix the problem on figure 3
rephrased some English

@@
 \centerline{
-  \psfig{figure=ratioprofile_v4.eps,width=0.5\textwidth}
+  \psfig{figure=ratioprofile.eps,width=0.5\textwidth}
 }
@@
   of ionic  columns densities. This new method combines the
-  information available from different ??? during the photoionization
+  information available from different sightlines during the photoionization
   modeling, and was applied to the COS-HALOs data,  yielding a total
@@
 
-\item {\bf ??? I don't understand this sentence ?? Cool gas is a major
-  component in total baryons  whose mass is same as the fiducial
-  baryonic mass of  total dark matter mass inside virial radius. Most
-  of the cool gas in these baryons locates out of the virial radius.}
+\item {\bf Cool gas is a major component of the total baryons within
+      R$_{\rm bar}$, most of which is outside of the virial radius.}
 

### 2016-06-01 ms_nihao_budget.tex
Add some content on HI and OVI absorption line and cite Thales' paper in Introduction

@@
 \def \oii      {[\ion{O}{II}]}
+\def \ovi      {\ion{O}{VI}}
 
@@
 {\bf The circum galactic medium (CGM) is a major potential  reservoir
-  of the missing baryons.}  Recent advances in the detection of  gas
+  of the missing baryons. \hi{} and metal absorption lines are expected 
+to exhibit such diffuse baryonic content. \hi{} is mainly from gas with
+temperature T $\sim 10^4$ K so that it is able to detect cold gas in CGM.
+Meanwhile, theoretical work has predicted that a substaince portion of 
+CGM is in warm or hot phase with temperature T $> 10^{4.5}$ K, either
+through photoionization, accretion shock or shock caused by galactic winds
+\citep{voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, the detection
+is dominated by metal line, e.g. \ovi{}.}  Recent advances in the detection of gas
 in the CGM have come  from the COS survey \citep{Tumlinson11,
@@
 be extended to a wider range of halo masses.
+{\bf A number of large volume cosmological simulations \citep{Ford13, Ford15,
+Suresh15b, Oppenheimer16} and zoom-in cosmological simulations \citep{Stinson12,
+Hummels13, Shull14} have given the prediction for the \hi{} and
+\ovi{} absorption line. \citet{Gutcke16}
+compared the column density profile of \ovi{} and \hi{} in CGM of galaxies
+of the cosmological hydrodynamical simulation suite NIHAO \citep{Wang15}
+with observations, studied the covering fraction of dense \hi{}, looked
+at the shape of the CGM and its chemical composition. The conclusion
+shows the simulations can reproduce the observation properties well.}
+
 %{\bf ??? To understand
@@
 cosmic baryonic fraction, but the missing fraction is strongly mass
-dependent.  {\bf Mention Gutcke et al. 2016}
+dependent.
 
@@
 
+%
+\bibitem[Ford et al.(2013)]{Ford13} Ford, A.~B., Oppenheimer, B.~D., Dav{\`e}, R., et al.\ 2013, \mnras, 432, 89
+
+%
+\bibitem[Ford et al.(2015)]{Ford15} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2015, arXiv:1503.02084
+
 % The Cosmic Baryon Budget
@@
 %% GGGGGGGGG
+
+% NIHAO VIII:
+\bibitem[Gutcke et al.(2016)]{Gutcke16} Gutcke, T.~A., Stinson, G.~S., Macci{\`o}, A.~V., et al.\ 2016, arXiv:1602.06956
 
@@
 He, P., Feng, L.~L., Fang, L.~Z.\ 2005, \apj, 623, 601
+
+%
+\bibitem[Hummels et al.(2013)]{Hummels13} Hummels, C.~B., Bryan, G.~L., Smith, B.~D., et al.\ 2013, \mnras, 430, 1548
 
@@
 
+%
+\bibitem[Oppenheimer et al.(2016)]{Oppenheimer16} Oppenheimer, B.~D., Crain, R.~A., Schaye, J., et al.\ 2016, arXiv:1603.05984
+
 %% PPPPPPPPP
@@
 
+%
+\bibitem[Shull (2014)]{Shull14} Shull, J.~M.\ 2014, \apj, 784, 142
+
 % Diffuse Coronae in Cosmological Simulations of Milky Way-sized Galaxies
@@
 
+%
+\bibitem[Stinson et al.(2012)]{Stinson12} Stinson, G.~S., Brook, C., Prochaska, J.~X., et al.\ 2012, \mnras, 425, 129
+
 %Making Galaxies In a Cosmological Context: the need for early stellar feedback
@@
 \bibitem[Stinson et al.(2015)]{Stinson15} Stinson, G.~S., Dutton, A.~A., Wang, L., et al.\ 2015, \mnras, 454, 1105
+
+%
+\bibitem[Suresh et al.(2015)]{Suresh15b} Suresh, J., Rubin, K.~H.~R., Kannan, R., et al.\ 2015, arXiv:1511.00687
 
@@
 %% VVVVVVVVVVVV
+
+% Properties of gas in and around galaxy haloes
+\bibitem[van de Voort \& Schaye (2012)]{voort12} van de Voort, F., Schaye, J.\ 2012, \mnras, 423, 2991
 

### 2016-06-02 ms_nihao_budget.tex
add a unit in the conclusion of figure 3

@@
 We thus conclude that, for galaxies with halo mass 
-below $10^{11}$, the majority of baryons associated with the
+below $10^{11} \Msun$, the majority of baryons associated with the
 dark matter halo are in the cold and cool phases, 

### 2016-06-08 ms_nihao_budget.tex
correct one mistake about the normalization of Figure 2

--- 2016-06-01 ms_nihao_budget.tex
@@
   10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
-  30\%$ missing, consistent with observational estimates.
-
-%  Finally we show that the baryonic budget of most massive 
-%  galaxies in NIHAO suite can match the observation for most 
-%  components but the cool gas, which requires further 
-%  theoretical and observational work to find the answer where
-%  the cool gas actually is.
+  30\%$ missing, consistent with {\bf recent} observational estimates.
 \end{abstract}
@@
 {\bf The circum galactic medium (CGM) is a major potential  reservoir
-  of the missing baryons. \hi{} and metal absorption lines are expected 
-to exhibit such diffuse baryonic content. \hi{} is mainly from gas with
-temperature T $\sim 10^4$ K so that it is able to detect cold gas in CGM.
-Meanwhile, theoretical work has predicted that a substaince portion of 
-CGM is in warm or hot phase with temperature T $> 10^{4.5}$ K, either
-through photoionization, accretion shock or shock caused by galactic winds
-\citep{voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, the detection
-is dominated by metal line, e.g. \ovi{}.}  Recent advances in the detection of gas
-in the CGM have come  from the COS survey \citep{Tumlinson11,
-  Tumlinson13, Thom12,  Werk12, Werk13}.  On the scale of Milky Way
-mass haloes $\Mhalo \sim 10^{12}\Msun$ a significant amount of warm
-($10^4 < T < 10^7$K) gas has been detected \citep{Werk14}, accounting
-for 33-88\% of the baryon budget. In the future such observations will
-be extended to a wider range of halo masses.
-{\bf A number of large volume cosmological simulations \citep{Ford13, Ford15,
-Suresh15b, Oppenheimer16} and zoom-in cosmological simulations \citep{Stinson12,
-Hummels13, Shull14} have given the prediction for the \hi{} and
-\ovi{} absorption line. \citet{Gutcke16}
-compared the column density profile of \ovi{} and \hi{} in CGM of galaxies
-of the cosmological hydrodynamical simulation suite NIHAO \citep{Wang15}
-with observations, studied the covering fraction of dense \hi{}, looked
-at the shape of the CGM and its chemical composition. The conclusion
-shows the simulations can reproduce the observation properties well.}
+  of the missing baryons. \hi{} and metal absorption lines are
+  expected  to signpost such diffuse baryonic content. \hi{} is mainly
+  from gas with temperature T $\sim 10^4$ K so that it is able to
+  detect cold gas in the CGM.  Meanwhile, theoretical work has
+  predicted that a substantial  portion of the CGM is in the warm or
+  hot phase with temperature T $> 10^{4.5}$ K.  Gas enters this phase
+  through photoionization, accretion shocks or shocks caused by
+  galactic winds \citep{Voort12}. Such dilute halo gas is at T$\sim
+  10^{4.5-7}$ K, so the detection is dominated by metal lines,
+  e.g. \ovi{}.}  Recent advances in the detection of gas in the CGM
+have come  from the COS survey \citep{Tumlinson11, Tumlinson13,
+  Thom12,  Werk12, Werk13}.  On the scale of Milky Way mass haloes
+$\Mhalo \sim 10^{12}\Msun$ a significant amount of warm ($10^4 < T <
+10^7$K) gas has been detected \citep{Werk14}, accounting for 33-88\%
+of the baryon budget. In the future such observations will be extended
+to a wider range of halo masses.  {\bf A number of large volume
+  cosmological simulations \citep{Ford13, Ford15, Suresh15b,
+    Oppenheimer16} and zoom-in cosmological simulations
+  \citep{Stinson12, Hummels13, Shull14} have given predictions for the
+  \hi{} and \ovi{} absorption line. \citet{Gutcke16} compared the
+  column density profile of \ovi{} and \hi{} in the CGM of galaxies
+  from the NIHAO \citep{Wang15} cosmological hydrodynamical
+  simulation suite with observations, studied the covering fraction of
+  dense \hi{}, looked at the shape of the CGM and its chemical
+  composition. The conclusion shows the simulations can reproduce the
+  observation properties well.}
 
-%{\bf ??? To understand
-%  the physical properties of the CGM and the origins of components in
-%  each phase has been shown to be able to test the impact of feedback
-%  models \citep{Sharma12,Marasco13}???
   {\bf The physical properties of the CGM has been shown to be able to
@@
 a sample of 88 zoom-in galaxy formation simulations from the NIHAO
-project. NIHAO galaxies are consistent with the stellar mass vs halo
-mass relations from halo abundance matching since redshift $z\sim 4$
-\citep{Wang15}, the galaxy star formation rate vs stellar mass
-relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
-stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore,
-the simulations make plausible predictions for the mass fractions and
+project.
+{\bf Reproducing the stellar mass content in dark matter haloes both
+  today and in the past has been a formidable challenge for cosmological galaxy
+  formation simulations \citep{Weinmann12, Hopkins14}. Even the latest
+  state-of-the art simulations have trouble: the ILLUSTRIS simulation
+  \citep{Vogelsberger14} strongly overpredicts the stellar masses in
+  dwarf galaxy haloes $(M_{200} \lta 10^{11}\Msun)$, while the EAGLE
+  simulations \citep{Schaye15} underpredict the peak of the star
+  formation efficiency in halos of mass $M_{200}\sim 10^{12}\Msun$. In
+  contrast, the} NIHAO galaxies are consistent with the stellar mass
+vs halo mass relations from halo abundance matching since redshift
+$z\sim 4$ \citep{Wang15}, the galaxy star formation rate vs stellar
+mass relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
+stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore, the
+simulations make plausible predictions for the mass fractions and
 physical locations of the warm and hot gas components.  We find that
@@
 
-%We study the baryonic budget using the full set simulations of the NIHAO project.  
-%The large range of the mass covered by our simulations enables
-%us see the baryon fractions and mass profiles of different 
-%galaxies, depending on the halo mass and stellar content.
-
 %% FIGURE 1
@@
 %  \psfig{figure=barbudget_v3.eps,width=0.5\textwidth}
-  \psfig{figure=barbudget_linearlog.eps,width=0.5\textwidth}
+  \psfig{figure=barbudget_linearlog.eps,width=0.48\textwidth}
 }
@@
   and logarithmic (lower panel) scales emphasize the large amount of
-  ``missing'' baryons and the low star formation efficiencies.}
+  ``missing'' baryons, and the power-law nature of the relations,
+  respectively.}
 \label{fig:budget}
 \end{figure}
-
-%% FIGURE 2
-\begin{figure*}
-\centerline{
-  \psfig{figure=budgetpro.eps,width=0.99\textwidth}
-}
-\caption{Radial profile of the mass fraction of the gas in each phase
-         to total baryon mass in each radial bin 
-         at z=0 for all galaxies in NIHAO sample.
-         Each solid line is from one galaxy and color coded with
-         the halo mass. {\bf tickmarks overlap. fix. use $R_{200}$ for virial radius}}
-\label{fig:corona}
-\end{figure*}
 
@@
 \end{equation}
-where the $M_{\rm dm}$ is the total dark matter mass in the halo, and
+where the $M_{\rm dm}$ is the total dark matter mass of the halo, and
 the $f_{\rm b} = \Omegab/\Omegam \sim 0.15$ is the cosmic baryon
 fraction (the ratio between baryon density and mass density including baryonic mass
-plus dark matter), so that the  $M_{\rm b}$ is the baryonic mass inside the
-virial radius if the baryons follow the dark matter closely.
+plus dark matter), so that $M_{\rm b}$ would be the baryonic mass inside the
+virial radius if the baryons followed the dark matter closely.
 
@@
 \citet{Kravtsov14}.
+Fig.~\ref{fig:budget} shows that all haloes in our study contain less
+than the universal fraction of baryons. The upper panel uses a linear
+y-axis scale, which highlights the large amount of baryons that are
+missing, especially in low mass haloes. The logarithmic scale in the
+lower panel highlights the power-law nature of the relations.
 
-We tried to capture the behavior of the baryonic mass fraction as a 
-function of the halo mass using a double power law formula:
+The trends of each component fraction are similar, in that  the
+fractions are relatively low in low mass haloes, and increase as the
+halo mass increases.  The main difference between the different
+components is the slope, with the baryonic mass fraction having a
+shallower slope than the stellar mass fraction.  This is because in
+low mass haloes ($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in
+the form of gas, while in the highest mass haloes we study
+($\Mhalo\sim 10^{12}\Msun$) there are roughly equal amounts of stars
+and gas.
+
+Since most of the haloes we study are above the mass where the cosmic UV
+background prevents gas from cooling, the missing baryons have most
+likely been ejected from the central galaxies in supernova/stellar
+feedback driven winds.  Although the lower mass galaxies have
+converted a smaller fraction of their available baryons into stars,
+and hence there is proportionally less energy available to drive an
+outflow, they have expelled a larger fraction of their baryons,
+consistent with expectations from energy driven gas outflows
+\citep[e.g.,][]{Dutton12}.
+
+The behavior of the baryonic mass fraction, $f_{\rm bar}$, as a 
+function of the halo mass is captured using a double power law formula:
 \begin{equation}
@@
 and 0.0518 for halo mass in
-$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.}
+$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.
 
-The trends of each component fraction are similar, in that  the
-fractions are relatively low in low mass haloes, and increase as the
-halo mass increases.  The main difference between the different
-components is the slope, with the baryonic mass fraction having a
-shallower slope than the stellar mass fraction.  This is because in
-low mass haloes ($\Mhalo\sim 10^{10}\Msun$) most of the baryons are in
-the form of gas, while in the highest mass haloes we study
-($\Mhalo\sim 10^{12}\Msun$) there are roughly equal amounts of stars
-and gas.
-
-Fig.~\ref{fig:budget} shows that all haloes in our study contain less
-than the universal fraction of baryons. The upper panel uses a linear
-y-axis scale, which highlights the large amount of baryons that are
-missing, especially in low mass haloes. The logarithmic scale in the
-lower panel highlights the power-law nature of the relations.
-
-Since the haloes we study are above the mass where the cosmic UV
-background prevents gas from cooling, the missing baryons have most
-likely been ejected from the central galaxies in supernova/stellar
-feedback driven winds.  Although the lower mass galaxies have
-converted a smaller fraction of their available baryons into stars,
-and hence there is proportionally less energy available to drive an
-outflow, they have expelled a larger fraction of their baryons,
-consistent with expectations from energy driven gas outflows
-\citep[e.g.,][]{Dutton12}.
+As might be expected, haloes with the highest masses we study have
+high baryon fractions with relatively  small scatter. As halo mass
+decreases, the baryon fraction decreases and the scatter increases,
+consistent with expectations from outflows driven by stellar
+feedback. At the lowest halo masses we study, below $10^{10}\Msun$,
+the scatter starts to decrease. By contrast the scatter in the stellar
+mass fraction increases below this scale. Thus it seems unlikely that
+stellar feedback is primarily responsible for the low baryon
+fractions.  Rather, we suggest an increased importance of the UV
+background, which heats gas to above the virial temperature, thus
+preventing it from collapsing into the low mass haloes.}
 
@@
 
+%% FIGURE 2
+\begin{figure}
+\centerline{
+  \psfig{figure=budgetpro.eps,width=0.48\textwidth}
+}
+\caption{Radial profile of the mass fraction of the gas in each phase
+         to total baryonic mass in each radial bin 
+         at $z=0$ for all galaxies in NIHAO sample.
+         Each solid line is from one galaxy and colour coded with
+         the halo mass.}
+\label{fig:corona}
+\end{figure}
+
 {\bf In Fig.~\ref{fig:corona}, we present the radial distribution of
-  gas in different phases at $z=0$, normalized to the total baryon
-  mass profile, such that for a given halo the four phases add up to
+  gas in different phases at $z=0$, normalized to the total baryonic
+  mass profile, such that, in the region far away from central galaxy
+  where the stars are rare, for a given halo the four phases add up to
   unity.  All simulations share a common attribute.  The cold gas (T$<
@@
 
-%% FIGURE 3
-\begin{figure}
-\centerline{
-  \psfig{figure=ratioprofile.eps,width=0.5\textwidth}
-}
-\caption{Baryon distribution of each galaxy from NIHAO simulations. 
- The lines are color coded by their halo mass, which shows a
-  clear trend that the more massive haloes preserve more baryons at
-  all radii.}
-\label{fig:rps}
-\end{figure}
-
-%% FIGURE 4
-\begin{figure}
-\centerline{
-  \psfig{figure=missing_vr.eps,width=0.5\textwidth}
-}
-\caption{Baryon radius as function of total virial mass.
-         The points are color coded by the ratio 
-         between baryon radius and the virial radius of each galaxy.}
-\label{fig:missvr}
-\end{figure}
-
-%% FIGURE 5
-\begin{figure*}
-\centerline{
-  \psfig{figure=budget_inout.eps,width=0.99\textwidth}
-}
-\caption{Mass fraction of gas in four phases (relative to the fiducial
-  baryonic mass within virial radius). The blue and red points are for
-  gas  inside and outside the virial radius, respectively. Cool gas is
-  the dominant component of the CGM in NIHAO simulations.}
-\label{fig:inout}
-\end{figure*}
-
 \subsection{Where are the missing baryons?}
@@
 
-Each solid curve represents a halo, and the curves are colored by
+Each solid curve represents a halo, and the curves are coloured by
 their halo mass (red for high masses to blue for low masses).  Broadly
@@
 
-%The curves show a gradual transition based on mass that confirms 
-%what we find in Fig.~\ref{fig:budget}. 
-%In general terms, the lowest mass halos have a small peak but drop
-%relatively steeply until $\sim$ 0.2R$_{200}$, then the curves rise slowly.
-%As the masses increase, the central peaks rise and the curves in the 
-%outer part are flater.
-%Finally, the most massive galaxies have an almost constant curve 
-%which are close but still less than 1.
+%% FIGURE 3
+\begin{figure}
+\centerline{
+  \psfig{figure=ratioprofile.eps,width=0.5\textwidth}
+}
+\caption{Baryon distribution of each galaxy from NIHAO simulations. 
+ The lines are colour coded by their halo mass, which shows a
+  clear trend that the more massive haloes preserve more baryons at
+  all radii.}
+\label{fig:rps}
+\end{figure}
 
@@
 
-{\bf In Fig.~\ref{fig:inout}, we calculate the fractions of gas (in each phase)
-inside the virial radius (blue points) and between 
-the virial and baryon radii (red points).
+%% FIGURE 4
+\begin{figure}
+\centerline{
+  \psfig{figure=missing_vr.eps,width=0.5\textwidth}
+}
+\caption{Baryon radius as function of total virial mass.
+         The points are colour coded by the ratio 
+         between baryon radius and the virial radius of each galaxy.}
+\label{fig:missvr}
+\end{figure}
+
+%% FIGURE 5
+\begin{figure*}
+\centerline{
+  \psfig{figure=budget_inout.eps,width=1.0\textwidth}
+}
+\caption{Mass fraction of gas in four phases (relative to the fiducial
+  baryonic mass within the virial radius). The blue and red points are for
+  gas  inside and outside the virial radius, respectively. Cool gas is
+  the dominant component of the CGM in the NIHAO simulations.}
+\label{fig:inout}
+\end{figure*}
+
+{\bf In Fig.~\ref{fig:inout}, we show the fractions of gas (in each
+  phase) inside the virial radius (blue points) and between  the
+  virial and baryon radii (red points).
   %
-The upper-left panel shows the  fractions of cold gas. The fractions
-of cold gas between the virial radius and baryon radius of galaxies with
-halo masses in the range between $10^{9} \Msun$ to  $10^{10} \Msun$
-are greater than 80\%. As the halo mass increases, this fraction goes
-down dramatically, in the mass range between $10^{10} \Msun$ and
-$10^{11} \Msun$ the fractions are less than  20\% for most of galaxies
-and the fractions for galaxies with halo mass above $10^{11} \Msun$ are
-almost 0.  For the cold gas inside the virial radius, the fractions
-increase gradually as halo mass increases and the maximum fraction is
-about 20\% with at a halo mass of $10^{12} \Msun$.
+  The fractions of cold gas,
+  $f_{\rm cold}$, are shown in the upper-left panel.  Inside the
+  virial radius $f_{\rm cold}$ increases gradually from zero at a halo
+  mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo mass of
+  $10^{12}\Msun$.  The gas outside the virial radius has the opposite
+  and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of mass
+  $10^{10}\Msun$ and decreases to zero by halo masses of
+  $10^{11}\Msun$.
   %
-The upper-right panel shows the fractions of cool gas.  The fractions
-of cool gas in region outside of virial radius  increase from 0 at
-halo masses are $10^9 \Msun$ to 80\% at halo  masses are around
-$10^{10} \Msun$ to $10^{11} \Msun$, then  decrease in higher mass
-range and reach 0 again at halo masses are $10^{12} \Msun$. The cool
-gas inside virial radius shares  a similar trend but the maximum
-fraction is about 40\% at  halo masses are $10^{11} \Msun$.
+  The fractions of cool gas, $f_{\rm cool}$, are
+  shown in the upper-right panel.  Inside the virial radius, $f_{\rm
+    cool}$, has a maximum of 40\% at a halo mass of $10^{11} \Msun$,
+  and declines to less than 10\% below and above halo masses of
+  $10^{10}\Msun$ and $10^{12}\Msun$, respectively.  For most haloes there
+  is more cool gas outside than inside the virial radius.  In haloes
+  of mass $10^{10}\Msun$, $f_{\rm cool}\sim 80\%$, and decreases to
+  less than 10\% by a halo mass of $10^{12}\Msun$.
 %
-The fractions for warm-hot gas are shown in the lower-left panel.
-The trends of the gas inside and outside gas are quite similar
-which increase as the halo masses increase monotonically and whose 
-maximum values are only 20\%.
+The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
+lower-left panel.  The trends of the gas inside and outside the virial
+radius are quite similar, $f_{\rm warm}$ increases monotonically with
+halo mass with maximum values of $\sim 30\%$.
 %
@@
 %
-We thus conclude that, for galaxies with halo mass 
-below $10^{11}$, the majority of baryons associated with the
-dark matter halo are in the cold and cool phases, 
-and are located well outside of virial radius. For the gas inside
-virial radius, the majority is cool gas for the galaxies with
-halo masses are $10^{11} \Msun$ and when halo masses are higher
-than $10^{11} \Msun$ the fractions of cold gas, cool gas and 
-warm-hot gas are comparable.}
-
-%% FIGURE 6
-\begin{figure}
-\centerline{
-  \psfig{figure=budget.eps,width=0.5\textwidth}
-}
-\caption{Baryonic budget 
-  of NIHAO haloes of mass $3.5\times 10^{11} < M_{200}/\Msun <
-  3.5 \times 10^{12}$ (blue points 
-  with 1$\sigma$ error bars) compared with observations of 
-  $M_{200} \sim 10^{12}\Msun$ haloes (shaded regions)
-  }
-\label{fig:comparison}
-\end{figure}
-
-%% TABLE 1
-\begin{table*}
-  \caption{The baryonic budget parameters for NIHAO galaxies
-    in different halo  mass bins. We refer to gas in the temperature range  T
-  $<$ $10^4$ K as cold; $10^4$ K $\leqslant$ T $<$ $10^5$ K as cool;
-  $10^5$ K $\leqslant$ T $<$ $10^7$ K as warm;  and T $\geqslant$
-  $10^7$ K as hot.}
-\begin{center}
-\begin{tabular}{ccccc}
-\hline
-\input{budgettable4.txt}
-\hline
-\end{tabular}
-\label{tab:comparison}
-\end{center}
-\end{table*}
+We thus conclude that, for galaxies with halo masses in the range
+$10^{10} \lta M_{200}\lta 10^{11} \Msun$, the majority of baryons
+associated with the dark matter halo are in the cold and cool phases,
+and are located well outside of virial radius.  For haloes in the mass
+range $10^{11} \lta M_{200}\lta 10^{12} \Msun$, the fractions of cold
+gas, cool gas and  warm-hot gas are comparable.}
 
@@
 in Fig. 11 in \citet{Werk14}.
+
+%% FIGURE 6
+\begin{figure}
+\centerline{
+  \psfig{figure=budget.eps,width=0.5\textwidth}
+}
+\caption{Baryonic budget 
+  of NIHAO haloes of mass $3.5\times 10^{11} < M_{200}/\Msun <
+  3.5 \times 10^{12}$ (blue points 
+  with 1$\sigma$ error bars) compared with observations of 
+  $M_{200} \sim 10^{12}\Msun$ haloes (shaded regions). There is good agreement, except for the cool gas which has two conflicting measurements.
+  }
+\label{fig:comparison}
+\end{figure}
+
+%% TABLE 1
+\begin{table*}
+  \caption{The baryonic budget parameters for NIHAO galaxies
+    in different halo  mass bins. We refer to gas in the temperature range  T
+  $<$ $10^4$ K as cold; $10^4$ K $\leqslant$ T $<$ $10^5$ K as cool;
+  $10^5$ K $\leqslant$ T $<$ $10^7$ K as warm;  and T $\geqslant$
+  $10^7$ K as hot.}
+\begin{center}
+\begin{tabular}{ccccc}
+\hline
+\input{budgettable4.txt}
+\hline
+\end{tabular}
+\label{tab:comparison}
+\end{center}
+\end{table*}
 
@@
 
-\item The missing baryons in all haloes are beyond 2 virial radii.
+\item The missing baryons from all haloes are located beyond 2 virial radii.
 
@@
 
+% Galaxies on FIRE (Feedback In Realistic Environments): stellar
+% feedback explains cosmologically inefficient star formation
+\bibitem[Hopkins et al.(2014)]{Hopkins14} Hopkins, P.~F., Kere{\v s}, D., O{\~n}orbe, J., et al.\ 2014, \mnras, 445, 581
+
 %
@@
 
+% The EAGLE project: simulating the evolution and assembly of
+% galaxies and their environments
+\bibitem[Schaye et al.(2015)]{Schaye15} Schaye, J., Crain,
+  R.~A., Bower, R.~G., et al.\ 2015, \mnras, 446, 521
+
 % The enrichment of the intergalactic medium with adiabatic feedback - I. Metal cooling and metal diffusion
@@
 % Properties of gas in and around galaxy haloes
-\bibitem[van de Voort \& Schaye (2012)]{voort12} van de Voort, F., Schaye, J.\ 2012, \mnras, 423, 2991
+\bibitem[van de Voort \& Schaye (2012)]{Voort12} van de Voort, F., Schaye, J.\ 2012, \mnras, 423, 2991
+
+%	Introducing the Illustris Project: simulating the coevolution
+% of dark and visible matter in the Universe
+\bibitem[Vogelsberger et al.(2014)]{Vogelsberger14} Vogelsberger, M., 
+Genel, S., Springel, V., et al.\ 2014, \mnras, 444, 1518
 
@@
 \bibitem[Wang et al.(2015)]{Wang15} Wang, L., Dutton, A.~A.,  Stinson, G.~S., et al.\ 2015, \mnras, 454, 83
+
+%  A fundamental problem in our understanding of low-mass galaxy evolution
+  \bibitem[Weinmann et al.(2012)]{Weinmann12} Weinmann, S.~M., Pasquali, A., Oppenheimer, B.~D., et al.\ 2012, \mnras, 426, 2797
 

### 2016-08-10 ms_nihao_budget.tex
thank referee
remove bold face enviroment

@@
   fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
-  find that all of our haloes {\bf are missing baryons. The missing
-    mass been relocated past 2 virial radii, and is dominated by cool gas.}
+  find that all of our haloes are missing baryons. The missing
+    mass been relocated past 2 virial radii, and is dominated by cool gas.
    Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
@@
   10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
-  30\%$ missing, consistent with {\bf recent} observational estimates.
+  30\%$ missing, consistent with recent observational estimates.
 \end{abstract}
@@
 discrepancy is referred to as the ``missing baryon problem''.
-{\bf Several theoretical studies with cosmological simulations
+Several theoretical studies with cosmological simulations
 have constrained the phase and cosmological environments of
 the potential reservoirs of the missing baryons 
-\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.}
+\citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.
 
-{\bf The circum galactic medium (CGM) is a major potential  reservoir
+The circum galactic medium (CGM) is a major potential  reservoir
 of the missing baryons. \hi{} and metal absorption lines are
@@
 10^{4.5-7}$ K, so the detection is dominated by metal lines,
-  e.g. \ovi{}.}  Recent advances in the detection of gas in the CGM
+e.g. \ovi{}.  Recent advances in the detection of gas in the CGM
 have come  from the COS survey \citep{Tumlinson11, Tumlinson13,
@@
 of the baryon budget. In the future such observations will be extended
-to a wider range of halo masses.  {\bf A number of large volume
+to a wider range of halo masses.  A number of large volume
 cosmological simulations \citep{Ford13, Ford15, Suresh15b,
@@
 composition. The conclusion shows the simulations can reproduce the
-  observation properties well.}
+observation properties well.
 
-  {\bf The physical properties of the CGM has been shown to be able to
+The physical properties of the CGM has been shown to be able to
 test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
@@
 mapping of the warm-hot medium will provide  a stringent test for
-  feedback models.}
+feedback models.
 
@@
 project.
-{\bf Reproducing the stellar mass content in dark matter haloes both
+Reproducing the stellar mass content in dark matter haloes both
 today and in the past has been a formidable challenge for cosmological galaxy
@@
 formation efficiency in halos of mass $M_{200}\sim 10^{12}\Msun$. In
-  contrast, the} NIHAO galaxies are consistent with the stellar mass
+contrast, the NIHAO galaxies are consistent with the stellar mass
 vs halo mass relations from halo abundance matching since redshift
@@
 
+%% FIGURE 2
+\begin{figure}
+\centerline{
+  \psfig{figure=budget_res.eps,width=0.48\textwidth}
+}
+\caption{Linear fractional baryon content of our NIHAO simulations  as a
+  function of halo mass. }
+\label{fig:budget_res}
+\end{figure}
+
 \section{Baryon budget}
@@
 The green shaded region indicates the scatter about the best fit line,
-{\bf which is 0.151 for haloes with mass in the range of  
+which is 0.151 for haloes with mass in the range of  
 $3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
@@
 background, which heats gas to above the virial temperature, thus
-preventing it from collapsing into the low mass haloes.}
+preventing it from collapsing into the low mass haloes.
 
@@
 
-{\bf In Fig.~\ref{fig:corona}, we present the radial distribution of
+In Fig.~\ref{fig:corona}, we present the radial distribution of
 gas in different phases at $z=0$, normalized to the total baryonic
@@
 for all galaxies in the NIHAO sample, with the maximum hot gas
-  fraction at any radius being  less than 5\%.}
+fraction at any radius being  less than 5\%.
 
-{\bf Despite these similarities, we find a considerably higher proportion
+Despite these similarities, we find a considerably higher proportion
 of cool gas in lower mass galaxies (M$_{\rm tot} < 10^{11} \Msun$)
@@
 surrounding galaxies within large distance is the major reservoir of
-  baryons.}
+baryons.
 
@@
 
-{\bf To estimate how far the baryons escape, we measured the radius,
+To estimate how far the baryons escape, we measured the radius,
 $\Rbar$, within which the total baryon mass equals to the fiducial
@@
 radius, the distance baryons are ejected to span a similar range of radii
-  $\Rbar/R_{200}\sim 2-6$.}
+$\Rbar/R_{200}\sim 2-6$.
 
@@
 
-{\bf In Fig.~\ref{fig:inout}, we show the fractions of gas (in each
+In Fig.~\ref{fig:inout}, we show the fractions of gas (in each
 phase) inside the virial radius (blue points) and between  the
@@
 range $10^{11} \lta M_{200}\lta 10^{12} \Msun$, the fractions of cold
-gas, cool gas and  warm-hot gas are comparable.}
+gas, cool gas and  warm-hot gas are comparable.
 
@@
 
-The observations and the simulations match well in every phase {\bf
-  except} the cool CGM gas, where the observations find $3\times$ the
+The observations and the simulations match well in every phase except
+ the cool CGM gas, where the observations find $3\times$ the
 mass that simulations predict.  If the observations are correct, the
-simulations have either ejected {\bf cool gas too far}, or  they have
+simulations have either ejected cool gas too far, or  they have
 created a CGM with the wrong mix of gas temperatures. The total gas
 fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
-option.   {\bf However, \citet{Stern16} developed a new method to
+option.   However, \citet{Stern16} developed a new method to
 constrain the physical conditions in the cool CGM from measurements
@@
 knowledge of the physical properties of CGM are necessary to better
-  understand the role of the CGM in galaxy formation.}
+understand the role of the CGM in galaxy formation.
 %
@@
 
-\item {\bf Cold gas ($T<10^4$K) is mostly restricted to be within
+\item Cold gas ($T<10^4$K) is mostly restricted to be within
       0.2 virial radii.  The cool gas ($10^4 < T < 10^5$K) dominates
@@
       while the warm-hot gas ($10^5 < T < 10^7$K) dominates at high
-      masses ($M_{200}\gta 3\times 10^{11} \Msun$).}
+      masses ($M_{200}\gta 3\times 10^{11} \Msun$).
 
@@
 
-\item {\bf Cool gas is a major component of the total baryons within
-      R$_{\rm bar}$, most of which is outside of the virial radius.}
+\item Cool gas is a major component of the total baryons within
+      R$_{\rm bar}$, most of which is outside of the virial radius.
 
@@
 
-\item {\bf For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
+\item For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
       which is significantly lower than the observations from COS-HALOs
       ($f_{\rm cool}=0.28-0.48$), but is in excellent agreement with the
-      analysis of \citet{Stern16}.}
+      analysis of \citet{Stern16}.
 
@@
 
+We thank the anonymous referee whose suggestions greatly 
+improve the paper.
 {\sc Gasoline} was written by Tom Quinn and James Wadsley. Without

### 2016-08-10 ms_nihao_budget.tex
add one paragraph to show the convergence of our result.

@@
 }
-\caption{Linear fractional baryon content of our NIHAO simulations  as a
-  function of halo mass. }
+\caption{{\bf Linear fractional baryon content of our NIHAO simulations  as a
+  function of halo mass color coded by number of all particles per halo.}}
 \label{fig:budget_res}
@@
 preventing it from collapsing into the low mass haloes.
+
+{\bf Since the resolution is one key parameter in simulation, 
+the convergence of the baryonic fraction predicted by NIHAO suite
+is worth to estimate. Fig.~\ref{fig:budget_res} shows baryonic 
+fraction color coded by number of total particles per halo.
+In the plot, the number of total partilce per halo spans 2 magnitudes
+and has no correlation with baryonic fraction. Therefore, we can conclude 
+the resolution of NIHAO suite is proper to study the fractional 
+baryon content.}
 

### 2016-08-10 ms_nihao_budget.tex
resolution test for cold/cool gas fraction

--- 2016-08-10 ms_nihao_budget.tex
@@
 preventing it from collapsing into the low mass haloes.
+
+{\bf Since the resolution is one key parameter in simulation, and one
+can imagine that with increased resolution, higher densities can be 
+achieved in the CGM, potential leading to more cooling and larger
+cold/cool gas fraction,
+the convergence of the baryonic fraction predicted by NIHAO suite
+is worth to estimate. Fig.~\ref{fig:budget_res} shows cold and cool
+gas (HI + HeI) fraction color coded by number of dark matter particles 
+per halo. In the plot, the number of dark matter partilce per halo spans 
+2 magnitudes and has no correlation with cold and cool gas fraction. 
+Therefore, we can conclude the resolution of NIHAO suite is 
+proper to study the fractional baryon content.}
 

### 2016-08-11 ms_nihao_budget.tex
fix some details

@@
 where the stars are rare, for a given halo the four phases add up to
-unity.  All simulations share a common attribute.  The cold gas (T$<
+unity, {\bf each line is colour coded to the virial mass}.  
+All simulations share a common attribute.  The cold gas (T$<
 10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
@@
 Despite these similarities, we find a considerably higher proportion
-of cool gas in lower mass galaxies (M$_{\rm tot} < 10^{11} \Msun$)
+of cool gas in lower mass galaxies (M$_{200} < 10^{11} \Msun$)
 in the whole corona region.  For higher mass galaxies, warm-hot gas
-dominates the corona  which signals higher efficiency  of feedback.
+dominates the corona  which signals {\bf stronger virial shock} and
+higher efficiency  of feedback.
 Even beyond the virial radius, the cool and warm-hot gas has similar
@@
 
-Fig.~\ref{fig:rps} shows the mass ratio profiles of total baryons  for
+Fig.~\ref{fig:rps} shows the {\bf cumulative fraction} of total baryons  for
 each simulation. Here the y-axis is the ratio between the baryonic to

### 2016-08-15 ms_nihao_budget.tex
change the label of figure 4 (figure 4 in current verion)

@@
 function of the virial mass.  We find the baryon radius generally
-increases with virial mass. But when normalized by the virial
-radius, the distance baryons are ejected to span a similar range of radii
-$\Rbar/R_{200}\sim 2-6$.
+increases with virial mass. {\bf when normalized by the virial
+radius, the distance baryons are ejected span a similar range of radii
+$\Rbar/R_{200}\sim 2-6$ and gradually decrease as halo mass 
+rise, even the majority of massive galaxies have $\Rbar \sim \Rvir$.}
 
@@
 }
-\caption{Baryon radius as function of total virial mass.
-         The points are colour coded by the ratio 
-         between baryon radius and the virial radius of each galaxy.}
+\caption{Normalized baryon radius as function of total virial mass.
+         The points are colour coded by  
+         baryon radius of each galaxy.}
 \label{fig:missvr}

### 2016-08-15 ms_nihao_budget.tex
remove hot gas panel in both figure 3 and figure 6

@@
 %% FIGURE 2
-\begin{figure}
+\begin{figure*}
 \centerline{
-  \psfig{figure=budgetpro.eps,width=0.48\textwidth}
+  \psfig{figure=budgetpro.eps,width=1.0\textwidth}
 }
@@
 \label{fig:corona}
-\end{figure}
+\end{figure*}
 
@@
 The fractions of cold gas,
-$f_{\rm cold}$, are shown in the upper-left panel.  Inside the
+$f_{\rm cold}$, are shown in the {\bf left} panel.  Inside the
 virial radius $f_{\rm cold}$ increases gradually from zero at a halo
@@
 The fractions of cool gas, $f_{\rm cool}$, are
-shown in the upper-right panel.  Inside the virial radius, $f_{\rm
+shown in the {\bf middle} panel.  Inside the virial radius, $f_{\rm
   cool}$, has a maximum of 40\% at a halo mass of $10^{11} \Msun$,
@@
 The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
-lower-left panel.  The trends of the gas inside and outside the virial
+{\bf right} panel.  The trends of the gas inside and outside the virial
 radius are quite similar, $f_{\rm warm}$ increases monotonically with
@@
 %
-The hot gas shown in the lower-right panel and is negligible both
+The hot gas {\bf isn't shown since} is negligible both
 inside and outside the virial radius across the whole mass range we

### 2016-08-16 ms_nihao_budget.tex
rephrase the statement about the majority of CGM

@@
 The green shaded region indicates the scatter about the best fit line,
-which is 0.151 for haloes with mass in the range of  
+which is 0.151 {\bf dex} for haloes with mass in the range of  
 $3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
@@
 \caption{Mass fraction of gas in four phases (relative to the fiducial
-  baryonic mass within the virial radius). The blue and red points are for
-  gas  inside and outside the virial radius, respectively. Cool gas is
-  the dominant component of the CGM in the NIHAO simulations.}
+  baryonic mass within the virial radius)
+  {\bf gas inside the virial radius (filled blue points) and between 
+   virial and baryon radius (open red points)}, respectively. Cool gas is
+  the dominant component of {\bf the fiducial baryonic mass within the 
+  virial radius for most galaxies ($10^{10} < M/\Msun < 10^{12}$, cold 
+   and warm-hot gas is majority only for the galaxies at lower and higher
+   mass end.}}
 \label{fig:inout}
@@
 
-In Fig.~\ref{fig:inout}, we show the fractions of gas (in each
-phase) inside the virial radius (blue points) and between  the
-virial and baryon radii (red points).
+In Fig.~\ref{fig:inout}, we show the mass fractions of gas (in four
+phases) inside the virial radius (filled blue points) and between the
+virial and baryon radius (open red points).
 %
@@
 %
-The hot gas {\bf isn't shown since} is negligible both
+The hot gas {\bf isn't shown} since it is negligible both
 inside and outside the virial radius across the whole mass range we
@@
 Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
-the most important component in CGM so that the more accurate
+the most important component {\bf for most galaxies in NIHAO simulation
+($10^{10} < M/\Msun < 10^{12}$), the cold and hot gas only dominate for
+galaxies at lower and higher mass end in NIHAO suite.} The more accurate
 knowledge of the physical properties of CGM are necessary to better
@@
 \item Cool gas is a major component of the total baryons within
-      R$_{\rm bar}$, most of which is outside of the virial radius.
+      R$_{\rm bar}$ {\bf for galaxies at mass range between $10^{10} \Msun$ 
+      to $10^{12} \Msun$ cold and warm-hot gas dominates only for galaxies 
+      at lower and higher mass end. Most of baryons are} outside of the 
+      virial radius.
 

### 2016-08-17 ms_nihao_budget.tex
expand the abstract by adding our finding

@@
   fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
-  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas ($10^7$K$ <
-  T$), inside the virial radius, $R_{200}$.  Compared to the predicted
+  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas (T$> 10^7$K) 
+  , inside the virial radius, $R_{200}$.  Compared to the predicted
   baryon mass, using the dark halo mass and the universal baryon
@@
   find that all of our haloes are missing baryons. The missing
-    mass been relocated past 2 virial radii, and is dominated by cool gas.
+    mass been relocated past 2 virial radii, and {\bf cool gas dominates
+  corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$) while the 
+  warm-hot gas dominates dominates at high mass (M$_{200} \gta 3 \times 10^{11} \Msun$)}.
    Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
@@
   30\%$ missing, consistent with recent observational estimates.
+  {\bf Moreover, these more massive haloes reproduce the observed 
+  fraction of cold, warm-hot and hot gas, the fraction of cool gas we
+  predict is significant lower than the observation from COS-HALOs,
+  but agree with the analysis of \citet{Stern16}}.
 \end{abstract}
@@
   the dominant component of {\bf the fiducial baryonic mass within the 
-  virial radius for most galaxies ($10^{10} < M/\Msun < 10^{12}$, cold 
+  virial radius for most galaxies ($10^{10} < M/\Msun < 10^{12}$), cold 
    and warm-hot gas is majority only for the galaxies at lower and higher

### 2016-08-17 ms_nihao_budget.tex
answer the question which baryon estimate these paper take

@@
 However, the cold baryonic mass density implied by several galaxy baryon
-estimates is only 3-8\% of the big bang nucleosynthesis expectation
+estimates {\bf mainly about stars and cold gas)}is only 3-8\% of 
+the big bang nucleosynthesis expectation
 \citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the

### 2016-08-17 ms_nihao_budget.tex
explained why we don't compare our result with the previous cosmological simulations and rephrase the conclusion of Thales' paper

--- 2016-08-17 ms_nihao_budget.tex
@@
 However, the cold baryonic mass density implied by several galaxy baryon
-estimates is only 3-8\% of the big bang nucleosynthesis expectation
+estimates {\bf (mainly about stars and cold gas)} is only 3-8\% of 
+the big bang nucleosynthesis expectation
 \citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
@@
 Several theoretical studies with cosmological simulations
-have constrained the phase and cosmological environments of
-the potential reservoirs of the missing baryons 
+have constrained the phase of
+the potential reservoirs of the missing baryons {\bf in intergalactic
+medium (IGM), and find a large fraction of the baryons with low density
+and high temperature resides between the galaxies}
 \citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.
 
-The circum galactic medium (CGM) is a major potential  reservoir
+The circum galactic medium (CGM) is {\bf another}  major potential  reservoir
 of the missing baryons. \hi{} and metal absorption lines are
@@
 dense \hi{}, looked at the shape of the CGM and its chemical
-composition. The conclusion shows the simulations can reproduce the
-observation properties well.
+composition. The conclusion shows {\bf the simulation can reproduce 
+the observational covering fraction and column density profile
+of cool \hi{} well, and echo observed \ovi{} column density trend.
+As commonly in other simulations, however, the column density of \ovi{}
+is lower and the extent of optically thick \hi{} is smaller than
+observed.}
 

### 2016-08-18 ms_nihao_budget.tex
rephrase the statement about the situation of emission and absorption observation

@@
 \subsection{Comparison with Observations of Milky Way mass haloes}
-Since the CGM is too diffuse to create emission lines, it must be
-observed using quasar absorption lines.  The COS-HALOs survey is
+{\bf Observations can gain information of CGM from absorption lines
+and emission lines. Although emission lines allow us to direct obtain
+a 3D picture of the distribution of gas in the CGM, emission line studies
+preferentially probe the dense gas closer to galaxies since gas 
+emissivity scales with the square of density. The situation is changing
+by building current facilities, e.g.\citet{Hayes16}, absorption line,
+however, is the most common observational constraints on the physical
+state of the CGM.}
+The COS-HALOs survey is
 filling in details about the $z \sim 0$ CGM \citep{Peeples14,
@@
 
+% O VI Emission Imaging of a Galaxy with the Hubble Space Telescope: a Warm Gas Halo Surrounding the Intense Starburst SDSS J115630.63+500822.1O VI Emission Imaging of a Galaxy with the Hubble Space Telescope: a Warm Gas Halo Surrounding the Intense Starburst SDSS J115630.63+500822.1
+\bibitem[Hayes et al.(2016)]{Hayes16}
+Hayes, M., Melinder, J., {\"O}stlin, G., et al.\ 2016, arXiv:1606.04536
+
 % Distributions of the Baryon Fraction on Large Scales in the Universe

### 2016-08-21 ms_nihao_budget.tex
compare the baryon fraction with FIRE

@@
 return to low-mass galaxies than high-mass galaxies.
+{\bf \citet{Muratov15} showed similar results that the gas and
+baryon fractions are lower at lower redshift, after powerful
+outflows at intermediate redshift z $\approx 0.5-2$ remove a large
+amount of gas from the halo. \citet{Voort16} found baryon fraction
+and gas fraction are reduced compared to the cosmic mean baryon
+fraction, and low mass haloes reduce larger since feedback can
+easily expel gas from it, which is consistent with existing 
+observation.}
 %  
@@
 parameters from the Planck  satellite \citep{Planck14}. 
-More information on the collisionless parent simulations and
+More information on the collisionless parent simulations,
+{\bf the force softenings and particle masses for the highest 
+refinement level for each simulation} and
 sample  selection can be found in \citet{Dutton14} and \citet{Wang15}
@@
 and ionization and  cooling due to hydrogen, helium and metals
-\citep{Shen10}.  The star formation and feedback modeling follows what
-was used in the MaGICC simulations \citep{Stinson13}.  There are two
+\citep{Shen10}.
+
+khe star formation and feedback modeling follows what
+was used in the MaGICC simulations \citep{Stinson13}.  
+{\bf The gas converts into stars according to the Kennicutt-Schmidt Law
+when it satisfies a temperature and density threshold. Stars feed both
+metals and energy back into the ISM gas surrounding the region where
+they formed. SN feedback is implemented using the blastwave formalism
+described in \citet{Stinson06}. Pre-SN feedback is an effort to consider
+radiation energy from massive stars which is am important complementary
+to physcial model for stellar feedback. Heating is introduced immediately
+after massive stars form based on how much star light is radiated. 
+Our simulations use thermal feedback to provide pressure support and 
+increase gas temperature above the star formation threshold to
+decrease star formation.}
+There are two
 small changes in NIHAO simulations: The change in  number of neighbors
@@
 \centerline{
+  \psfig{figure=m500c_frac.eps,width=0.48\textwidth}
+}
+\caption{{\bf Baryon fraction within R$_{500}$ comparing with \citet{Voort16}.
+   The blue points are from NIHAO simulations and the red pentagons are from
+   FIRE simulations.}}
+\label{fig:fire_com}
+\end{figure}
+
+%% FIGURE 3
+\begin{figure}
+\centerline{
   \psfig{figure=budget_res.eps,width=0.48\textwidth}
@@
 and gas.
+{\bf To compare with baryon fraction in \citet{Voort16}, we derive
+the M$_{500}$ and R$_{500}$ to recalculate the ratio between 
+baryon fraction to the universal fraction of baryons. The baryon
+fraction have good agreement with each other in the whole mass range
+where NIHAO simulations explored. For the massive haloes with 
+M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
+reduced baryon fraction and four more massive galaxies from FIRE
+have larger reduced baryon fraction which may hint that the baryon
+fraction will decrease as the halo mass increases in large mass range.}
 
@@
 
+% Gusty, gaseous flows of FIRE: galactic winds in cosmological simulations with explicit stellar feedback
+\bibitem[Muratov et al.(2015)]{Muratov15} Muratov, A.~L., Ker{\v e}s, D., Faucher-Gigu{\`e}re, C., et al.\ 2015, \mnras, 454, 2691
+
 %% NNNNNNNNN
@@
 
+% Star formation and feedback in smoothed particle hydrodynamic simulations - I. Isolated galaxies
+\bibitem[Stinson et al.(2006)]{Stinson06} Stinson, G.~S., Seth, A., Katz, N., et al.\ 2006, \mnras, 373, 1074
+
 %
@@
 \bibitem[van de Voort \& Schaye (2012)]{Voort12} van de Voort, F., Schaye, J.\ 2012, \mnras, 423, 2991
+
+%The impact of stellar feedback on hot gas in galaxy haloes:
+%the Sunyaev-Zeldovich effect and soft X-ray emission 
+\bibitem[van de Voort et al.(2016)]{Voort16} van de Voort, F., Quataert, E., Hopkins, P.~F., et al.\ 2016, arXiv:1604.01397
 

### 2016-08-21 ms_nihao_budget.tex
rephrase to explain why the slope of baryon fraction and star fraction is different

@@
 the form of gas, while in the highest mass haloes we study
-($\Mhalo\sim 10^{12}\Msun$) there are roughly equal amounts of stars
-and gas.
+($\Mhalo\sim 10^{12}\Msun$) {\bf a substantial amounts of gas
+forms stars}.
 {\bf To compare with baryon fraction in \citet{Voort16}, we derive

### 2016-08-23 ms_nihao_budget.tex
discuss about the three most massive galaxies

@@
 preventing it from collapsing into the low mass haloes. 
+{\bf Although the three most massive galaixes in NIHAO suite have fairly 
+high stellar masses (see blue filled circles in Fig.~\ref{fig:budget}),
+they don't have large deviations apart from the fitting baryon fraction, 
+and in the comparason with FIRE (see Fig.~\ref{fig:fire_com}), these
+three objects seem to hint the trend on massive galaxy end associated
+with the data from \citet{Voort16}. Moreover, the fitting relation 
+about the baryon fraction is not sensitive to these three most massive 
+galaxies as well since they have equal weight with other more than 
+80 galaxies to shape the fitting curve.}
 

### 2016-08-24 ms_nihao_budget.tex
compare with simulation works

@@
   Oppenheimer16} and zoom-in cosmological simulations
-\citep{Stinson12, Hummels13, Shull14} have given predictions for the
+\citep{Stinson12, Hummels13, Shull14} have given 
+predictions for the
 \hi{} and \ovi{} absorption line. \citet{Gutcke16} compared the
@@
 forms stars}.
-{\bf To compare with baryon fraction in \citet{Voort16}, we derive
+
+{\bf \citet{Christensen16} run twenty galaxy simulations spanning the mass range
+from $10^{9.5} - 10^{12} \Msun$ using zoom-in cosmological hydrodynamic 
+simulation code and didn't only reproduce the stellar mass - halo mass
+relation but also showed a similar baryon fraction relation, e.g. in 
+L$^*$ galaxies, the fraction is reduced by 20\% while in galaxies with
+halo mass $< 10^{10} \Msun$ there can be as large as an 80\% mass reduction.
+This suggests that the potential well of the halo regulates the baryon
+fraction.
+To compare with baryon fraction in \citet{Voort16}, we derive
 the M$_{500}$ and R$_{500}$ to recalculate the ratio between 
@@
 
+{\bf Two cosmological hydrodynamic simulations in \citet{Ford15} 
+which employed two prescriptions for galactic 
+outflow models to compare with COS-Halos showed this cumulative
+baryon fraction profile for COS-Halos matched sample of galaxies.
+One hybrid energy/momentum driven winds model ("ezw" model) makes up to
+65\% of all baryons inside the halo. This is broadly consistent with
+estimates of baryonic mass derived from \citet{Werk14} and our 
+finding in Fig.~\ref{fig:budget}. Comparing the cumulative baryon
+fraction profile in detail, Fig.10 in \citet{Ford15} shows the baryon
+fraction within 0.1$\Rvir$ is only $\sim 30\%$ and the fraction 
+gradually increases to 65\% at $\Rvir$ while the profile of galaxies
+with halo mass below $10^{11} \Msun$ in Fig.~\ref{fig:rps} have 
+similar feature, the more massive galaxies all have roughly flat slopes.
+The simplified outflow model (constant wind model or "cw" model) shows
+lower fraction at all radii inside $\Rvir$ even though "ezw" model
+and "cw" model generally gives similar observational absorption 
+line properties. This suggests that the profile of cumulative baryon
+fraction, as a complementary of total amount observation of CGM,
+ is important to distinguish between competing outflow models
+that often closely relate to the feedback models.
+}
 %% FIGURE 3
@@
 
-\subsection{Comparison with Observations of Milky Way mass haloes}
+\subsection{Comparison with observations
+of Milky Way mass haloes}
+
 {\bf Observations can gain information of CGM from absorption lines
@@
 emissivity scales with the square of density. The situation is changing
-by building current facilities, e.g.\citet{Hayes16}, absorption line,
+by building current facilities, e.g.~\citet{Hayes16}, absorption line,
 however, is the most common observational constraints on the physical
@@
 ($10^{10} < M/\Msun < 10^{12}$), the cold and hot gas only dominate for
-galaxies at lower and higher mass end in NIHAO suite.} The more accurate
+galaxies at lower and higher mass end in NIHAO suite.} 
+{\bf A new estimation for the baryonic fractions from a set of
+eight Milky Way-sized zoom-in cosmological simulations 
+\citep{Colin16} is genenrally consistence with our results. The 
+fraction of cool gas from their simulation is even lower 
+($f_{\rm cool}$ = 0.034) than ours and the result from 
+\citet{Stern16}. On the other hand, \citet{Peeples14} gave 
+a conservative observational estimate about warm-hot gas and
+showed that the fraction of gas in this phase is only 5\%, 
+which is the lower limit of the estimates from \citet{Werk14} 
+and less than the average values from \citet{Colin16} 
+($f_{\rm warm-hot} \approx 24\%$) and our finding 
+($f_{\rm warm-hot} \approx 17\%$). Therefore, the mix temperature
+of CGM have large uncertainty and}
+the more accurate
 knowledge of the physical properties of CGM are necessary to better
@@
 
+%In-N-Out: The Gas Cycle from Dwarfs to Spiral Galaxies
+\bibitem[Christensen et al.(2016)]{Christensen16}
+Christensen, C.~R., Dav{\'e}, R., Governato, F., et al.\ 2016, \apj, 824, 57
+
+%Cosmological simulations of Milky Way-sized galaxies
+\bibitem[Colin et al.(2016)]{Colin16}
+Colin, P., Avila-Reese, V., Roca-Fabrega, S., et al.\ 2016, \apj, in press
+
 %% DDDDDDDD
@@
 %
-\bibitem[Ford et al.(2015)]{Ford15} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2015, arXiv:1503.02084
+\bibitem[Ford et al.(2015)]{Ford15} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2016, \mnras, 459, 1745
 

### 2016-08-25 ms_nihao_budget.tex
first version of the draft for the second referee's comments

@@
 \usepackage{array}
+\usepackage{amsmath}
+\usepackage{amssymb}
 %\usepackage{graphicx}
@@
 consistent with expectations from outflows driven by stellar
-feedback. At the lowest halo masses we study, below $10^{10}\Msun$,
+feedback {\bf since the energy-driven wind model determined that
+mass loading factors show a power-law dependency on circular velocity
+, with an exponent of $\approx -2$, \eg \citet{Christensen16}, 
+which means the greater efficiency of small galaxies at 
+driving outflows is simply a result of their shallower potential 
+well and the increasing scatters come from the increasing scatters of
+stellar mass halo mass relation in lower mass range.}
+At the lowest halo masses we study, below $10^{10}\Msun$,
 the scatter starts to decrease. By contrast the scatter in the stellar
@@
       inside the virial radius, than the cosmic baryon fraction. 
+      {\bf Higher fractions of baryons are lost as the virial mass 
+      decreases in the mass range of $\lesssim 10^{12} \Msun$.
+      The trend confirmed with \citet{Christensen16} and \citet{Voort16},
+      and associated by \citet{Voort16}, the trend at higher mass range
+      may suggest the baryon fraction is reduced larger as virial mass
+      increase. }
+
+\item Lower mass haloes have lost a larger fraction of their baryons, 
+      even though they convert a lower fraction of the baryons into stars.
 
@@
 
-\item The missing baryons from all haloes are located beyond 2 virial radii.
+\item {\bf All haloes have less baryons than baryon mass derived by cosmic
+       baryonic fraction even beyond 2 virial radii. The total 
+       baryons derived by cosmic baryonic fraction within virial radius 
+       can expand more than $8\Rvir$ for low mass haloes but less than
+       $2\Rvir$ for high mass haloes.}
 
@@
 
-\item Lower mass haloes have lost a larger fraction of their baryons, 
-      even though they convert a lower fraction of the baryons into stars.
-
 \item For the highest mass haloes in our study $\sim 10^{12}\Msun$ our
       simulations are consistent with the observed  fractions of stars,
-      cold gas, warm and hot gas.
+      cold gas, warm and hot gas \citep{Werk14}. {\bf \citet{Peeples14} 
+      showed a conservative observational estimate for warm-hot gas 
+      which is lower limit of the result from \citet{Werk14} and the 
+      warm-hot fraction from our study is well within the range of less
+      conservative estimates.}
 
@@
       analysis of \citet{Stern16}.
+      {\bf As in \citet{Colin16}, the simulations suggest that the
+      fraction of cool gas is approximately 10\%.}
 
@@
 
-We thank the anonymous referee whose suggestions greatly 
+We thank the two anonymous referees whose suggestions greatly 
 improve the paper.
+{\bf We thank Freeke van de Voort for kindly sharing data of the FIRE
+simulation.}
 {\sc Gasoline} was written by Tom Quinn and James Wadsley. Without

### 2016-09-12 ms_nihao_budget.tex
new plot for comparason by including Christensen+16

@@
 %% FIGURE 2
-\begin{figure}
+\begin{figure*}
 \centerline{
-  \psfig{figure=m500c_frac.eps,width=0.48\textwidth}
+  \psfig{figure=m500c_frac.eps,width=1.00\textwidth}
 }
-\caption{{\bf Baryon fraction within R$_{500}$ comparing with \citet{Voort16}.
-   The blue points are from NIHAO simulations and the red pentagons are from
-   FIRE simulations.}}
+\caption{{\bf Upper panel shows baryon fraction comparing with 
+   \citet{Voort16} (left) and \citet{Christensen16} (right), and lower
+   panel shows stellar fraction comparing with \citet{Voort16} (left) 
+   and \citet{Christensen16} (right).
+   The blue points are from this work, the red pentagons are from
+   \citet{Voort16} and the magenta pentagons are from 
+   \citet{Christensen16}.}}
 \label{fig:fire_com}
-\end{figure}
+\end{figure*}
 
@@
 fraction.
-To compare with baryon fraction in \citet{Voort16}, we derive
-the M$_{500}$ and R$_{500}$ to recalculate the ratio between 
-baryon fraction to the universal fraction of baryons. The baryon
-fraction have good agreement with each other in the whole mass range
+Meanwhile, \citet{Voort16} have similar result produced by zoom-in 
+cosmological hydrodynamic simulation suit FIRE which has 16 galaxies 
+with similar halo mass range.
+Fig.~\ref{fig:fire_com} compares baryon and stellar fraction with 
+\citet{Voort16} and \citet{Christensen}, we derive
+new baryonic mass and stellar mass within R$_{500}$ and R$_{100}$
+to make sure the ratios compared in each panel have same definitions with
+ratios from other simulation suites. The baryon fraction in NIHAO simulations
+have good agreement with both of the simulation suite in the whole mass range
 where NIHAO simulations explored. For the massive haloes with 
@@
 have larger reduced baryon fraction which may hint that the baryon
-fraction will decrease as the halo mass increases in large mass range.}
+fraction will decrease as the halo mass increases in large mass range.
+For stellar fraction, \citet{Voort16} shows a almost same result with
+our work, even at low mass range, the two galaixes may suggest the 
+large scatter as we produced.}
 

### 2016-09-12 ms_nihao_budget.tex
enlarge the axis label and reproduce the comparason figure

@@
 Fig.~\ref{fig:fire_com} compares baryon and stellar fraction with 
-\citet{Voort16} and \citet{Christensen}, we derive
+\citet{Voort16} and \citet{Christensen16}, we derive
 new baryonic mass and stellar mass within R$_{500}$ and R$_{100}$
@@
 have good agreement with both of the simulation suite in the whole mass range
-where NIHAO simulations explored. For the massive haloes with 
+where NIHAO simulations explored. The massive haloes with 
 M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
@@
 our work, even at low mass range, the two galaixes may suggest the 
-large scatter as we produced.}
+large scatter as we produced. However, \citet{Christensen16} predicts
+one magnitude higher stellar fraction than what we found at the halo 
+mass range belowe $10^{11.5} \Msun$, which is expected by the
+comparason with abundance-matching-derived fits shown in Fig. 3 in
+their paper.}
 

### 2016-09-21 ms_nihao_budget.tex
Version revised by Aaron

--- 2016-08-25 ms_nihao_budget.tex
@@
 
-\voffset=-0.8in
+\voffset=-0.4in
 
@@
 
-\date{to be submitted to MNRAS}
-
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2015}
+\date{submitted to MNRAS}
+
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2016}
 
@@
   fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
-  find that all of our haloes are missing baryons. The missing
-    mass been relocated past 2 virial radii, and {\bf cool gas dominates
-  corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$) while the 
-  warm-hot gas dominates dominates at high mass (M$_{200} \gta 3 \times 10^{11} \Msun$)}.
-   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
-  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
-  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
-  30\%$ missing, consistent with recent observational estimates.
-  {\bf Moreover, these more massive haloes reproduce the observed 
-  fraction of cold, warm-hot and hot gas, the fraction of cool gas we
-  predict is significant lower than the observation from COS-HALOs,
-  but agree with the analysis of \citet{Stern16}}.
+  find that all of our haloes are missing baryons. The missing mass
+  has been relocated past 2 virial radii, and {\bf cool gas dominates
+    the corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$)
+    while the  warm-hot gas dominates dominates at high mass (M$_{200}
+    \gta 3 \times 10^{11} \Msun$)}.  Haloes of mass $\Mhalo\sim
+  10^{10}\Msun$ are missing $\sim 90\%$ of their baryons.  More
+  massive haloes ($\Mhalo\sim 10^{12}\Msun$) retain a higher fraction
+  of their baryons, with $\sim 30\%$ missing, consistent with recent
+  observational estimates.  {\bf Moreover, these more massive haloes
+    reproduce the observed  fraction of cold, warm-hot and hot gas.
+    The fraction of cool gas we predict (0.11) is significantly lower
+    than the observation from COS-HALOs (0.3-0.47), but agrees with
+    the alternative analysis of \citet{Stern16}}.
 \end{abstract}
@@
 and hot (ionized) gas. The theories of galaxy formation can predict
-the amount of mass in these different states, which can in turn be tested by
-observational constraints.
+the amount of mass in these different states, which can in turn be
+tested by observational constraints.
 
@@
   b}/\Omega_{\rm m}\simeq 0.15$ (The Planck Collaboration 2014).
-However, the cold baryonic mass density implied by several galaxy baryon
-estimates {\bf (mainly about stars and cold gas)} is only 3-8\% of 
-the big bang nucleosynthesis expectation
-\citep{Persic92, Fukugita98,  Bell03, McGaugh10}.  The majority of the
-cosmic baryons are thought to be in the form of hot gas around or
-between galaxies \citep{Cen09}. Until recently only a fraction of
-these baryons had been detected \citep{Bregman07, Shull12}.  This
-discrepancy is referred to as the ``missing baryon problem''.
-Several theoretical studies with cosmological simulations
-have constrained the phase of
-the potential reservoirs of the missing baryons {\bf in intergalactic
-medium (IGM), and find a large fraction of the baryons with low density
-and high temperature resides between the galaxies}
+However, the cold baryonic mass density implied by several galaxy
+baryon estimates {\bf (mainly stars and cold gas)} is only 3-8\% of
+the big bang nucleosynthesis expectation \citep{Persic92, Fukugita98,
+  Bell03, McGaugh10}.  The majority of the cosmic baryons are thought
+to be in the form of hot gas around or between galaxies
+\citep{Cen09}. Until recently only a fraction of these baryons had
+been detected \citep{Bregman07, Shull12}.  This discrepancy is
+referred to as the ``missing baryon problem''.  Several theoretical
+studies with cosmological simulations have constrained the phase of
+the potential reservoirs of the missing baryons {\bf in the
+  intergalactic medium (IGM), and find a large fraction of the baryons
+  with low density and high temperature resides between galaxies}
 \citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.
 
-The circum galactic medium (CGM) is {\bf another}  major potential  reservoir
-of the missing baryons. \hi{} and metal absorption lines are
+The circum galactic medium (CGM) is {\bf another}  major potential
+reservoir of the missing baryons. \hi{} and metal absorption lines are
 expected  to signpost such diffuse baryonic content. \hi{} is mainly
-from gas with temperature T $\sim 10^4$ K so that it is able to
-detect cold gas in the CGM.  Meanwhile, theoretical work has
-predicted that a substantial  portion of the CGM is in the warm or
-hot phase with temperature T $> 10^{4.5}$ K.  Gas enters this phase
-through photoionization, accretion shocks or shocks caused by
-galactic winds \citep{Voort12}. Such dilute halo gas is at T$\sim
-10^{4.5-7}$ K, so the detection is dominated by metal lines,
-e.g. \ovi{}.  Recent advances in the detection of gas in the CGM
-have come  from the COS survey \citep{Tumlinson11, Tumlinson13,
-Thom12,  Werk12, Werk13}.  On the scale of Milky Way mass haloes
-$\Mhalo \sim 10^{12}\Msun$ a significant amount of warm ($10^4 < T <
-10^7$K) gas has been detected \citep{Werk14}, accounting for 33-88\%
-of the baryon budget. In the future such observations will be extended
-to a wider range of halo masses.  A number of large volume
-cosmological simulations \citep{Ford13, Ford15, Suresh15b,
-  Oppenheimer16} and zoom-in cosmological simulations
-\citep{Stinson12, Hummels13, Shull14} have given 
-predictions for the
-\hi{} and \ovi{} absorption line. \citet{Gutcke16} compared the
-column density profile of \ovi{} and \hi{} in the CGM of galaxies
-from the NIHAO \citep{Wang15} cosmological hydrodynamical
-simulation suite with observations, studied the covering fraction of
-dense \hi{}, looked at the shape of the CGM and its chemical
-composition. The conclusion shows {\bf the simulation can reproduce 
-the observational covering fraction and column density profile
-of cool \hi{} well, and echo observed \ovi{} column density trend.
-As commonly in other simulations, however, the column density of \ovi{}
+from gas with temperature T $\sim 10^4$ K so that it is able to detect
+cold gas in the CGM.  Meanwhile, theoretical work has predicted that a
+substantial  portion of the CGM is in the warm or hot phase with
+temperature T $> 10^{4.5}$ K.  Gas enters this phase through
+photoionization, accretion shocks or shocks caused by galactic winds
+\citep{Voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, so
+the detection is dominated by metal lines, e.g. \ovi{}.  Recent
+advances in the detection of gas in the CGM have come  from the COS
+survey \citep{Tumlinson11, Tumlinson13, Thom12,  Werk12, Werk13}.  On
+the scale of Milky Way mass haloes $\Mhalo \sim 10^{12}\Msun$ a
+significant amount of warm ($10^4 < T < 10^7$K) gas has been detected
+\citep{Werk14}, accounting for 33-88\% of the baryon budget. In the
+future such observations will be extended to a wider range of halo
+masses.  A number of large volume cosmological simulations
+\citep{Ford13, Ford15, Suresh15b, Oppenheimer16} and zoom-in
+cosmological simulations \citep{Stinson12, Hummels13, Shull14} have
+given  predictions for the \hi{} and \ovi{} absorption
+line. \citet{Gutcke16} compared the column density profile of \ovi{}
+and \hi{} in the CGM of galaxies from the NIHAO \citep{Wang15}
+cosmological hydrodynamical simulation suite with observations,
+studied the covering fraction of dense \hi{}, looked at the shape of
+the CGM and its chemical composition. {\bf The simulations
+  reproduce  the observational covering fraction and column density
+  profile of cool \hi{} well, and recover the observed trends of
+  \ovi{} column density with luminosity and impact parameter. In
+  common with other simulations, however, the column density of \ovi{}
   is lower and the extent of optically thick \hi{} is smaller than
@@
 baryon fractions are lower at lower redshift, after powerful
-outflows at intermediate redshift z $\approx 0.5-2$ remove a large
-amount of gas from the halo. \citet{Voort16} found baryon fraction
-and gas fraction are reduced compared to the cosmic mean baryon
-fraction, and low mass haloes reduce larger since feedback can
-easily expel gas from it, which is consistent with existing 
-observation.}
+outflows at intermediate redshift $z \approx 0.5-2$ remove a large
+amount of gas from the halo. \citet{Voort16} found the baryon fraction
+and gas fraction are reduced compared to the cosmic baryon
+fraction, especially in low mass haloes.}
 %  
@@
 a sample of 88 zoom-in galaxy formation simulations from the NIHAO
-project.
-Reproducing the stellar mass content in dark matter haloes both
-today and in the past has been a formidable challenge for cosmological galaxy
-formation simulations \citep{Weinmann12, Hopkins14}. Even the latest
-state-of-the art simulations have trouble: the ILLUSTRIS simulation
-\citep{Vogelsberger14} strongly overpredicts the stellar masses in
-dwarf galaxy haloes $(M_{200} \lta 10^{11}\Msun)$, while the EAGLE
-simulations \citep{Schaye15} underpredict the peak of the star
-formation efficiency in halos of mass $M_{200}\sim 10^{12}\Msun$. In
-contrast, the NIHAO galaxies are consistent with the stellar mass
-vs halo mass relations from halo abundance matching since redshift
-$z\sim 4$ \citep{Wang15}, the galaxy star formation rate vs stellar
-mass relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
-stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore, the
-simulations make plausible predictions for the mass fractions and
-physical locations of the warm and hot gas components.  We find that
-all the haloes contain less baryons than expected according to the
-cosmic baryonic fraction, but the missing fraction is strongly mass
-dependent.
+project.  Reproducing the stellar mass content in dark matter haloes
+both today and in the past has been a formidable challenge for
+cosmological galaxy formation simulations \citep{Weinmann12,
+  Hopkins14}. Even the latest state-of-the art simulations have
+trouble: the ILLUSTRIS simulation \citep{Vogelsberger14} strongly
+overpredicts the stellar masses in dwarf galaxy haloes $(M_{200} \lta
+10^{11}\Msun)$, while the EAGLE simulations \citep{Schaye15}
+underpredict the peak of the star formation efficiency in halos of
+mass $M_{200}\sim 10^{12}\Msun$. In contrast, the NIHAO galaxies are
+consistent with the stellar mass vs halo mass relations from halo
+abundance matching since redshift $z\sim 4$ \citep{Wang15}, the galaxy
+star formation rate vs stellar mass relation since $z\sim 4$
+\citep{Wang15}, and the cold gas mass vs stellar mass relation at
+$z\sim 0$ \citep{Stinson15}.  Therefore, the simulations make
+plausible predictions for the mass fractions and physical locations of
+the warm and hot gas components.  We find that all the haloes contain
+less baryons than expected according to the cosmic baryonic fraction,
+but the missing fraction is strongly mass dependent.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% SECTION 2 SIMULATIONS
@@
 In this study we use simulations from the NIHAO (Numerical
-Investigation of a Hundred Astrophysical Objects) project \citep{Wang15}.  
-The initial conditions are created to keep the same numerical
-resolution across the whole mass range with typically a million dark
-matter particles inside the virial radius of the target halo at 
-redshift $z=0$.  The halos to be re-simulated at higher resolution
-with baryons have been extracted from 3 different pure N-body
-simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
+Investigation of a Hundred Astrophysical Objects) project
+\citep{Wang15}.   The initial conditions are created to keep the same
+numerical resolution across the whole mass range with typically a
+million dark matter particles inside the virial radius of the target
+halo at  redshift $z=0$.  The halos to be re-simulated at higher
+resolution with baryons have been extracted from 3 different pure
+N-body simulations with a box size of 60, 20 and 15 $h^{-1}$ Mpc
 respectively.  We adopted the  latest compilation of cosmological
-parameters from the Planck  satellite \citep{Planck14}. 
-More information on the collisionless parent simulations,
-{\bf the force softenings and particle masses for the highest 
-refinement level for each simulation} and
-sample  selection can be found in \citet{Dutton14} and \citet{Wang15}
+parameters from the Planck  satellite \citep{Planck14}.  More
+information on the collisionless parent simulations, {\bf the force
+  softenings and particle masses for the highest refinement level for
+  each simulation} and sample  selection can be found in
+\citet{Dutton14} and \citet{Wang15}.
 
@@
 
-khe star formation and feedback modeling follows what
-was used in the MaGICC simulations \citep{Stinson13}.  
-{\bf The gas converts into stars according to the Kennicutt-Schmidt Law
-when it satisfies a temperature and density threshold. Stars feed both
-metals and energy back into the ISM gas surrounding the region where
-they formed. SN feedback is implemented using the blastwave formalism
-described in \citet{Stinson06}. Pre-SN feedback is an effort to consider
-radiation energy from massive stars which is am important complementary
-to physcial model for stellar feedback. Heating is introduced immediately
-after massive stars form based on how much star light is radiated. 
-Our simulations use thermal feedback to provide pressure support and 
-increase gas temperature above the star formation threshold to
-decrease star formation.}
-There are two
-small changes in NIHAO simulations: The change in  number of neighbors
-and the new combination of softening length and  particle mass increases
-the threshold for star formation from  9.3 to 10.3
+The star formation and feedback modeling follows what was used in the
+MaGICC simulations \citep{Stinson13}.   {\bf The gas is converted into
+  stars according to the Kennicutt-Schmidt Law when it satisfies a
+  temperature and density threshold. Stars feed both metals and energy
+  back into the ISM gas surrounding the region where they formed. SN
+  feedback is implemented using the blastwave formalism described in
+  \citet{Stinson06}. Pre-SN feedback is an attempt to consider
+  radiation energy from massive stars. Heating is introduced
+  immediately after massive stars form based on how much star light is
+  radiated.  Our simulations use thermal feedback to provide pressure
+  support and  increase gas temperature above the star formation
+  threshold, and thus to decrease star formation.}  There are two
+small changes in NIHAO simulations compared to MaGICC:
+The change in  number of neighbors
+and the new combination of softening length and  particle mass
+increases the threshold for star formation from  9.3 to 10.3
 cm$^{-3}$, the increase of pre-SN feedback efficiency $\epsilon_{\rm
-  ESF}$, from 0.1 to 0.13.  The more detail on star formation and
+  ESF}$, from 0.1 to 0.13.  More details on the star formation and
 feedback modeling can be found in \citet{Wang15}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% SECTION 3 RESULTS
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Results}
-%\label{sec:results}
 
@@
 \centerline{
-%  \psfig{figure=barbudget_linear_v3.eps,width=0.5\textwidth}}
-%\centerline{
-%  \psfig{figure=barbudget_v3.eps,width=0.5\textwidth}
   \psfig{figure=barbudget_linearlog.eps,width=0.48\textwidth}
@@
 %% FIGURE 2
-\begin{figure}
+\begin{figure*}
 \centerline{
-  \psfig{figure=m500c_frac.eps,width=0.48\textwidth}
+  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
 }
-\caption{{\bf Baryon fraction within R$_{500}$ comparing with \citet{Voort16}.
-   The blue points are from NIHAO simulations and the red pentagons are from
-   FIRE simulations.}}
+\caption{{\bf Comparison between baryon (upper panels) and stellar
+    fractions (lower panels) in the NIHAO simulations (blue circles)
+    with simulations from \citet{Voort16} (left, red pentagons) and
+    \citet{Christensen16} (right, purple pentagons).}}
 \label{fig:fire_com}
-\end{figure}
-
-%% FIGURE 3
-\begin{figure}
-\centerline{
-  \psfig{figure=budget_res.eps,width=0.48\textwidth}
-}
-\caption{{\bf Linear fractional baryon content of our NIHAO simulations  as a
-  function of halo mass color coded by number of all particles per halo.}}
-\label{fig:budget_res}
-\end{figure}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% SECTION 3 BARYON BUDGET
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 grey area is the one sigma scatter around the mean value  from
-\citet{Kravtsov14}.
-Fig.~\ref{fig:budget} shows that all haloes in our study contain less
-than the universal fraction of baryons. The upper panel uses a linear
-y-axis scale, which highlights the large amount of baryons that are
-missing, especially in low mass haloes. The logarithmic scale in the
-lower panel highlights the power-law nature of the relations.
+\citet{Kravtsov14}.  Fig.~\ref{fig:budget} shows that all haloes in
+our study contain less than the universal fraction of baryons. The
+upper panel uses a linear y-axis scale, which highlights the large
+amount of baryons that are missing, especially in low mass haloes. The
+logarithmic scale in the lower panel highlights the power-law nature
+of the relations.
 
@@
 the form of gas, while in the highest mass haloes we study
-($\Mhalo\sim 10^{12}\Msun$) {\bf a substantial amounts of gas
-forms stars}.
-
-{\bf \citet{Christensen16} run twenty galaxy simulations spanning the mass range
-from $10^{9.5} - 10^{12} \Msun$ using zoom-in cosmological hydrodynamic 
-simulation code and didn't only reproduce the stellar mass - halo mass
-relation but also showed a similar baryon fraction relation, e.g. in 
-L$^*$ galaxies, the fraction is reduced by 20\% while in galaxies with
-halo mass $< 10^{10} \Msun$ there can be as large as an 80\% mass reduction.
-This suggests that the potential well of the halo regulates the baryon
-fraction.
-To compare with baryon fraction in \citet{Voort16}, we derive
-the M$_{500}$ and R$_{500}$ to recalculate the ratio between 
-baryon fraction to the universal fraction of baryons. The baryon
-fraction have good agreement with each other in the whole mass range
-where NIHAO simulations explored. For the massive haloes with 
-M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
-reduced baryon fraction and four more massive galaxies from FIRE
-have larger reduced baryon fraction which may hint that the baryon
-fraction will decrease as the halo mass increases in large mass range.}
-
-Since most of the haloes we study are above the mass where the cosmic UV
-background prevents gas from cooling, the missing baryons have most
+($\Mhalo\sim 10^{12}\Msun$) {\bf a substantial amount of gas
+has been turned into stars}.
+
+Since most of the haloes we study are above the mass where the cosmic
+UV background prevents gas from cooling, the missing baryons have most
 likely been ejected from the central galaxies in supernova/stellar
@@
 and hence there is proportionally less energy available to drive an
-outflow, they have expelled a larger fraction of their baryons,
-consistent with expectations from energy driven gas outflows
-\citep[e.g.,][]{Dutton12}.
+outflow, they have expelled a larger fraction of their baryons. {\bf
+  This is consistent with expectations from energy driven gas
+  outflows, where the lower star formation efficiency is more than
+  compensated by the shallower potential wells of lower lower mass
+  halos according the mass loading factor and circular velocity 
+  relaion $\eta \propto V^{-2}$
+   \citep[e.g.,][]{Dutton12, Christensen16}.}
 
@@
 sharp the transition is from the lower to the higher ends.
-The best fit parameters are as follows:
+Giving all points equal weight, the best fit parameters are as follows:
 \begin{eqnarray}
@@
 \end{eqnarray}
+
+{\bf The three most massive galaxies in the NIHAO suite have fairly high
+  stellar masses compared to abundance matching results (see blue
+  filled circles in Fig.~\ref{fig:budget}), and are thus possibly
+  overcooled.  However, they don't significantly bias the baryon
+  fraction fitting formula since the high mass slope ($M_{200} >
+  10^{11}\Msun$) is constrained by $\sim 40$ other haloes.}
+
 The green shaded region indicates the scatter about the best fit line,
@@
 $7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
-and 0.0518 for halo mass in
+and 0.052 for halo mass in
 $3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.
 
-As might be expected, haloes with the highest masses we study have
-high baryon fractions with relatively  small scatter. As halo mass
-decreases, the baryon fraction decreases and the scatter increases,
-consistent with expectations from outflows driven by stellar
-feedback {\bf since the energy-driven wind model determined that
-mass loading factors show a power-law dependency on circular velocity
-, with an exponent of $\approx -2$, \eg \citet{Christensen16}, 
-which means the greater efficiency of small galaxies at 
-driving outflows is simply a result of their shallower potential 
-well and the increasing scatters come from the increasing scatters of
-stellar mass halo mass relation in lower mass range.}
-At the lowest halo masses we study, below $10^{10}\Msun$,
-the scatter starts to decrease. By contrast the scatter in the stellar
-mass fraction increases below this scale. Thus it seems unlikely that
-stellar feedback is primarily responsible for the low baryon
+As might be expected, haloes with the highest masses  we study ($\sim
+10^{12}\Msun$) have high baryon fractions ($\sim 0.7$) with relatively
+small scatter (0.05 dex). As halo mass decreases, the baryon fraction
+decreases and the scatter increases reaching a maximum of $\sim 0.24$
+dex in haloes of mass $\sim 4\times10^{10}\Msun$.  However, at the
+lowest halo masses we study, below $10^{10}\Msun$, the scatter starts
+to decrease. By contrast the scatter in the stellar mass fraction
+increases below this scale. Thus it seems unlikely that stellar
+feedback is primarily responsible for the low baryon
 fractions. Rather, we suggest an increased importance of the UV
 background, which heats gas to above the virial temperature, thus
-preventing it from collapsing into the low mass haloes. 
-{\bf Although the three most massive galaixes in NIHAO suite have fairly 
-high stellar masses (see blue filled circles in Fig.~\ref{fig:budget}),
-they don't have large deviations apart from the fitting baryon fraction, 
-and in the comparason with FIRE (see Fig.~\ref{fig:fire_com}), these
-three objects seem to hint the trend on massive galaxy end associated
-with the data from \citet{Voort16}. Moreover, the fitting relation 
-about the baryon fraction is not sensitive to these three most massive 
-galaxies as well since they have equal weight with other more than 
-80 galaxies to shape the fitting curve.}
-
-{\bf Since the resolution is one key parameter in simulation, and one
-can imagine that with increased resolution, higher densities can be 
-achieved in the CGM, potential leading to more cooling and larger
-cold/cool gas fraction,
-the convergence of the baryonic fraction predicted by NIHAO suite
-is worth to estimate. Fig.~\ref{fig:budget_res} shows cold and cool
-gas (HI + HeI) fraction color coded by number of dark matter particles 
-per halo. In the plot, the number of dark matter partilce per halo spans 
-2 magnitudes and has no correlation with cold and cool gas fraction. 
-Therefore, we can conclude the resolution of NIHAO suite is 
-proper to study the fractional baryon content.}
-
-\subsection{Mass budget of the corona}
-\label{sec:corona}
-
-%% FIGURE 2
+preventing it from collapsing into the low mass haloes. {\bf The
+  baryon fractions are thus controlled primarily by the halo masses,
+  and thus are independent of the large scatter in the star formation
+  efficiency.}
+
+%% FIGURE 3
 \begin{figure*}
@@
 
+\subsubsection{Comparison with other zoom-in simulations}
+{\bf In Fig.~\ref{fig:fire_com} we compare the NIHAO results for the
+  stellar and baryonic mass fractions with other recent
+  state-of-the-art zoom-in simulations from \citet{Voort16} and
+  \citet{Christensen16}.  Since these authors both use different halo
+  mass definitions than we adopt here, we re-calculate the NIHAO
+  results using a virial radius defined at $500\times$ critical
+  density (left panels) and $100\times$ critical density (right
+  panels).  The simulations analyzed in \citet{Voort16} are from the
+  FIRE project \citep{Hopkins14}, which uses a different
+  hydrodynamical code and different sub-grid model for star formation
+  and feedback. The simulations analyzed in \citet{Christensen16} use
+  a similar code as NIHAO, i.e.,  {\sc gasoline}, but with important
+  differences. NIHAO uses an upgraded version that improves mixing
+  \citep{Keller14}, and includes stronger feedback which was found to
+  be necessary to delay star formation at early times
+  \citep{Stinson13}. Despite these different codes employed, the
+  baryon fractions in the three sets of simulations are in remarkably
+  good agreement.
+
+For the massive haloes with  M$_{500} > 10^{12} \Msun$, there are
+three galaxies from NIHAO and four from FIRE.  There is a hint that
+more massive haloes have lower baryon fractions.  Of course the caveat
+here is that neither NIHAO or FIRE includes AGN feedback, which could
+have a significant impact on the gaseous content of these haloes.
+
+For the stellar fractions, \citet{Voort16} shows almost the same
+result as our work. Even at the low mass end, their two lowest mass
+galaxies may suggest the  large scatter as found in NIHAO.  However,
+\citet{Christensen16} predicts one magnitude higher stellar fractions
+than what we find for halo  masses below $10^{11.5}
+\Msun$. This difference is likely due to the additional early stellar
+feedback included in the NIHAO version of gasoline.
+
+In summary, while the stellar mass fractions are dependent on the
+sub-grid models, the baryon fractions (for haloes in the mass range
+$10^{10}\lta M_{200} \lta 10^{12}\Msun$) appear insensitive to the
+details of the simulation code. In particular all three codes predict a
+greater fraction of missing baryons in lower mass haloes. This
+suggests that the potential well of the halo regulates the baryon
+fraction more than the strength of the feedback.  }
+
+\subsection{Mass budget of the corona}
+\label{sec:corona}
+
 In Fig.~\ref{fig:corona}, we present the radial distribution of
 gas in different phases at $z=0$, normalized to the total baryonic
-mass profile, such that, in the region far away from central galaxy
+mass profile, such that, in the region far away from the central galaxy
 where the stars are rare, for a given halo the four phases add up to
-unity, {\bf each line is colour coded to the virial mass}.  
-All simulations share a common attribute.  The cold gas (T$<
-10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
-where most stars in galaxies form.  In contrast, the cool ($10^4$K
-$<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
+unity, {\bf each line is colour coded by the virial mass}.  
+All simulations share a common attribute.  The cold gas (T$<10^4$K)
+is mostly located  near the center  ($R<0.2R_{200}$)
+where most stars in galaxies form.  In contrast, the cool ($10^4$K$<$T$<10^5$K)
+and  warm-hot ($10^5$K$<$T$<10^7$K) gas are
 located at large distances with roughly constant fractions up to 2
@@
 Despite these similarities, we find a considerably higher proportion
-of cool gas in lower mass galaxies (M$_{200} < 10^{11} \Msun$)
-in the whole corona region.  For higher mass galaxies, warm-hot gas
-dominates the corona  which signals {\bf stronger virial shock} and
-higher efficiency  of feedback.
-Even beyond the virial radius, the cool and warm-hot gas has similar
-features as the gas within virial radius which reveals the gas
-surrounding galaxies within large distance is the major reservoir of
-baryons.
+of cool gas in lower mass galaxies (M$_{200} < 10^{11} \Msun$) in the
+whole corona region.  For higher mass galaxies, warm-hot gas dominates
+the corona  which signals {\bf stronger virial shocks} and higher
+efficiency  of feedback.  Even beyond the virial radius, the cool and
+warm-hot gas has similar features as the gas within virial radius
+which reveals the gas surrounding galaxies within large distances is
+the major reservoir of baryons.
 
@@
 
-Each solid curve represents a halo, and the curves are coloured by
-their halo mass (red for high masses to blue for low masses).  Broadly
-speaking, the curves have a similar shape, with a normalization that
-depends on halo mass. They have a cusp in  the central region where the
-stars and cold gas dominate, then become flat in the outer region.
-More massive haloes have higher baryon fractions at all radii.  At
-small radii, the baryon to dark matter ratio is higher than the cosmic
-value due to gas dissipation.  Even beyond the virial radius, there is
-little change in the baryon fraction up to 2 virial radii.  We thus
-conclude that the missing baryons are well outside of the virial
-radius.
-
-{\bf Two cosmological hydrodynamic simulations in \citet{Ford15} 
-which employed two prescriptions for galactic 
-outflow models to compare with COS-Halos showed this cumulative
-baryon fraction profile for COS-Halos matched sample of galaxies.
-One hybrid energy/momentum driven winds model ("ezw" model) makes up to
-65\% of all baryons inside the halo. This is broadly consistent with
-estimates of baryonic mass derived from \citet{Werk14} and our 
-finding in Fig.~\ref{fig:budget}. Comparing the cumulative baryon
-fraction profile in detail, Fig.10 in \citet{Ford15} shows the baryon
-fraction within 0.1$\Rvir$ is only $\sim 30\%$ and the fraction 
-gradually increases to 65\% at $\Rvir$ while the profile of galaxies
-with halo mass below $10^{11} \Msun$ in Fig.~\ref{fig:rps} have 
-similar feature, the more massive galaxies all have roughly flat slopes.
-The simplified outflow model (constant wind model or "cw" model) shows
-lower fraction at all radii inside $\Rvir$ even though "ezw" model
-and "cw" model generally gives similar observational absorption 
-line properties. This suggests that the profile of cumulative baryon
-fraction, as a complementary of total amount observation of CGM,
- is important to distinguish between competing outflow models
-that often closely relate to the feedback models.
-}
-%% FIGURE 3
+%% FIGURE 4
 \begin{figure}
@@
 
+Each solid curve represents a halo, and the curves are coloured by
+their halo mass (red for high masses to blue for low masses).  Broadly
+speaking, the curves have a similar shape, with a normalization that
+depends on halo mass. They have a cusp in  the central region where
+the stars and cold gas dominate, then become flat in the outer region.
+More massive haloes have higher baryon fractions at all radii.  At
+small radii, the baryon to dark matter ratio is higher than the cosmic
+value due to gas dissipation. {\bf Beyond 0.5 virial radii, all haloes
+  are missing baryons.}  Even beyond the virial radius, there is
+little change in the baryon fraction up to 2 virial radii.  We thus
+conclude that the missing baryons are well outside of the virial
+radius.
+
+{\bf \citet{Ford16} compare results for the cumulative baryon profile
+  from two cosmological hydrodynamic simulations which employed
+  different prescriptions for galactic  outflow models. They
+  constructed samples of simulated galaxies with a similar
+  distribution of stellar masses to that of COS-Halos.
+
+  In the hybrid energy/momentum driven winds model (``ezw'') 65\% of
+  all available baryons are inside the halo. This is broadly
+  consistent with estimates of baryonic mass derived from
+  \citet{Werk14} and our  finding in Fig.~\ref{fig:budget}. Comparing
+  the cumulative baryon fraction profile in detail, Fig.10 in
+  \citet{Ford16} shows the baryon fraction within 0.1$\Rvir$ is only
+  $\sim 30\%$ and the fraction  gradually increases to 65\% at
+  $\Rvir$. In the NIHAO simulations the profile of galaxies with halo
+  masses below $10^{11} \Msun$ in Fig.~\ref{fig:rps} have  similar
+  features, the more massive galaxies all have roughly flat slopes.
+
+The simplified constant wind outflow model (``cw'') shows
+a lower fraction at all radii inside $\Rvir$, even though the ``ezw'' 
+and ``cw'' models generally gives similar observational absorption 
+line properties. This suggests that the cumulative baryon
+fraction profile is complementary to the total amount of CGM gas for
+distinguishing between competing outflow models.
+}
+
 To estimate how far the baryons escape, we measured the radius,
-$\Rbar$, within which the total baryon mass equals to the fiducial
+$\Rbar$, within which the total baryon mass equals the fiducial
 baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
-the true extent of the missing baryons since the baryon mass
-includes gas and stars that belong to nearby lower mass haloes.
+the true extent of the missing baryons since the baryon mass includes
+gas and stars that belong to nearby lower mass haloes.
 Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
-function of the virial mass.  We find the baryon radius generally
-increases with virial mass. {\bf when normalized by the virial
-radius, the distance baryons are ejected span a similar range of radii
-$\Rbar/R_{200}\sim 2-6$ and gradually decrease as halo mass 
-rise, even the majority of massive galaxies have $\Rbar \sim \Rvir$.}
-
-%% FIGURE 4
+function of the virial mass. In physical units, we find that the
+baryon radius generally increases with virial mass. {\bf When
+  normalized by the virial radius, the distance baryons are ejected
+  gradually decreases as halo mass increases, varying from
+  $\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$
+  to $\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.}
+
+%% FIGURE 5
 \begin{figure}
@@
 
-%% FIGURE 5
+%% FIGURE 6
 \begin{figure*}
@@
 }
-\caption{Mass fraction of gas in four phases (relative to the fiducial
-  baryonic mass within the virial radius)
-  {\bf gas inside the virial radius (filled blue points) and between 
-   virial and baryon radius (open red points)}, respectively. Cool gas is
-  the dominant component of {\bf the fiducial baryonic mass within the 
-  virial radius for most galaxies ($10^{10} < M/\Msun < 10^{12}$), cold 
-   and warm-hot gas is majority only for the galaxies at lower and higher
-   mass end.}}
+\caption{{\bf Mass fraction of gas in three phases (relative to the
+    fiducial baryonic mass within the virial radius) inside the
+    virial radius (filled blue points) and between  virial and baryon
+    radius (open red points), respectively. Cool gas is the dominant
+    component of the fiducial baryonic mass for most galaxies
+    ($10^{10} < M_{200}/\Msun < 10^{12}$). Cold  and warm-hot gas is
+    the majority only for galaxies at the low and high mass
+    ends, respectively.}}
 \label{fig:inout}
@@
 
-In Fig.~\ref{fig:inout}, we show the mass fractions of gas (in four
+In Fig.~\ref{fig:inout}, we show the mass fractions of gas (in three
 phases) inside the virial radius (filled blue points) and between the
@@
 
-{\bf Observations can gain information of CGM from absorption lines
-and emission lines. Although emission lines allow us to direct obtain
+{\bf Observations can gain information of CGM from absorption
+and emission lines. Although emission lines allow us to directly obtain
 a 3D picture of the distribution of gas in the CGM, emission line studies
-preferentially probe the dense gas closer to galaxies since gas 
-emissivity scales with the square of density. The situation is changing
-by building current facilities, e.g.~\citet{Hayes16}, absorption line,
-however, is the most common observational constraints on the physical
-state of the CGM.}
-The COS-HALOs survey is
-filling in details about the $z \sim 0$ CGM \citep{Peeples14,
-  Tumlinson11, Tumlinson13, Werk12, Werk13, Werk14}.  For the CGM of
-low-redshift $\sim L^*$ galaxies ($\Mstar\sim 10^{10.5}\Msun$),
-\citet{Tumlinson13} and \citet{Peeples14} constrain the mass of  the
-warm-hot CGM ($T \sim 10^{5-7}$K), \citet{Werk14} provides a strict
-lower limit to the mass of cool material ($T \sim 10^{4-5}$K) in the
-CGM of these galaxies.  In a study using X-rays,  \citet{Anderson13}
-place a constraints on the mass of  hot gas ($T > 10^7$K) residing in
-the extended hot halos.
-
-In Fig.~\ref{fig:comparison}, we show the mean values and standard deviation
-of the mass fraction of stars and different components of gas in our
-most massive galaxies ($3.49 \times 10^{11} \Msun$ $<$ M$_{200}$ $<$ 
-$3.53 \times 10^{12} \Msun$) with blue points and error bars.
-The gas is assigned to a range of temperature bins: 
-cold gas (T $< 10^4$ K), cool gas ($10^4$ K $<$ T $< 10^5$ K), 
-warm gas ($10^5$ K $<$ T $< 10^7$ K) and hot gas (T $> 10^7$ K).
-The observational constraints are shown with the same colour scheme
-in Fig. 11 in \citet{Werk14}.
-
-%% FIGURE 6
-\begin{figure}
+preferentially probe the dense gas closer to galaxies, since gas 
+emissivity scales with the square of density. While the situation is improving
+with new facilities, e.g.~\citet{Hayes16}, absorption lines are  the
+most common observational constraints on the physical state of the CGM.}
+
+The COS-HALOs survey is filling in details about the CGM at low
+redshift \citep{Peeples14, Tumlinson11, Tumlinson13, Werk12, Werk13,
+  Werk14}.  For the CGM of low-redshift $\sim L^*$ galaxies
+($\Mstar\sim 10^{10.5}\Msun$), \citet{Tumlinson13} and
+\citet{Peeples14} constrain the mass of  the warm-hot CGM ($T \sim
+10^{5-7}$K), \citet{Werk14} provides a strict lower limit to the mass
+of cool material ($T \sim 10^{4-5}$K) in the CGM of these galaxies.
+In a study using X-rays, \citet{Anderson13} place a constraints on the
+mass of  hot gas ($T > 10^7$K) residing in the extended hot halos.
+These observational constraints are shown in Fig.~\ref{fig:comparison}
+with the same colour scheme as in Fig.11 of \citet{Werk14}.  The
+stellar mass fractions are based on halo abundance matching as
+described in \citet{Kravtsov14}, while the cold disk gas mass comes
+from \citet{Dutton11}.
+
+%% FIGURE 7
+\begin{figure*}
 \centerline{
-  \psfig{figure=budget.eps,width=0.5\textwidth}
+  \psfig{figure=budget.eps,width=0.8\textwidth}
 }
-\caption{Baryonic budget 
-  of NIHAO haloes of mass $3.5\times 10^{11} < M_{200}/\Msun <
-  3.5 \times 10^{12}$ (blue points 
-  with 1$\sigma$ error bars) compared with observations of 
-  $M_{200} \sim 10^{12}\Msun$ haloes (shaded regions). There is good agreement, except for the cool gas which has two conflicting measurements.
-  }
+\caption{Baryonic budget  of NIHAO haloes of mass $3.5\times 10^{11} <
+  M_{200}/\Msun < 3.5 \times 10^{12}$ (blue points  with 1$\sigma$
+  error bars) compared with observations of  $M_{200} \sim
+  10^{12}\Msun$ haloes (shaded regions). There is good agreement,
+  except for the cool gas which has two conflicting measurements:
+  \citet[][upper]{Werk14} upper, \citet[][lower]{Stern16}.  }
 \label{fig:comparison}
-\end{figure}
+\end{figure*}
+
+The blue points and error bars show the mean values and standard
+deviation of the mass fraction of stars and different components of
+gas in our most massive galaxies ($3.49 \times 10^{11} \Msun$ $<$
+M$_{200}$ $<$  $3.53 \times 10^{12} \Msun$).  The gas is assigned to a
+range of temperature bins:  cold gas (T $< 10^4$ K), cool gas ($10^4$
+K $<$ T $< 10^5$ K),  warm gas ($10^5$ K $<$ T $< 10^7$ K) and hot gas
+(T $> 10^7$ K).  The observations and the simulations match well in
+every phase except the cool CGM gas, where the observations from
+\citet{Werk14} find $3\times$ the mass that NIHAO simulations predict.
+
+If the observations are correct, the simulations have either ejected
+cool gas too far, or  they have created a CGM with the wrong mix of
+gas temperatures. The total gas fractions (0.39 in COS-HALOs, 0.41 in
+NIHAO) suggest the latter option.   However, \citet{Stern16} developed
+a new method to constrain the physical conditions in the cool CGM from
+measurements of ionic  columns densities. This new method combines the
+information available from different sight-lines during the
+photoionization modeling, and was applied to the COS-HALOs data
+yielding a total cool CGM mass within the virial radius of
+$1.3\times10^{10}\Msun$.  The corresponding cool gas fraction is
+shown by the green hashed bar in Fig~\ref{fig:budget} and is in good
+agreement with our prediction.
+
+As the Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool
+gas is the most important component {\bf for most haloes in the NIHAO
+  simulations ($10^{10} < M_{200}/\Msun < 10^{12}$). The cold and
+  warm-hot gas only dominate for galaxies at the lower and higher mass
+  ends.  As the CGM of lower mass galaxies will soon be observed,
+  Table~\ref{tab:comparison} lists information about CGM mass
+  fractions of the different components of gas in haloes down to a
+  halo mass of $\sim 10^{10}\Msun$.
+
+  A recent estimation for the baryonic fractions from a set of eight
+  Milky Way-sized zoom-in cosmological simulations \citep{Colin16} is
+  generally consistence with our results. The fraction of cool gas
+  from their simulations is even lower  ($f_{\rm cool}$ = 0.034) than
+  ours and the result from  \citet{Stern16}. On the other hand,
+  \citet{Peeples14} gave  a conservative observational estimate about
+  warm-hot gas and showed that the fraction of gas in this phase is
+  only 5\%,  which is the lower limit of the estimates from
+  \citet{Werk14}  and less than the average values from
+  \citet{Colin16}  ($f_{\rm warm-hot} \approx 24\%$) and our finding
+  ($f_{\rm warm-hot} \approx 17\%$). Therefore, the mix of
+  temperatures of the CGM has large uncertainties.} More accurate
+knowledge of the physical properties of the CGM are necessary to
+better constrain feedback models and to understand the role of the CGM
+in galaxy formation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% SECTION 4: SUMMARY
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}
+\label{sec:sum}
+
+We have used the NIHAO galaxy simulation suite \citep{Wang15} to study
+the statistical features of the baryonic budget and distribution
+spanning halo masses of $\sim 10^{10}$ to $\sim 10^{12}\Msun$. NIHAO
+is a large (currently 88) set of high resolution cosmological zoom-in
+hydrodynamical galaxy formation simulations. As shown in previous
+papers the NIHAO galaxies reproduce several key observed scaling
+relations, {\bf and thus they make plausible predictions for the
+  baryon budget in and around galaxies.}  We summarize our results as
+follows:
+
+\begin{itemize}
+\item All of the NIHAO haloes have a lower baryon to dark matter
+  ratio,  inside the virial radius, than the cosmic baryon fraction
+  (Fig.~\ref{fig:budget}).
+
+\item Lower mass haloes have lost a larger fraction of their baryons,
+  even though they convert a much lower fraction of the baryons into
+  stars (Fig.~\ref{fig:budget}).  {\bf Similar trends are found by
+    other recent simulations \citep{Christensen16,Voort16} using
+    different codes (Fig.~\ref{fig:fire_com})}.
+
+\item {\bf The missing baryons have been expelled well beyond the
+  virial radius, $R_{200}$, (Fig.~\ref{fig:rps}). Relative to the
+  virial radius, the baryons in the amount of fiducial baryonic mass 
+  within the virial radiusare expelled to smaller radii in more
+  massive haloes: $\Rbar \sim 5 R_{200}$ for $M_{200}=10^{10}\Msun$ and
+  $\Rbar \sim 2 R_{200}$ for $M_{200}=10^{12}\Msun$
+  (Fig.~\ref{fig:missvr}).}
+
+\item Cold gas ($T<10^4$K) is mostly restricted to be within 0.2
+  virial radii (Fig.~\ref{fig:corona}). Cool gas ($10^4 < T < 10^5$K)
+  dominates the baryonic mass outside the virial radius at low masses
+  ($M_{200}\lta 3\times 10^{11} \Msun$) while the warm-hot gas ($10^5
+  < T < 10^7$K) dominates at high masses ($M_{200}\gta 3\times 10^{11}
+  \Msun$) (Figs.~\ref{fig:corona} \& \ref{fig:inout}).
+
+\item For the highest mass haloes in our study $\sim 10^{12}\Msun$ our
+  simulations are consistent with the observed  fractions
+  \citep[e.g.][]{Werk14} of stars, cold gas, warm and hot gas inside
+  the virial radius (Fig.~\ref{fig:comparison}).
+
+\item For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
+      which is significantly lower than the observations from COS-HALOs
+      ($f_{\rm cool}=0.28-0.48$), but is in excellent agreement with the
+      analysis of \citet{Stern16}.
+
+\end{itemize}
+
+{\bf We hope our results will motivate observers to obtain more
+  accurate measurements of the mass fractions in different phases of
+  the CGM over a wide range of galaxy masses, and simulators to make
+  the corresponding predictions.}
 
@@
 
-In this plot \citet{Werk14} provides observational constraints for
-CGM gas mass that are shown as the shaded bars.  The stellar  mass
-range comes from halo abundance matching as described in
-\citet{Kravtsov14}.   The cold disk gas mass comes from from
-\citet{Dutton11}.
-
-The observations and the simulations match well in every phase except
- the cool CGM gas, where the observations find $3\times$ the
-mass that simulations predict.  If the observations are correct, the
-simulations have either ejected cool gas too far, or  they have
-created a CGM with the wrong mix of gas temperatures. The total gas
-fractions (0.39 in COS-HALOs, 0.41 in NIHAO) suggest the latter
-option.   However, \citet{Stern16} developed a new method to
-constrain the physical conditions in the cool CGM from measurements
-of ionic  columns densities. This new method combines the
-information available from different sightlines during the photoionization
-modeling, and was applied to the COS-HALOs data,  yielding a total
-cool CGM mass within the virial radius of $1.3\times10^{10}\Msun$
-which is shown by the green hashed bar in Fig~\ref{fig:budget} and
-is in good agreement with our prediction.  As the
-Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool gas is
-the most important component {\bf for most galaxies in NIHAO simulation
-($10^{10} < M/\Msun < 10^{12}$), the cold and hot gas only dominate for
-galaxies at lower and higher mass end in NIHAO suite.} 
-{\bf A new estimation for the baryonic fractions from a set of
-eight Milky Way-sized zoom-in cosmological simulations 
-\citep{Colin16} is genenrally consistence with our results. The 
-fraction of cool gas from their simulation is even lower 
-($f_{\rm cool}$ = 0.034) than ours and the result from 
-\citet{Stern16}. On the other hand, \citet{Peeples14} gave 
-a conservative observational estimate about warm-hot gas and
-showed that the fraction of gas in this phase is only 5\%, 
-which is the lower limit of the estimates from \citet{Werk14} 
-and less than the average values from \citet{Colin16} 
-($f_{\rm warm-hot} \approx 24\%$) and our finding 
-($f_{\rm warm-hot} \approx 17\%$). Therefore, the mix temperature
-of CGM have large uncertainty and}
-the more accurate
-knowledge of the physical properties of CGM are necessary to better
-understand the role of the CGM in galaxy formation.
-%
-As the CGM of lower mass galaxies will soon be observed,
-Table~\ref{tab:comparison} lists information about CGM
-mass fractions of the different components of gas in haloes down to a
-halo mass of $\sim 10^{10}\Msun$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% SECTION 4: SUMMARY
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary}
-\label{sec:sum}
-
-We have used the NIHAO galaxy simulation suite \citep{Wang15} to study
-the statistical features of the baryonic budget and distribution
-spanning halo masses of $\sim 10^{10}$ to $\sim 10^{12}\Msun$. NIHAO
-is a large (currently 88) set of high resolution cosmological
-hydrodynamical galaxy formation simulations. As shown in previous papers
-the NIHAO galaxies reproduce several key observed scaling relations.
-We summarize our results as follows:
-
-\begin{itemize}
-\item All of the NIHAO haloes have a lower baryon to dark matter ratio, 
-      inside the virial radius, than the cosmic baryon fraction. 
-      {\bf Higher fractions of baryons are lost as the virial mass 
-      decreases in the mass range of $\lesssim 10^{12} \Msun$.
-      The trend confirmed with \citet{Christensen16} and \citet{Voort16},
-      and associated by \citet{Voort16}, the trend at higher mass range
-      may suggest the baryon fraction is reduced larger as virial mass
-      increase. }
-
-\item Lower mass haloes have lost a larger fraction of their baryons, 
-      even though they convert a lower fraction of the baryons into stars.
-
-\item Cold gas ($T<10^4$K) is mostly restricted to be within
-      0.2 virial radii.  The cool gas ($10^4 < T < 10^5$K) dominates
-      the corona at low masses ($M_{200}\lta 3\times 10^{11} \Msun$)
-      while the warm-hot gas ($10^5 < T < 10^7$K) dominates at high
-      masses ($M_{200}\gta 3\times 10^{11} \Msun$).
-
-\item {\bf All haloes have less baryons than baryon mass derived by cosmic
-       baryonic fraction even beyond 2 virial radii. The total 
-       baryons derived by cosmic baryonic fraction within virial radius 
-       can expand more than $8\Rvir$ for low mass haloes but less than
-       $2\Rvir$ for high mass haloes.}
-
-\item Cool gas is a major component of the total baryons within
-      R$_{\rm bar}$ {\bf for galaxies at mass range between $10^{10} \Msun$ 
-      to $10^{12} \Msun$ cold and warm-hot gas dominates only for galaxies 
-      at lower and higher mass end. Most of baryons are} outside of the 
-      virial radius.
-
-\item For the highest mass haloes in our study $\sim 10^{12}\Msun$ our
-      simulations are consistent with the observed  fractions of stars,
-      cold gas, warm and hot gas \citep{Werk14}. {\bf \citet{Peeples14} 
-      showed a conservative observational estimate for warm-hot gas 
-      which is lower limit of the result from \citet{Werk14} and the 
-      warm-hot fraction from our study is well within the range of less
-      conservative estimates.}
-
-\item For the cool gas we predict $f_{\rm cool}=0.11\pm0.06$
-      which is significantly lower than the observations from COS-HALOs
-      ($f_{\rm cool}=0.28-0.48$), but is in excellent agreement with the
-      analysis of \citet{Stern16}.
-      {\bf As in \citet{Colin16}, the simulations suggest that the
-      fraction of cool gas is approximately 10\%.}
-
-\end{itemize}
-
 \section*{Acknowledgments}
 
-We thank the two anonymous referees whose suggestions greatly 
-improve the paper.
-{\bf We thank Freeke van de Voort for kindly sharing data of the FIRE
-simulation.}
-{\sc Gasoline} was written by Tom Quinn and James Wadsley. Without
-their contribution, this paper would have been impossible.
+We thank the two anonymous referees whose suggestions greatly  improve
+the paper.  {\bf We thank Freeke van de Voort for kindly sharing data
+  of the FIRE simulation.}  {\sc Gasoline} was written by Tom Quinn
+and James Wadsley. Without their contribution, this paper would have
+been impossible.
 %
@@
 %
-\bibitem[Ford et al.(2015)]{Ford15} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2016, \mnras, 459, 1745
+\bibitem[Ford et al.(2016)]{Ford16} Ford, A.~B., Werk, J.~W., Dav{\`e}, R., et al.\ 2016, \mnras, 459, 1745
 

### 2016-09-30 ms_nihao_budget.tex
rephase the conclusion to explain the definition of R_bar

@@
   ratio,  inside the virial radius, than the cosmic baryon fraction
-  (Fig.~\ref{fig:budget}).
-
-\item Lower mass haloes have lost a larger fraction of their baryons,
+  (Fig.~\ref{fig:budget}). {\bf We refer to the cosmic baryon fraction associated 
+  with each dark matter halo as the fiducial baryons.}
+
+\item Lower mass haloes are missing a larger fraction of their {\bf fiducial} baryons,
   even though they convert a much lower fraction of the baryons into
@@
   virial radius, $R_{200}$, (Fig.~\ref{fig:rps}). Relative to the
-  virial radius, the baryons in the amount of fiducial baryonic mass 
-  within the virial radiusare expelled to smaller radii in more
+  virial radius, the baryons are expelled to smaller radii in more
   massive haloes: $\Rbar \sim 5 R_{200}$ for $M_{200}=10^{10}\Msun$ and

### 2016-10-04 ms_nihao_budget.tex
mention the ionization model in comparasion with observation
fix one typo

@@
     the corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$)
-    while the  warm-hot gas dominates dominates at high mass (M$_{200}
+    while the  warm-hot gas dominates at high mass (M$_{200}
     \gta 3 \times 10^{11} \Msun$)}.  Haloes of mass $\Mhalo\sim
@@
 agreement with our prediction.
+{\bf We should note that \citet{Stern16} does not follow a same 
+assumption on CGM ionization that assume all \ovi{} is produced
+through photoionization and no collisional ionization, however, 
+\citet{Gutcke16} finds the CGM in $L^*$ galaxies in NIHAO is mostly 
+ionized by collsional ionization.}
 

### 2016-11-07 ms_nihao_budget.tex
modified as the referee's comments except three of them

--- 2016-09-21 ms_nihao_budget.tex
@@
   find that all of our haloes are missing baryons. The missing mass
-  has been relocated past 2 virial radii, and {\bf cool gas dominates
+  has been relocated past 2 virial radii, and cool gas dominates
     the corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$)
-    while the  warm-hot gas dominates dominates at high mass (M$_{200}
-    \gta 3 \times 10^{11} \Msun$)}.  Haloes of mass $\Mhalo\sim
+    while the  warm-hot gas dominates at high mass (M$_{200}
+    \gta 3 \times 10^{11} \Msun$).  Haloes of mass $\Mhalo\sim
   10^{10}\Msun$ are missing $\sim 90\%$ of their baryons.  More
@@
   of their baryons, with $\sim 30\%$ missing, consistent with recent
-  observational estimates.  {\bf Moreover, these more massive haloes
+  observational estimates.  Moreover, these more massive haloes
     reproduce the observed  fraction of cold, warm-hot and hot gas.
@@
     than the observation from COS-HALOs (0.3-0.47), but agrees with
-    the alternative analysis of \citet{Stern16}}.
+    the alternative analysis of \citet{Stern16}.
 \end{abstract}
@@
 However, the cold baryonic mass density implied by several galaxy
-baryon estimates {\bf (mainly stars and cold gas)} is only 3-8\% of
+baryon estimates (mainly stars and cold gas) is only 3-8\% of
 the big bang nucleosynthesis expectation \citep{Persic92, Fukugita98,
@@
 studies with cosmological simulations have constrained the phase of
-the potential reservoirs of the missing baryons {\bf in the
+the potential reservoirs of the missing baryons in the
   intergalactic medium (IGM), and find a large fraction of the baryons
-  with low density and high temperature resides between galaxies}
+  with low density and high temperature resides between galaxies
 \citep{Yoshida05, He05, Dave10, Zhu11, Haider16}.
 
-The circum galactic medium (CGM) is {\bf another}  major potential
+{\bf As a part of the IGM, the circum galactic medium (CGM) is always 
+treated as }an major potential
 reservoir of the missing baryons. \hi{} and metal absorption lines are
@@
 studied the covering fraction of dense \hi{}, looked at the shape of
-the CGM and its chemical composition. {\bf The simulations
+the CGM and its chemical composition. The simulations
   reproduce  the observational covering fraction and column density
@@
   is lower and the extent of optically thick \hi{} is smaller than
-  observed.}
+  observed.
 
@@
 return to low-mass galaxies than high-mass galaxies.
-{\bf \citet{Muratov15} showed similar results that the gas and
+\citet{Muratov15} showed similar results that the gas and
 baryon fractions are lower at lower redshift, after powerful
 outflows at intermediate redshift $z \approx 0.5-2$ remove a large
-amount of gas from the halo. \citet{Voort16} found the baryon fraction
+amount of gas from the halo. {\bf Several simulations 
+\citep{Crain10, Christensen16,Voort16}} found the baryon fraction
 and gas fraction are reduced compared to the cosmic baryon
-fraction, especially in low mass haloes.}
+fraction, especially in low mass haloes.
 %  
@@
 respectively.  We adopted the  latest compilation of cosmological
-parameters from the Planck  satellite \citep{Planck14}.  More
-information on the collisionless parent simulations, {\bf the force
+parameters from the Planck  satellite \citep{Planck14}.  
+{\bf Dark matter particle masses range from $\sim 10^3 \Msun$ in 
+our lowest mass haloes to $\sim 10^5 \Msun$ in our most massive 
+haloes, and their force softenings range from $\sim$ 100 pc in 
+low mass range to $\sim$ 900 pc in high mass range.
+Gas particles are less massive in factor of 5 correspondingly, and
+the force softenings are 3 times less than dark matters.}
+More information on the collisionless parent simulations, the force
   softenings and particle masses for the highest refinement level for
-  each simulation} and sample  selection can be found in
+  each simulation and sample  selection can be found in
 \citet{Dutton14} and \citet{Wang15}.
@@
 The star formation and feedback modeling follows what was used in the
-MaGICC simulations \citep{Stinson13}.   {\bf The gas is converted into
+MaGICC simulations \citep{Stinson13}.   The gas is converted into
   stars according to the Kennicutt-Schmidt Law when it satisfies a
@@
   support and  increase gas temperature above the star formation
-  threshold, and thus to decrease star formation.}  There are two
+  threshold, and thus to decrease star formation.  There are two
 small changes in NIHAO simulations compared to MaGICC:
@@
 }
-\caption{{\bf Comparison between baryon (upper panels) and stellar
+\caption{Comparison between baryon (upper panels) and stellar
     fractions (lower panels) in the NIHAO simulations (blue circles)
     with simulations from \citet{Voort16} (left, red pentagons) and
-    \citet{Christensen16} (right, purple pentagons).}}
+    \citet{Christensen16} (right, purple pentagons).}
 \label{fig:fire_com}
@@
 the most massive galaxy in each zoom-in region. We present the
-fractions of total stellar mass (blue points), and the total baryonic
+fractions of total stellar mass {\bf within 20\% $\Rvir$} (blue points), 
+and the total baryonic
 mass including stellar mass plus gas mass (green points).  For the
@@
 the form of gas, while in the highest mass haloes we study
-($\Mhalo\sim 10^{12}\Msun$) {\bf a substantial amount of gas
-has been turned into stars}.
+($\Mhalo\sim 10^{12}\Msun$) a substantial amount of gas
+has been turned into stars.
 
@@
 and hence there is proportionally less energy available to drive an
-outflow, they have expelled a larger fraction of their baryons. {\bf
+outflow, they have expelled a larger fraction of their baryons. 
   This is consistent with expectations from energy driven gas
@@
   compensated by the shallower potential wells of lower lower mass
-  halos according the mass loading factor and circular velocity 
-  relaion $\eta \propto V^{-2}$
-   \citep[e.g.,][]{Dutton12, Christensen16}.}
+  halos according {\bf to} the mass loading factor and circular velocity 
+  {\bf relation }$\eta \propto V^{-2}$
+   \citep[e.g.,][]{Dutton12, Christensen16}.
 
@@
 
-{\bf The three most massive galaxies in the NIHAO suite have fairly high
+  The three most massive galaxies in the NIHAO suite have fairly high
   stellar masses compared to abundance matching results (see blue
@@
   fraction fitting formula since the high mass slope ($M_{200} >
-  10^{11}\Msun$) is constrained by $\sim 40$ other haloes.}
+  10^{11}\Msun$) is constrained by $\sim 40$ other haloes.
 
 The green shaded region indicates the scatter about the best fit line,
-which is 0.151 {\bf dex} for haloes with mass in the range of  
+which is 0.151 dex for haloes with mass in the range of  
 $3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
@@
 background, which heats gas to above the virial temperature, thus
-preventing it from collapsing into the low mass haloes. {\bf The
-  baryon fractions are thus controlled primarily by the halo masses,
-  and thus are independent of the large scatter in the star formation
-  efficiency.}
+preventing it from collapsing into the low mass haloes. The
+  baryon fractions {\bf in low mass haloes} are thus controlled primarily 
+  by the halo masses,
+  and thus are independent of the large scatter in the 
+  {\bf stellar mass}.
 
@@
 \subsubsection{Comparison with other zoom-in simulations}
-{\bf In Fig.~\ref{fig:fire_com} we compare the NIHAO results for the
+  In Fig.~\ref{fig:fire_com} we compare the NIHAO results for the
   stellar and baryonic mass fractions with other recent
@@
 suggests that the potential well of the halo regulates the baryon
-fraction more than the strength of the feedback.  }
+fraction more than the strength of the feedback.
 
@@
 where the stars are rare, for a given halo the four phases add up to
-unity, {\bf each line is colour coded by the virial mass}.  
+unity, each line is colour coded by the virial mass.  
 All simulations share a common attribute.  The cold gas (T$<10^4$K)
@@
 whole corona region.  For higher mass galaxies, warm-hot gas dominates
-the corona  which signals {\bf stronger virial shocks} and higher
+the corona  which signals stronger virial shocks and higher
 efficiency  of feedback.  Even beyond the virial radius, the cool and
@@
 
-Fig.~\ref{fig:rps} shows the {\bf cumulative fraction} of total baryons  for
+Fig.~\ref{fig:rps} shows the cumulative fraction of total baryons  for
 each simulation. Here the y-axis is the ratio between the baryonic to
@@
 small radii, the baryon to dark matter ratio is higher than the cosmic
-value due to gas dissipation. {\bf Beyond 0.5 virial radii, all haloes
-  are missing baryons.}  Even beyond the virial radius, there is
+value due to gas dissipation. Beyond 0.5 virial radii, all haloes
+  are missing baryons.  Even beyond the virial radius, there is
 little change in the baryon fraction up to 2 virial radii.  We thus
@@
 
-{\bf \citet{Ford16} compare results for the cumulative baryon profile
+ \citet{Ford16} compare results for the cumulative baryon profile
   from two cosmological hydrodynamic simulations which employed
@@
 distinguishing between competing outflow models.
-}
 
@@
 the true extent of the missing baryons since the baryon mass includes
-gas and stars that belong to nearby lower mass haloes.
+gas and stars that belong to nearby lower mass haloes,
+{\bf and is a radius within the effective volume of the simulations
+since contamination fraction in a shell between 0.9 and 
+1.0 $\Rbar$ shows most NIHAO galaxies have a fraction close to 0,
+with largest only around 10 - 20. }
 Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
 function of the virial mass. In physical units, we find that the
-baryon radius generally increases with virial mass. {\bf When
+baryon radius generally increases with virial mass. When
   normalized by the virial radius, the distance baryons are ejected
@@
   $\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$
-  to $\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.}
+  to $\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.
 
@@
 }
-\caption{{\bf Mass fraction of gas in three phases (relative to the
+\caption{ Mass fraction of gas in three phases (relative to the
     fiducial baryonic mass within the virial radius) inside the
@@
     the majority only for galaxies at the low and high mass
-    ends, respectively.}}
+    ends, respectively.}
 \label{fig:inout}
@@
 phases) inside the virial radius (filled blue points) and between the
-virial and baryon radius (open red points).
+virial and baryon radius (open red points)
+{\bf which are relative to the fiducial baryonic mass within the 
+virial radius}.
 %
 The fractions of cold gas,
-$f_{\rm cold}$, are shown in the {\bf left} panel.  Inside the
+$f_{\rm cold}$, are shown in the left panel.  Inside the
 virial radius $f_{\rm cold}$ increases gradually from zero at a halo
@@
 The fractions of cool gas, $f_{\rm cool}$, are
-shown in the {\bf middle} panel.  Inside the virial radius, $f_{\rm
+shown in the middle panel.  Inside the virial radius, $f_{\rm
   cool}$, has a maximum of 40\% at a halo mass of $10^{11} \Msun$,
@@
 The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
-{\bf right} panel.  The trends of the gas inside and outside the virial
+right panel.  The trends of the gas inside and outside the virial
 radius are quite similar, $f_{\rm warm}$ increases monotonically with
@@
 %
-The hot gas {\bf isn't shown} since it is negligible both
+The hot gas isn't shown since it is negligible both
 inside and outside the virial radius across the whole mass range we
@@
 
-{\bf Observations can gain information of CGM from absorption
+Observations can gain information of CGM from absorption
 and emission lines. Although emission lines allow us to directly obtain
@@
 with new facilities, e.g.~\citet{Hayes16}, absorption lines are  the
-most common observational constraints on the physical state of the CGM.}
+most common observational constraints on the physical state of the CGM.
 
@@
 from \citet{Dutton11}.
+{\bf The mean value of missing fraction is the residual fraction
+of the sum of mean values of all components fractions in unity
+and the lower and upper limits are calculated in the same manner
+by the upper and lower limits of the all fractions.}
 
@@
 agreement with our prediction.
+We should note that \citet{Stern16} does not follow a same 
+assumption on CGM ionization that assume all \ovi{} is produced
+through photoionization and no collisional ionization, however, 
+\citet{Gutcke16} finds the CGM in $L^*$ galaxies in NIHAO is mostly 
+ionized by collsional ionization.
 
 As the Fig.~\ref{fig:corona} and Fig.~\ref{fig:inout} show, the cool
-gas is the most important component {\bf for most haloes in the NIHAO
+gas is the most important component for most haloes in the NIHAO
   simulations ($10^{10} < M_{200}/\Msun < 10^{12}$). The cold and
@@
   Milky Way-sized zoom-in cosmological simulations \citep{Colin16} is
-  generally consistence with our results. The fraction of cool gas
+  generally {\bf consistent} with our results. The fraction of cool gas
   from their simulations is even lower  ($f_{\rm cool}$ = 0.034) than
@@
   ($f_{\rm warm-hot} \approx 17\%$). Therefore, the mix of
-  temperatures of the CGM has large uncertainties.} More accurate
+  temperatures of the CGM has large uncertainties. More accurate
 knowledge of the physical properties of the CGM are necessary to
@@
 papers the NIHAO galaxies reproduce several key observed scaling
-relations, {\bf and thus they make plausible predictions for the
-  baryon budget in and around galaxies.}  We summarize our results as
+relations, and thus they make plausible predictions for the
+  baryon budget in and around galaxies.  We summarize our results as
 follows:
@@
   ratio,  inside the virial radius, than the cosmic baryon fraction
-  (Fig.~\ref{fig:budget}).
-
-\item Lower mass haloes have lost a larger fraction of their baryons,
+  (Fig.~\ref{fig:budget}). We refer to the cosmic baryon fraction associated 
+  with each dark matter halo as the fiducial baryons.
+
+\item Lower mass haloes are missing a larger fraction of their fiducial baryons,
   even though they convert a much lower fraction of the baryons into
-  stars (Fig.~\ref{fig:budget}).  {\bf Similar trends are found by
+  stars (Fig.~\ref{fig:budget}).  Similar trends are found by
     other recent simulations \citep{Christensen16,Voort16} using
-    different codes (Fig.~\ref{fig:fire_com})}.
-
-\item {\bf The missing baryons have been expelled well beyond the
+    different codes (Fig.~\ref{fig:fire_com}).
+
+\item The missing baryons have been expelled well beyond the
   virial radius, $R_{200}$, (Fig.~\ref{fig:rps}). Relative to the
-  virial radius, the baryons in the amount of fiducial baryonic mass 
-  within the virial radiusare expelled to smaller radii in more
+  virial radius, the baryons are expelled to smaller radii in more
   massive haloes: $\Rbar \sim 5 R_{200}$ for $M_{200}=10^{10}\Msun$ and
   $\Rbar \sim 2 R_{200}$ for $M_{200}=10^{12}\Msun$
-  (Fig.~\ref{fig:missvr}).}
+  (Fig.~\ref{fig:missvr}).
 
@@
   virial radii (Fig.~\ref{fig:corona}). Cool gas ($10^4 < T < 10^5$K)
-  dominates the baryonic mass outside the virial radius at low masses
+  dominates the baryonic mass outside the virial radius, {\bf as well
+  as outside the 20\% $\Rvir$}, at low masses
   ($M_{200}\lta 3\times 10^{11} \Msun$) while the warm-hot gas ($10^5
@@
 
-{\bf We hope our results will motivate observers to obtain more
+ We hope our results will motivate observers to obtain more
   accurate measurements of the mass fractions in different phases of
   the CGM over a wide range of galaxy masses, and simulators to make
-  the corresponding predictions.}
+  the corresponding predictions.
 
@@
 We thank the two anonymous referees whose suggestions greatly  improve
-the paper.  {\bf We thank Freeke van de Voort for kindly sharing data
-  of the FIRE simulation.}  {\sc Gasoline} was written by Tom Quinn
+the paper.  We thank Freeke van de Voort for kindly sharing data
+  of the FIRE simulation.  {\sc Gasoline} was written by Tom Quinn
 and James Wadsley. Without their contribution, this paper would have
@@
 
+%X-ray coronae in simulations of disc galaxy formation
+\bibitem[Crain et al.(2010)]{Crain10}
+Crain, R.~A., McCarthy, I.~G., Frenk, C.~S., et al.\ 2010, \mnras, 470, 1403
+
 %% DDDDDDDD

### 2016-11-18 ms_nihao_budget.tex
first version according to the third referee report

@@
   fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
-  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas (T$> 10^7$K)
+  10^5$K), warm-hot gas ($10^5 < T < 5\times10^6$K), and hot gas (T$> 5\times10^6$K)
   , inside the virial radius, $R_{200}$.  Compared to the predicted
@@
 the scale of Milky Way mass haloes $\Mhalo \sim 10^{12}\Msun$ a
-significant amount of warm ($10^4 < T < 10^7$K) gas has been detected
+significant amount of warm ($10^4 < T <5\times 10^6$K) gas has been detected
 \citep{Werk14}, accounting for 33-88\% of the baryon budget. In the
@@
 \centerline{
+  \psfig{figure=budget_res.eps,width=0.85\textwidth}
+}
+\caption{{\bf Linear fractional baryon content of NIHAO
+simulations as a function of halo mass color coded by
+number of dark matter particles per halo.}}
+\label{fig:budget_res}
+\end{figure*}
+
+%% FIGURE 2
+\begin{figure*}
+\centerline{
   \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
@@
 
+Fig.~\ref{fig:budget_res} shows the budget fraction of cold, 
+cool and warm-hot gas fraction. Since one can imagine that 
+with increased resolution, higher densities can be achieved in the
+CGM, potential leading to more cooling and larger
+cold/cool gas fraction, all the points are color coded by 
+the total number of dark matter particles within the haloes.
+In the plot, the number of dark matter
+partilce per halo spans 2 magnitudes and has no correlation 
+with cold and cool gas fraction.
+Therefore, the baryonic fractions predicted by NIHAO simulations
+are convergent.
+
 %% FIGURE 3
@@
 greater fraction of missing baryons in lower mass haloes. This
-suggests that the potential well of the halo regulates the baryon
-fraction more than the strength of the feedback.
+suggests that the potential well of the halo {\bf correlates the baryon
+fraction more closely} than the strength of the feedback.
 
@@
 where most stars in galaxies form.  In contrast, the cool ($10^4$K$<$T$<10^5$K)
-and  warm-hot ($10^5$K$<$T$<10^7$K) gas are
+and  warm-hot ($10^5$K$<$T$<5\times10^6$K) gas are
 located at large distances with roughly constant fractions up to 2
-times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
+times $R_{200}$.  The hot gas (T$>5\times10^6$K) is a minority component
 for all galaxies in the NIHAO sample, with the maximum hot gas
@@
 \citet{Peeples14} constrain the mass of  the warm-hot CGM ($T \sim
-10^{5-7}$K), \citet{Werk14} provides a strict lower limit to the mass
+10^{5-6.7}$K), \citet{Werk14} provides a strict lower limit to the mass
 of cool material ($T \sim 10^{4-5}$K) in the CGM of these galaxies.
 In a study using X-rays, \citet{Anderson13} place a constraints on the
-mass of  hot gas ($T > 10^7$K) residing in the extended hot halos.
+mass of  hot gas ($T > 5\times10^6$K) residing in the extended hot halos.
 These observational constraints are shown in Fig.~\ref{fig:comparison}
@@
 from \citet{Dutton11}.
+{\bf In addition, since \citet{Crain10} and \citet{Voort13} show that 
+soft X-ray emission traces gas with temperatures a few times the 
+virial temperature (T$_{\rm vir} = 10^6$ K for M$_{200} \sim 
+10^{12} \Msun$), we also estimate the hot gas fraction with lower
+boundaries ($3\times 10^6$ K and $10^6$ K) between the hot gas and 
+warm-hot gas, the fractions can increase to 0.00511 ($3\times 10^6$K) 
+and 0.04168 ($10^6$ K).}
 {\bf The mean value of missing fraction is the residual fraction
@@
 range of temperature bins:  cold gas (T $< 10^4$ K), cool gas ($10^4$
-K $<$ T $< 10^5$ K),  warm gas ($10^5$ K $<$ T $< 10^7$ K) and hot gas
-(T $> 10^7$ K).  The observations and the simulations match well in
+K $<$ T $< 10^5$ K),  warm gas ($10^5$ K $<$ T $<5\times 10^6$ K) and hot gas
+(T $>5\times 10^6$ K).  The observations and the simulations match well in
 every phase except the cool CGM gas, where the observations from
@@
   ($M_{200}\lta 3\times 10^{11} \Msun$) while the warm-hot gas ($10^5
-  < T < 10^7$K) dominates at high masses ($M_{200}\gta 3\times 10^{11}
+  < T <5\times 10^6$K) dominates at high masses ($M_{200}\gta 3\times 10^{11}
   \Msun$) (Figs.~\ref{fig:corona} \& \ref{fig:inout}).
@@
   $<$ $10^4$ K as cold; $10^4$ K $\leqslant$ T $<$ $10^5$ K as cool;
-  $10^5$ K $\leqslant$ T $<$ $10^7$ K as warm;  and T $\geqslant$
-  $10^7$ K as hot.}
+  $10^5$ K $\leqslant$ T $<$ $5\times10^6$ K as warm;  and T $\geqslant$
+  $5\times10^6$ K as hot.}
 \begin{center}
@@
 
+% Soft X-ray and ultraviolet metal-line emission from the gas around galaxies
+\bibitem[van de Voort \& Schaye (2013)]{Voort13} van de Voort, F., Schaye, J.\ 2013, \mnras, 430, 2688
+
 %The impact of stellar feedback on hot gas in galaxy haloes:

### 2016-11-30 ms_nihao_budget.tex
final version for third submission

@@
 
-\author[Wang et al.]{Liang Wang$^{1,3}$\thanks{wangliang@pmo.ac.cn}, Aaron A. Dutton$^{2,3}$,
+\author[Wang et al.]{Liang Wang$^{1,3,4}$\thanks{wangliang@pmo.ac.cn}, Aaron A. Dutton$^{2,3}$,
   Gregory S. Stinson$^3$, Andrea V. Macci\`o$^{2,3}$, 
@@
 $^2$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\
-$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany}
+$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany\\
+$^4$International Centre for Radio Astronomy Research (ICRAR)
+, M468, University of Western Australia, 35 Stirling Hwy, Cr
+awley, WA 6009, Australia}
 \begin{document}
@@
   fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
-  10^5$K), warm-hot gas ($10^5 < T < 5\times10^6$K), and hot gas (T$> 5\times10^6$K)
-  , inside the virial radius, $R_{200}$.  Compared to the predicted
-  baryon mass, using the dark halo mass and the universal baryon
-  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
-  find that all of our haloes are missing baryons. The missing mass
-  has been relocated past 2 virial radii, and cool gas dominates
-    the corona at low mass (M$_{200} \lta 3 \times 10^{11} \Msun$)
-    while the  warm-hot gas dominates at high mass (M$_{200}
-    \gta 3 \times 10^{11} \Msun$).  Haloes of mass $\Mhalo\sim
-  10^{10}\Msun$ are missing $\sim 90\%$ of their baryons.  More
-  massive haloes ($\Mhalo\sim 10^{12}\Msun$) retain a higher fraction
-  of their baryons, with $\sim 30\%$ missing, consistent with recent
-  observational estimates.  Moreover, these more massive haloes
-    reproduce the observed  fraction of cold, warm-hot and hot gas.
-    The fraction of cool gas we predict (0.11) is significantly lower
-    than the observation from COS-HALOs (0.3-0.47), but agrees with
-    the alternative analysis of \citet{Stern16}.
+  10^5$K), warm-hot gas ($10^5 < T < 5\times10^6$K), and hot gas (T$>
+  5\times10^6$K), inside the virial radius, $R_{200}$.  Compared to
+  the predicted baryon mass, using the dark halo mass and the
+  universal baryon fraction, $f_{\rm b}\equiv \Omega_{\rm
+    b}/\Omega_{\rm m}=0.15$, we find that all of our haloes are
+  missing baryons. The missing mass has been relocated past 2 virial
+  radii, and cool gas dominates the corona at low mass (M$_{200} \lta
+  3 \times 10^{11} \Msun$) while the  warm-hot gas dominates at high
+  mass (M$_{200} \gta 3 \times 10^{11} \Msun$).  Haloes of mass
+  $\Mhalo\sim 10^{10}\Msun$ are missing $\sim 90\%$ of their baryons.
+  More massive haloes ($\Mhalo\sim 10^{12}\Msun$) retain a higher
+  fraction of their baryons, with $\sim 30\%$ missing, consistent with
+  recent observational estimates.  Moreover, these more massive haloes
+  reproduce the observed  fraction of cold, warm-hot and hot gas.  The
+  fraction of cool gas we predict ($0.11\pm0.06$) is significantly
+  lower than the observation from COS-HALOs (0.3-0.47), but agrees
+  with the alternative analysis of \citet{Stern16}.
 \end{abstract}
@@
 masses.  A number of large volume cosmological simulations
-\citep{Ford13, Ford15, Suresh15b, Oppenheimer16} and zoom-in
+\citep{Ford13, Ford16, Suresh15, Oppenheimer16} and zoom-in
 cosmological simulations \citep{Stinson12, Hummels13, Shull14} have
 given  predictions for the \hi{} and \ovi{} absorption
-line. \citet{Gutcke16} compared the column density profile of \ovi{}
+lines. \citet{Gutcke16} compared the column density profile of \ovi{}
 and \hi{} in the CGM of galaxies from the NIHAO \citep{Wang15}
@@
 amount of gas from the halo. {\bf Several simulations 
-\citep{Crain10, Christensen16,Voort16}} found the baryon fraction
+\citep[e.g.,][]{Crain10, Christensen16,Voort16}} found the baryon fraction
 and gas fraction are reduced compared to the cosmic baryon
@@
 a sample of 88 zoom-in galaxy formation simulations from the NIHAO
-project.  Reproducing the stellar mass content in dark matter haloes
+project.
+
+Reproducing the stellar mass content in dark matter haloes
 both today and in the past has been a formidable challenge for
@@
 respectively.  We adopted the  latest compilation of cosmological
-parameters from the Planck  satellite \citep{Planck14}.  
-{\bf Dark matter particle masses range from $\sim 10^3 \Msun$ in 
-our lowest mass haloes to $\sim 10^5 \Msun$ in our most massive 
-haloes, and their force softenings range from $\sim$ 100 pc in 
-low mass range to $\sim$ 900 pc in high mass range.
-Gas particles are less massive in factor of 5 correspondingly, and
-the force softenings are 3 times less than dark matters.}
-More information on the collisionless parent simulations, the force
+parameters from the Planck  satellite \citep{Planck14}.   {\bf Dark
+  matter particle masses range from $\sim 10^{4} \Msun$ in  our lowest
+  mass haloes to $\sim 10^{6} \Msun$ in our most massive  haloes, and
+  their force softenings range from $\sim$ 150 pc to $\sim$ 900 pc,
+  respectively Gas particles are less massive by factor of
+  $(\Omega_{\rm dm}/\Omega_{\rm b})\simeq 5.48$, and  the
+  corresponding force softenings are 2.34 times smaller.}  More
+information on the collisionless parent simulations, the force
 softenings and particle masses for the highest refinement level for
-  each simulation and sample  selection can be found in
-\citet{Dutton14} and \citet{Wang15}.
+each simulation and sample  selection can be found in \citet{Dutton14}
+and \citet{Wang15}.
 
@@
 feedback is implemented using the blastwave formalism described in
-  \citet{Stinson06}. Pre-SN feedback is an attempt to consider
-  radiation energy from massive stars. Heating is introduced
-  immediately after massive stars form based on how much star light is
-  radiated.  Our simulations use thermal feedback to provide pressure
-  support and  increase gas temperature above the star formation
-  threshold, and thus to decrease star formation.  There are two
-small changes in NIHAO simulations compared to MaGICC:
-The change in  number of neighbors
-and the new combination of softening length and  particle mass
-increases the threshold for star formation from  9.3 to 10.3
-cm$^{-3}$, the increase of pre-SN feedback efficiency $\epsilon_{\rm
-  ESF}$, from 0.1 to 0.13.  More details on the star formation and
-feedback modeling can be found in \citet{Wang15}.
+\citet{Stinson06}. Pre-SN feedback is an attempt to consider radiation
+energy from massive stars. Heating is introduced immediately after
+massive stars form based on how much star light is radiated.  Our
+simulations use thermal feedback to provide pressure support and
+increase gas temperature above the star formation threshold, and thus
+to decrease star formation.  There are two small changes in NIHAO
+simulations compared to MaGICC: The change in  number of neighbors and
+the new combination of softening length and  particle mass increases
+the threshold for star formation from  9.3 to 10.3 cm$^{-3}$, the
+increase of pre-SN feedback efficiency $\epsilon_{\rm ESF}$, from 0.1
+to 0.13.  More details on the star formation and feedback modeling can
+be found in \citet{Wang15}.
 
@@
 \centerline{
-  \psfig{figure=barbudget_linearlog.eps,width=0.48\textwidth}
+  \psfig{figure=barbudget_linearlog.eps,width=0.46\textwidth}
 }
@@
 
-%% FIGURE 2
-\begin{figure*}
-\centerline{
-  \psfig{figure=budget_res.eps,width=0.85\textwidth}
-}
-\caption{{\bf Linear fractional baryon content of NIHAO
-simulations as a function of halo mass color coded by
-number of dark matter particles per halo.}}
-\label{fig:budget_res}
-\end{figure*}
-
-%% FIGURE 2
-\begin{figure*}
-\centerline{
-  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
-}
-\caption{Comparison between baryon (upper panels) and stellar
-    fractions (lower panels) in the NIHAO simulations (blue circles)
-    with simulations from \citet{Voort16} (left, red pentagons) and
-    \citet{Christensen16} (right, purple pentagons).}
-\label{fig:fire_com}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the $f_{\rm b} = \Omegab/\Omegam \sim 0.15$ is the cosmic baryon
-fraction (the ratio between baryon density and mass density including baryonic mass
-plus dark matter), so that $M_{\rm b}$ would be the baryonic mass inside the
-virial radius if the baryons followed the dark matter closely.
+fraction (the ratio between baryon density and mass density including
+baryonic mass plus dark matter), so that $M_{\rm b}$ would be the
+baryonic mass inside the virial radius if the baryons followed the
+dark matter closely.
 
@@
 the most massive galaxy in each zoom-in region. We present the
-fractions of total stellar mass {\bf within 20\% $\Rvir$} (blue points), 
-and the total baryonic
-mass including stellar mass plus gas mass (green points).  For the
-stellar mass fraction we also show the relations from the halo
-abundance  matching \citep{Moster13, Behroozi13, Kravtsov14}.  The
-grey area is the one sigma scatter around the mean value  from
-\citet{Kravtsov14}.  Fig.~\ref{fig:budget} shows that all haloes in
-our study contain less than the universal fraction of baryons. The
-upper panel uses a linear y-axis scale, which highlights the large
-amount of baryons that are missing, especially in low mass haloes. The
-logarithmic scale in the lower panel highlights the power-law nature
-of the relations.
+fractions of total stellar mass {\bf within 20\% $R_{200}$} (blue
+points),  and the total baryonic mass including stellar mass plus gas
+mass (green points).  For the stellar mass fraction we also show the
+relations from halo abundance  matching \citep{Moster13, Behroozi13,
+  Kravtsov14}.  The grey area is the one sigma scatter around the mean
+value  from \citet{Kravtsov14}.  Fig.~\ref{fig:budget} shows that all
+haloes in our study contain less than the universal fraction of
+baryons. The upper panel uses a linear y-axis scale, which highlights
+the large amount of baryons that are missing, especially in low mass
+haloes. The logarithmic scale in the lower panel highlights the
+power-law nature of the relations.
 
@@
 
+%% FIGURE 2
+\begin{figure*}
+\centerline{
+  \psfig{figure=budget_res.eps,width=0.95\textwidth}
+}
+\caption{{\bf Baryon content of NIHAO simulations as a function of
+    halo mass color coded by number of dark matter particles per
+    halo. This shows the stars and gas content of the simulations is
+    insensitive to order of magnitude changes in particle
+    resolution.}}
+\label{fig:budget_res}
+\end{figure*}
+
 Since most of the haloes we study are above the mass where the cosmic
@@
 and hence there is proportionally less energy available to drive an
-outflow, they have expelled a larger fraction of their baryons. 
-  This is consistent with expectations from energy driven gas
-  outflows, where the lower star formation efficiency is more than
-  compensated by the shallower potential wells of lower lower mass
-  halos according {\bf to} the mass loading factor and circular velocity 
-  {\bf relation }$\eta \propto V^{-2}$
-   \citep[e.g.,][]{Dutton12, Christensen16}.
+outflow, they have expelled a larger fraction of their baryons.  This
+is consistent with expectations from energy driven gas outflows, where
+the lower star formation efficiency is more than compensated by the
+shallower potential wells of lower mass halos according {\bf to} the
+mass loading factor and circular velocity  {\bf relation }$\eta
+\propto V^{-2}$ \citep[e.g.,][]{Dutton12, Christensen16}.
 
@@
 baryon fractions {\bf in low mass haloes} are thus controlled primarily 
-  by the halo masses,
-  and thus are independent of the large scatter in the 
+by the halo masses, and thus are independent of the large scatter in the
 {\bf stellar mass}.
 
-Fig.~\ref{fig:budget_res} shows the budget fraction of cold, 
-cool and warm-hot gas fraction. Since one can imagine that 
-with increased resolution, higher densities can be achieved in the
-CGM, potential leading to more cooling and larger
-cold/cool gas fraction, all the points are color coded by 
-the total number of dark matter particles within the haloes.
-In the plot, the number of dark matter
-partilce per halo spans 2 magnitudes and has no correlation 
-with cold and cool gas fraction.
-Therefore, the baryonic fractions predicted by NIHAO simulations
-are convergent.
+{\bf Fig.~\ref{fig:budget_res} shows the budget fraction of stars, cold, cool
+  and warm-hot gas color coded by the number of dark matter particles
+  inside the virial radius. Since one can imagine that with increased
+  resolution, higher densities can be achieved in the CGM, potential
+  leading to more cooling and larger cold/cool gas fractions.  In our
+  simulations we find no dependence of stars and gas fractions with particle
+  number, indicating these quantities are not sensitive to numerical
+  resolution using the NIHAO sub-grid model.}
 
@@
 \centerline{
-  \psfig{figure=budgetpro.eps,width=1.0\textwidth}
+  \psfig{figure=m500c_frac.eps,width=0.85\textwidth}
 }
-\caption{Radial profile of the mass fraction of the gas in each phase
-         to total baryonic mass in each radial bin 
-         at $z=0$ for all galaxies in NIHAO sample.
-         Each solid line is from one galaxy and colour coded with
-         the halo mass.}
-\label{fig:corona}
+\caption{Comparison between baryon (upper panels) and stellar
+    fractions (lower panels) in the NIHAO simulations (blue circles)
+    with simulations from \citet{Voort16} (left, red pentagons) and
+    \citet{Christensen16} (right, purple pentagons).}
+\label{fig:fire_com}
 \end{figure*}
@@
 
+  %% FIGURE 3
+\begin{figure*}
+\centerline{
+  \psfig{figure=budgetpro.eps,width=1.0\textwidth}
+}
+\caption{Radial profile of the mass fraction of the gas in each phase
+         to total baryonic mass in each radial bin 
+         at $z=0$ for all galaxies in NIHAO sample.
+         Each solid line is from one galaxy and colour coded with
+         the halo mass.}
+\label{fig:corona}
+\end{figure*}
+
 \subsection{Mass budget of the corona}
@@
 the true extent of the missing baryons since the baryon mass includes
-gas and stars that belong to nearby lower mass haloes,
-{\bf and is a radius within the effective volume of the simulations
-since contamination fraction in a shell between 0.9 and 
-1.0 $\Rbar$ shows most NIHAO galaxies have a fraction close to 0,
-with largest only around 10 - 20. }
-Fig.~\ref{fig:missvr} shows the baryon radius of each galaxy as
-function of the virial mass. In physical units, we find that the
-baryon radius generally increases with virial mass. When
-  normalized by the virial radius, the distance baryons are ejected
-  gradually decreases as halo mass increases, varying from
-  $\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$
-  to $\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.
+gas and stars that belong to nearby lower mass haloes.  {\bf It is a
+  radius within the high-resolution volume of the simulations since
+  the contamination fraction in a shell between 0.9 and  1.0 $\Rbar$
+  shows most NIHAO galaxies have a fraction close to 0, with largest
+  only around 10 - 20\%. } Fig.~\ref{fig:missvr} shows the baryon
+radius of each galaxy as function of the virial mass. In physical
+units, we find that the baryon radius generally increases with virial
+mass. When normalized by the virial radius, the distance baryons are
+ejected gradually decreases as halo mass increases, varying from
+$\Rbar/R_{200}\sim 5$ at a halo mass of $M_{200}\sim 10^{10}\Msun$ to
+$\sim 2$ at a halo mass of $M_{200}\sim 10^{12}\Msun$.
 
@@
 phases) inside the virial radius (filled blue points) and between the
-virial and baryon radius (open red points)
-{\bf which are relative to the fiducial baryonic mass within the 
-virial radius}.
-%
-The fractions of cold gas,
-$f_{\rm cold}$, are shown in the left panel.  Inside the
-virial radius $f_{\rm cold}$ increases gradually from zero at a halo
-mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo mass of
-$10^{12}\Msun$.  The gas outside the virial radius has the opposite
-and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of mass
-$10^{10}\Msun$ and decreases to zero by halo masses of
+virial and baryon radius (open red points).  {\bf All fractions are
+  relative to the fiducial baryonic mass within the  virial radius}.
+%
+The fractions of cold gas, $f_{\rm cold}$, are shown in the left
+panel.  Inside the virial radius $f_{\rm cold}$ increases gradually
+from zero at a halo mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo
+mass of $10^{12}\Msun$.  The gas outside the virial radius has the
+opposite and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of
+mass $10^{10}\Msun$ and decreases to zero by halo masses of
 $10^{11}\Msun$.
 %
-The fractions of cool gas, $f_{\rm cool}$, are
-shown in the middle panel.  Inside the virial radius, $f_{\rm
-  cool}$, has a maximum of 40\% at a halo mass of $10^{11} \Msun$,
-and declines to less than 10\% below and above halo masses of
-$10^{10}\Msun$ and $10^{12}\Msun$, respectively.  For most haloes there
-is more cool gas outside than inside the virial radius.  In haloes
-of mass $10^{10}\Msun$, $f_{\rm cool}\sim 80\%$, and decreases to
-less than 10\% by a halo mass of $10^{12}\Msun$.
+The fractions of cool gas, $f_{\rm cool}$, are shown in the middle
+panel.  Inside the virial radius, $f_{\rm cool}$, has a maximum of
+40\% at a halo mass of $10^{11} \Msun$, and declines to less than 10\%
+below and above halo masses of $10^{10}\Msun$ and $10^{12}\Msun$,
+respectively.  For most haloes there is more cool gas outside than
+inside the virial radius.  In haloes of mass $10^{10}\Msun$, $f_{\rm
+  cool}\sim 80\%$, and decreases to less than 10\% by a halo mass of
+$10^{12}\Msun$.
 %
@@
 
-Observations can gain information of CGM from absorption
-and emission lines. Although emission lines allow us to directly obtain
-a 3D picture of the distribution of gas in the CGM, emission line studies
+Observations can gain information of CGM from absorption and emission
+lines. Although emission lines allow us to directly obtain a 3D
+picture of the distribution of gas in the CGM, emission line studies
 preferentially probe the dense gas closer to galaxies, since gas
-emissivity scales with the square of density. While the situation is improving
-with new facilities, e.g.~\citet{Hayes16}, absorption lines are  the
-most common observational constraints on the physical state of the CGM.
+emissivity scales with the square of density. While the situation is
+improving with new facilities, e.g.~\citet{Hayes16}, absorption lines
+are  the most common observational constraints on the physical state
+of the CGM.
 
@@
 \citet{Peeples14} constrain the mass of  the warm-hot CGM ($T \sim
-10^{5-6.7}$K), \citet{Werk14} provides a strict lower limit to the mass
-of cool material ($T \sim 10^{4-5}$K) in the CGM of these galaxies.
-In a study using X-rays, \citet{Anderson13} place a constraints on the
-mass of  hot gas ($T > 5\times10^6$K) residing in the extended hot halos.
-These observational constraints are shown in Fig.~\ref{fig:comparison}
-with the same colour scheme as in Fig.11 of \citet{Werk14}.  The
-stellar mass fractions are based on halo abundance matching as
-described in \citet{Kravtsov14}, while the cold disk gas mass comes
-from \citet{Dutton11}.
-{\bf In addition, since \citet{Crain10} and \citet{Voort13} show that 
-soft X-ray emission traces gas with temperatures a few times the 
-virial temperature (T$_{\rm vir} = 10^6$ K for M$_{200} \sim 
-10^{12} \Msun$), we also estimate the hot gas fraction with lower
-boundaries ($3\times 10^6$ K and $10^6$ K) between the hot gas and 
-warm-hot gas, the fractions can increase to 0.00511 ($3\times 10^6$K) 
-and 0.04168 ($10^6$ K).}
-{\bf The mean value of missing fraction is the residual fraction
-of the sum of mean values of all components fractions in unity
-and the lower and upper limits are calculated in the same manner
-by the upper and lower limits of the all fractions.}
+10^{5-6.7}$K), \citet{Werk14} provides a strict lower limit to the
+mass of cool material ($T \sim 10^{4-5}$K) in the CGM of these
+galaxies.  In a study using X-rays, \citet{Anderson13} place a
+constraints on the mass of  hot gas ($T > 5\times10^6$K) residing in
+the extended hot halos.  These observational constraints are shown in
+Fig.~\ref{fig:comparison} with the same colour scheme as in Fig.11 of
+\citet{Werk14}.  The stellar mass fractions are based on halo
+abundance matching as described in \citet{Kravtsov14}, while the cold
+disk gas mass comes from \citet{Dutton11}.  {\bf The upper limits to
+  the missing fraction are calculated using the lower limits to all
+  the fractions. There are two upper limits shown which correspond to
+  the two measurements of the cool-gas fraction
+  \citep{Werk14,Stern16}. The lower limit to the missing fraction is
+  consistent with zero.}
 
@@
 \caption{Baryonic budget  of NIHAO haloes of mass $3.5\times 10^{11} <
-  M_{200}/\Msun < 3.5 \times 10^{12}$ (blue points  with 1$\sigma$
+  M_{200}/\Msun < 3.5 \times 10^{12}$ (black points  with 1$\sigma$
   error bars) compared with observations of  $M_{200} \sim
@@
   except for the cool gas which has two conflicting measurements:
-  \citet[][upper]{Werk14} upper, \citet[][lower]{Stern16}.  }
+  \citet[][upper]{Werk14} upper, \citet[][lower hatched]{Stern16}.  }
 \label{fig:comparison}
@@
 
-The blue points and error bars show the mean values and standard
+The black points and error bars show the mean values and standard
 deviation of the mass fraction of stars and different components of
@@
 yielding a total cool CGM mass within the virial radius of
-$1.3\times10^{10}\Msun$.  The corresponding cool gas fraction is
-shown by the green hashed bar in Fig~\ref{fig:budget} and is in good
-agreement with our prediction.
-We should note that \citet{Stern16} does not follow a same 
-assumption on CGM ionization that assume all \ovi{} is produced
-through photoionization and no collisional ionization, however, 
-\citet{Gutcke16} finds the CGM in $L^*$ galaxies in NIHAO is mostly 
-ionized by collsional ionization.
+$1.3\times10^{10}\Msun$.  The corresponding cool gas fraction is shown
+by the green hashed bar in Fig~\ref{fig:budget} and is in good
+agreement with our prediction.  We should note that \citet{Stern16}
+does not follow a same  assumption on CGM ionization that assume all
+\ovi{} is produced through photoionization and no collisional
+ionization, however,  \citet{Gutcke16} finds the CGM in $L^*$ galaxies
+in NIHAO is mostly  ionized by collisional ionization.
+
+{\bf Since \citet{Crain10} and \citet{Voort13} show that  soft X-ray
+  emission traces gas with temperatures a few times the  virial
+  temperature (T$_{\rm vir} = 10^6$ K for M$_{200} \sim  10^{12}
+  \Msun$), we also estimate the hot gas fraction with lower boundaries
+  ($3\times 10^6$ K and $10^6$ K) between the hot gas and  warm-hot
+  gas. The hot gas fractions increase to 0.00511 ($3\times 10^6$K)
+  and 0.0417 ($10^6$ K), while the warm-hot gas fractions decrease by
+  a corresponding amount. Even with these different definitions the
+  NIHAO simulations are in good agreement with the observed warm-hot
+  and hot gas fractions. }
 
@@
   dominates the baryonic mass outside the virial radius, {\bf as well
-  as outside the 20\% $\Rvir$}, at low masses
-  ($M_{200}\lta 3\times 10^{11} \Msun$) while the warm-hot gas ($10^5
-  < T <5\times 10^6$K) dominates at high masses ($M_{200}\gta 3\times 10^{11}
-  \Msun$) (Figs.~\ref{fig:corona} \& \ref{fig:inout}).
+    as outside 20\% $R_{200}$}, at low masses ($M_{200}\lta 3\times
+  10^{11} \Msun$) while the warm-hot gas ($10^5 < T <5\times 10^6$K)
+  dominates at high masses ($M_{200}\gta 3\times 10^{11} \Msun$)
+  (Figs.~\ref{fig:corona} \& \ref{fig:inout}).
 
@@
 % NIHAO VIII:
-\bibitem[Gutcke et al.(2016)]{Gutcke16} Gutcke, T.~A., Stinson, G.~S., Macci{\`o}, A.~V., et al.\ 2016, arXiv:1602.06956
+\bibitem[Gutcke et al.(2016)]{Gutcke16} Gutcke, T.~A., Stinson, G.~S., Macci{\`o}, A.~V., et al.\ 2016, arXiv:1602.06956, MNRAS in press
 
@@
 
-%
-\bibitem[Oppenheimer et al.(2016)]{Oppenheimer16} Oppenheimer, B.~D., Crain, R.~A., Schaye, J., et al.\ 2016, arXiv:1603.05984
+% Bimodality of low-redshift circumgalactic O VI in non-equilibrium EAGLE zoom simulations
+\bibitem[Oppenheimer et al.(2016)]{Oppenheimer16} Oppenheimer, B.~D., Crain, R.~A., Schaye, J., et al.\ 2016, \mnras, 460, 2157
 
@@
 % A Universal Density Structure for Circum-Galactic Gas
-\bibitem[Stern et al.(2016)]{Stern16} 
-Stern, J., Hennawi, J.~F., Prochaska, J.~X., Werk, J.~K.\ 2016, arXiv:1604.02168
+\bibitem[Stern et al.(2016)]{Stern16} Stern, J., Hennawi, J.~F., Prochaska, J.~X., \& Werk, J.~K.\ 2016, \apj, 830, 87
 
@@
 
-%
-\bibitem[Suresh et al.(2015)]{Suresh15b} Suresh, J., Rubin, K.~H.~R., Kannan, R., et al.\ 2015, arXiv:1511.00687
+% On the OVI Abundance in the Circumgalactic Medium of Low-Redshift Galaxies
+\bibitem[Suresh et al.(2015)]{Suresh15} Suresh, J., Rubin, K.~H.~R., Kannan, R., et al.\ 2015, arXiv:1511.00687
 
@@
 %the Sunyaev-Zeldovich effect and soft X-ray emission 
-\bibitem[van de Voort et al.(2016)]{Voort16} van de Voort, F., Quataert, E., Hopkins, P.~F., et al.\ 2016, arXiv:1604.01397
+\bibitem[van de Voort et al.(2016)]{Voort16} van de Voort, F., Quataert, E., Hopkins, P.~F., et al.\ 2016, \mnras, 463, 4533
 

### 2016-11-30 ms_nihao_budget.tex
fix a problem on afflication

@@
 $^4$International Centre for Radio Astronomy Research (ICRAR)
-, M468, University of Western Australia, 35 Stirling Hwy, Cr
-awley, WA 6009, Australia}
+, M468, University of Western Australia, 35 Stirling Hwy, \\
+Crawley, WA 6009, Australia}
 \begin{document}

### 2017-01-03 ms_nihao_budget.tex
version suggested by the referee

@@
 
-{\bf As a part of the IGM, the circum galactic medium (CGM) is always 
-treated as }an major potential
+As a part of the IGM, the circum galactic medium (CGM) is always 
+treated as an major potential
 reservoir of the missing baryons. \hi{} and metal absorption lines are
@@
 outflows at intermediate redshift $z \approx 0.5-2$ remove a large
-amount of gas from the halo. {\bf Several simulations 
-\citep[e.g.,][]{Crain10, Christensen16,Voort16}} found the baryon fraction
+amount of gas from the halo. Several simulations 
+\citep[e.g.,][]{Crain07, Christensen16,Voort16} found the baryon fraction
 and gas fraction are reduced compared to the cosmic baryon
@@
 respectively.  We adopted the  latest compilation of cosmological
-parameters from the Planck  satellite \citep{Planck14}.   {\bf Dark
+parameters from the Planck  satellite \citep{Planck14}.   Dark
   matter particle masses range from $\sim 10^{4} \Msun$ in  our lowest
@@
   $(\Omega_{\rm dm}/\Omega_{\rm b})\simeq 5.48$, and  the
-  corresponding force softenings are 2.34 times smaller.}  More
+  corresponding force softenings are 2.34 times smaller.  More
 information on the collisionless parent simulations, the force
@@
 the most massive galaxy in each zoom-in region. We present the
-fractions of total stellar mass {\bf within 20\% $R_{200}$} (blue
+fractions of total stellar mass within 20\% $R_{200}$ (blue
 points),  and the total baryonic mass including stellar mass plus gas
@@
 
-%% FIGURE 2
-\begin{figure*}
-\centerline{
-  \psfig{figure=budget_res.eps,width=0.95\textwidth}
-}
-\caption{{\bf Baryon content of NIHAO simulations as a function of
-    halo mass color coded by number of dark matter particles per
-    halo. This shows the stars and gas content of the simulations is
-    insensitive to order of magnitude changes in particle
-    resolution.}}
-\label{fig:budget_res}
-\end{figure*}
-
 Since most of the haloes we study are above the mass where the cosmic
@@
 the lower star formation efficiency is more than compensated by the
-shallower potential wells of lower mass halos according {\bf to} the
-mass loading factor and circular velocity  {\bf relation }$\eta
+shallower potential wells of lower mass halos according to the
+mass loading factor and circular velocity  relation $\eta
 \propto V^{-2}$ \citep[e.g.,][]{Dutton12, Christensen16}.
@@
 preventing it from collapsing into the low mass haloes. The
-baryon fractions {\bf in low mass haloes} are thus controlled primarily 
+baryon fractions in low mass haloes are thus controlled primarily 
 by the halo masses, and thus are independent of the large scatter in the
-{\bf stellar mass}.
-
-{\bf Fig.~\ref{fig:budget_res} shows the budget fraction of stars, cold, cool
-  and warm-hot gas color coded by the number of dark matter particles
-  inside the virial radius. Since one can imagine that with increased
-  resolution, higher densities can be achieved in the CGM, potential
-  leading to more cooling and larger cold/cool gas fractions.  In our
-  simulations we find no dependence of stars and gas fractions with particle
-  number, indicating these quantities are not sensitive to numerical
-  resolution using the NIHAO sub-grid model.}
-
-%% FIGURE 3
+stellar mass.
+
+%% FIGURE 2
 \begin{figure*}
@@
 details of the simulation code. In particular all three codes predict a
-greater fraction of missing baryons in lower mass haloes. This
-suggests that the potential well of the halo {\bf correlates the baryon
-fraction more closely} than the strength of the feedback.
+greater fraction of missing baryons in lower mass haloes. 
+{\bf It suggests that the baryon fraction correlates 
+strongly with halo mass, due to the deeper potential well of the halo and/or stronger 
+ram pressure experienced by the outflowing gas. However, Fig.~\ref{fig:fire_com}
+ suggests that the 
+ specific implementation of the feedback model does not matter, as long as the feedback 
+is efficient in driving outflows.}
 
@@
 To estimate how far the baryons escape, we measured the radius,
-$\Rbar$, within which the total baryon mass equals the fiducial
-baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
+$\Rbar$, within which the total baryon mass equals the {\bf fiducial
+baryonic mass defined by Eq.~\ref{equ:mb}}. This is a lower limit to
 the true extent of the missing baryons since the baryon mass includes
-gas and stars that belong to nearby lower mass haloes.  {\bf It is a
+gas and stars that belong to nearby lower mass haloes.  It is a
   radius within the high-resolution volume of the simulations since
-  the contamination fraction in a shell between 0.9 and  1.0 $\Rbar$
+  the {\bf mass fraction of low resolution dark matter particles}
+  in a shell between 0.9 and  1.0 $\Rbar$
   shows most NIHAO galaxies have a fraction close to 0, with largest
-  only around 10 - 20\%. } Fig.~\ref{fig:missvr} shows the baryon
+  only around 10 - 20\%.  Fig.~\ref{fig:missvr} shows the baryon
 radius of each galaxy as function of the virial mass. In physical
@@
 phases) inside the virial radius (filled blue points) and between the
-virial and baryon radius (open red points).  {\bf All fractions are
-  relative to the fiducial baryonic mass within the  virial radius}.
+virial and baryon radius (open red points).  All fractions are
+  relative to the fiducial baryonic mass within the  virial radius.
 %
@@
 abundance matching as described in \citet{Kravtsov14}, while the cold
-disk gas mass comes from \citet{Dutton11}.  {\bf The upper limits to
+disk gas mass comes from \citet{Dutton11}.  The upper limits to
   the missing fraction are calculated using the lower limits to all
@@
   \citep{Werk14,Stern16}. The lower limit to the missing fraction is
-  consistent with zero.}
+  consistent with zero.
 
@@
 
-{\bf Since \citet{Crain10} and \citet{Voort13} show that  soft X-ray
+ Since \citet{Crain07} and \citet{Voort13} show that  soft X-ray
   emission traces gas with temperatures a few times the  virial
@@
   NIHAO simulations are in good agreement with the observed warm-hot
-  and hot gas fractions. }
+  and hot gas fractions.
 
@@
   Milky Way-sized zoom-in cosmological simulations \citep{Colin16} is
-  generally {\bf consistent} with our results. The fraction of cool gas
+  generally consistent with our results. The fraction of cool gas
   from their simulations is even lower  ($f_{\rm cool}$ = 0.034) than
@@
   virial radii (Fig.~\ref{fig:corona}). Cool gas ($10^4 < T < 10^5$K)
-  dominates the baryonic mass outside the virial radius, {\bf as well
-    as outside 20\% $R_{200}$}, at low masses ($M_{200}\lta 3\times
+  dominates the baryonic mass outside the virial radius, as well
+    as outside 20\% $R_{200}$, at low masses ($M_{200}\lta 3\times
   10^{11} \Msun$) while the warm-hot gas ($10^5 < T <5\times 10^6$K)
@@
 
-%X-ray coronae in simulations of disc galaxy formation
-\bibitem[Crain et al.(2010)]{Crain10}
-Crain, R.~A., McCarthy, I.~G., Frenk, C.~S., et al.\ 2010, \mnras, 470, 1403
+%The baryon fraction of CDM haloes
+\bibitem[Crain et al.(2007)]{Crain07}
+Crain, R.~A., Eke, C.~R., Frenk, C.~S., et al.\ 2007, \mnras, 377, 41
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% APPENDICES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+\section{Resolution test}
+
+{\bf Fig.~\ref{fig:budget_res} shows the budget fraction of stars, cold, cool
+  and warm-hot gas color coded by the number of dark matter particles
+  inside the virial radius. Since one can imagine that with increased
+  resolution, higher densities can be achieved in the CGM, potential
+  leading to more cooling and larger cold/cool gas fractions.  In our
+  simulations we find no dependence of stars and gas fractions with particle
+  number, indicating these quantities are not sensitive to numerical
+  resolution using the NIHAO sub-grid model.}
+
+%% FIGURE in APPENDICES
+\begin{figure*}
+\centerline{
+  \psfig{figure=budget_res.eps,width=0.95\textwidth}
+}
+\caption{Baryon content of NIHAO simulations as a function of
+    halo mass color coded by number of dark matter particles per
+    halo. This shows the stars and gas content of the simulations is
+    insensitive to order of magnitude changes in particle
+    resolution.}
+\label{fig:budget_res}
+\end{figure*}
+
 \label{lastpage}

### 2017-01-03 ms_nihao_budget.tex
move ICRAR as first affliation

@@
 \newauthor{Thales Gutcke$^3$, Xi Kang$^1$}\\
-$^1$Purple Mountain Observatory, the Partner Group of MPI f\"ur Astronomie, 2 West Beijing Road, Nanjing 210008, China\\
-$^2$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\
-$^3$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany\\
-$^4$International Centre for Radio Astronomy Research (ICRAR)
+$^1$International Centre for Radio Astronomy Research (ICRAR)
 , M468, University of Western Australia, 35 Stirling Hwy, \\
-Crawley, WA 6009, Australia}
+Crawley, WA 6009, Australia\\
+$^2$Purple Mountain Observatory, the Partner Group of MPI f\"ur Astronomie, 2 West Beijing Road, Nanjing 210008, China\\
+$^3$New York University Abu Dhabi, PO Box 129188, Abu Dhabi, UAE\\
+$^4$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany}
 \begin{document}

### 2017-01-03 ms_nihao_budget.tex
change the email address and correct the affliation for authors

@@
 
-\author[Wang et al.]{Liang Wang$^{1,3,4}$\thanks{wangliang@pmo.ac.cn}, Aaron A. Dutton$^{2,3}$,
-  Gregory S. Stinson$^3$, Andrea V. Macci\`o$^{2,3}$, 
-\newauthor{Thales Gutcke$^3$, Xi Kang$^1$}\\
+\author[Wang et al.]{Liang Wang$^{1,2,4}$\thanks{liang.wang@uwa.edu.au}, Aaron A. Dutton$^{3,4}$,
+  Gregory S. Stinson$^4$, Andrea V. Macci\`o$^{3,4}$, 
+\newauthor{Thales Gutcke$^4$, Xi Kang$^2$}\\
 $^1$International Centre for Radio Astronomy Research (ICRAR)

### 2017-01-10 ms_nihao_budget.tex
make clean files

@@
 greater fraction of missing baryons in lower mass haloes. 
-{\bf It suggests that the baryon fraction correlates 
+It suggests that the baryon fraction correlates 
 strongly with halo mass, due to the deeper potential well of the halo and/or stronger 
@@
  specific implementation of the feedback model does not matter, as long as the feedback 
-is efficient in driving outflows.}
+is efficient in driving outflows.
 
@@
 To estimate how far the baryons escape, we measured the radius,
-$\Rbar$, within which the total baryon mass equals the {\bf fiducial
-baryonic mass defined by Eq.~\ref{equ:mb}}. This is a lower limit to
+$\Rbar$, within which the total baryon mass equals the fiducial
+baryonic mass defined by Eq.~\ref{equ:mb}. This is a lower limit to
 the true extent of the missing baryons since the baryon mass includes
@@
   radius within the high-resolution volume of the simulations since
-  the {\bf mass fraction of low resolution dark matter particles}
+  the mass fraction of low resolution dark matter particles
   in a shell between 0.9 and  1.0 $\Rbar$
@@
 
-{\bf Fig.~\ref{fig:budget_res} shows the budget fraction of stars, cold, cool
+ Fig.~\ref{fig:budget_res} shows the budget fraction of stars, cold, cool
   and warm-hot gas color coded by the number of dark matter particles
@@
   number, indicating these quantities are not sensitive to numerical
-  resolution using the NIHAO sub-grid model.}
+  resolution using the NIHAO sub-grid model.
 
